### 2012-12-01 docs/msr.tex
added docs folder

\documentclass[conference]{IEEEtran}

\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\title{TBA - software evolution, security defects oriented}

\author{\IEEEauthorblockN{Dimitris Mitropoulos, Vassilios Karakoidas, Georgios Gousios, Panos Louridas
and
Diomidis Spinellis}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: \{dimitro, bkarak, gousiosg, louridas, dds\}@aueb.gr}
}
\maketitle

\begin{abstract}
%\boldmath
The abstract goes here.
\end{abstract}

\begin{IEEEkeywords}
Software Vulnerabilities, Static Analysis, Software Evolution, Maven, FindBugs.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}

Cite this~\cite{MNN11}.

\section{Methodology}
\label{sec:meth}

\subsection{Data Provenance and Processing}

A snapshot of the maven repository - January 2012.

\section{Results and Analysis}
\label{sec:res}

\section{Conclusion}
\label{sec:con}
The conclusion goes here.

\section*{Acknowledgments}

The project is being co-financed by the European Regional Development Fund (ERDF)
and national funds and is a part of the Operational Programme ``Competitiveness \&
Entrepreneurship" (OPCE II), Measure ``COOPERATION" (Action I).

\bibliographystyle{IEEEtran}
\bibliography{msr}

\end{document}

### 2012-12-20 docs/msr.tex
Change my affiliation

@@
 
-\author{\IEEEauthorblockN{Dimitris Mitropoulos, Vassilios Karakoidas, Georgios Gousios, Panos Louridas
-and
-Diomidis Spinellis}
+\author{
+\IEEEauthorblockN{Dimitris Mitropoulos \and Vassilios Karakoidas \and Panos Louridas \and Diomidis Spinellis}
 \IEEEauthorblockA{Department of Management Science and Technology\\
@@
 Email: \{dimitro, bkarak, gousiosg, louridas, dds\}@aueb.gr}
+\and
+\IEEEauthorblockN{Georgios Gousios}
+\IEEEauthorblockA{Department of Software and Computer Technology\\
+Delft University of Technology \\
+Email: G.Gousios@tudelft.nl}
 }
+
 \maketitle

### 2012-12-20 worker/process-win.py
added initial port for win32

@@ -37,14 +37,6 @@ import pymongo
 import time
 import urllib
 from subprocess import Popen, PIPE, STDOUT
-from signal import signal, SIGINT, SIGUSR1, SIGTERM
-from daemon import daemon
-
-# Take care of differences between python-daemon versions.
-try:
-    from daemon import pidfile
-except:
-    from daemon import pidlockfile
 
 __author__ = 'Georgios Gousios <gousiosg@gmail.com>, Vassilios Karakoidas (vassilios.karakoidas@gmail.com), Dimitrios Mitropoulos (dimitro@aueb.gr)'
 
@@ -387,24 +379,6 @@ class RunFindbugs:
         log.info("Msgs acked: %d" % self.msgs_acked)
         log.info("Msgs rejected: %d" % self.msgs_rejected)
 
-def _exit_handler(signum, frame):
-    """"Catch exit signal in children processes"""
-    global log
-    log.info("Caught signal %d, will raise SystemExit", signum)
-    raise SystemExit
-
-
-def _usr1_handler(signum, frame):
-    global log
-    log.info("Caught signal %d, will print statistics to log", signum)
-    raise StatsException("stats")
-
-def _parent_handler(signum):
-    """"Catch exit signal in parent process and forward it to children."""
-    global children
-
-    log.info("Caught signal %d, sending SIGTERM to children %s", signum, children)
-    [os.kill(pid, SIGTERM) for pid in children]
 
 class StatsException():
     def __init__(self, msg):
@@ -459,45 +433,16 @@ def parse_arguments(args):
 
 
 def debug(opts):
-    signal(SIGINT, _exit_handler)
-    signal(SIGUSR1, _usr1_handler)
-    signal(SIGTERM, _exit_handler)
     RunFindbugs(opts)
 
 def spawn_workers(opts):
-    global children
-
     log.info("Spawning %s workers" % opts.workers)
-    # Fork workers
-    children = []
     i = 0
 
     while i < opts.workers:
-        try:
-            newpid = os.fork()
-            if newpid == 0:
-                signal(SIGINT, _exit_handler)
-                signal(SIGTERM, _exit_handler)
-                RunFindbugs(opts)
-                sys.exit(1)
-            else:
-                log.debug("%d, forked child: %d", os.getpid(), newpid)
-                children.append(newpid)
-        except Exception:
-            log.exception("Error spawning worker %d" % i)
-        finally:
-            i += 1
-
[…]

### 2012-12-20 worker/process.py
minor edit

@@ -211,12 +211,14 @@ class RunFindbugs:
     
         def get_jar_size(filename):
             size = 0
+            
             if zipfile.is_zipfile(filename):
                 try:
                     z = zipfile.ZipFile(filename)
                     for info in z.infolist():
                         if info.filename.endswith('.class'):
                             size += info.file_size
+
                     return size
                 except Exception, e:
                     return 0

### 2012-12-20 worker/process.py
fix: AutoReconnect pymongo exception is now handled

@@ -327,7 +327,8 @@ class RunFindbugs:
                     return result_json
 
                 # Save it
-                self.store_to_mongo(__convert_findbugs_xml(body, findbugs_xml))
+                if not self.record_exists(metadata):
+                    self.store_to_mongo(__convert_findbugs_xml(body, findbugs_xml))
             else:
                 log.warn('%s contains no .class files' % (file,))
 
@@ -356,19 +357,28 @@ class RunFindbugs:
         return coll
 
     def store_to_mongo(self, json):
-        id = self.get_collection().insert(json)
-        log.debug("Stored with ID: " + str(id))
+        try:
+            id = self.get_collection().insert(json)
+            log.debug("Stored with ID: " + str(id))
+        except pymongo.errors.AutoReconnect, ae:
+            log.warning('Mongo Connection is Down. Reconnecting! (store_to_mongo, %s)' % (ae,))
 
     def record_exists(self, metadata):
-        q = dict()
-        q['JarMetadata'] = dict()
-        q['JarMetadata']['group_id'] = metadata['group_id']
-        q['JarMetadata']['artifact_id'] = metadata['artifact_id']
-        q['JarMetadata']['version'] = metadata['version']
-        if self.get_collection().find_one(q) is None:
-            return False
-        else:
-            return True
+        try:
+            q = dict()
+            q['JarMetadata'] = dict()
+            q['JarMetadata']['group_id'] = metadata['group_id']
+            q['JarMetadata']['artifact_id'] = metadata['artifact_id']
+            q['JarMetadata']['version'] = metadata['version']
+            if self.get_collection().find_one(q, timeout=False) is None:                
+                log.info('findone() -  False')
+                return False
+            else:
+                log.info('findone() - True')
+                return True
+        except pymongo.errors.AutoReconnect, ae:
+            log.warning('Mongo Connection is Down. Reconnecting! (record_exists, %s)' % (ae,))
+            return record_exists(metadata)
 
     def get_mongo_db(self):
         """

### 2012-12-20 worker/process.py
added self before method calls

@@ -362,6 +362,7 @@ class RunFindbugs:
             log.debug("Stored with ID: " + str(id))
         except pymongo.errors.AutoReconnect, ae:
             log.warning('Mongo Connection is Down. Reconnecting! (store_to_mongo, %s)' % (ae,))
+            self.store_to_mongo(json)
 
     def record_exists(self, metadata):
         try:
@@ -378,7 +379,7 @@ class RunFindbugs:
                 return True
         except pymongo.errors.AutoReconnect, ae:
             log.warning('Mongo Connection is Down. Reconnecting! (record_exists, %s)' % (ae,))
-            return record_exists(metadata)
+            return self.record_exists(metadata)
 
     def get_mongo_db(self):
         """

### 2012-12-20 worker/process-win.py
ported fix to process-win.py

@@ -317,7 +317,8 @@ class RunFindbugs:
                     return result_json
 
                 # Save it
-                self.store_to_mongo(__convert_findbugs_xml(body, findbugs_xml))
+                if not self.record_exists(metadata):
+                    self.store_to_mongo(__convert_findbugs_xml(body, findbugs_xml))
             else:
                 log.warn('%s contains no .class files' % (file,))
 
@@ -346,19 +347,29 @@ class RunFindbugs:
         return coll
 
     def store_to_mongo(self, json):
-        id = self.get_collection().insert(json)
-        log.debug("Stored with ID: " + str(id))
+        try:
+            id = self.get_collection().insert(json)
+            log.debug("Stored with ID: " + str(id))
+        except pymongo.errors.AutoReconnect, ae:
+            log.warning('Mongo Connection is Down. Reconnecting! (store_to_mongo, %s)' % (ae,))
+            self.store_to_mongo(json)
 
     def record_exists(self, metadata):
-        q = dict()
-        q['JarMetadata'] = dict()
-        q['JarMetadata']['group_id'] = metadata['group_id']
-        q['JarMetadata']['artifact_id'] = metadata['artifact_id']
-        q['JarMetadata']['version'] = metadata['version']
-        if self.get_collection().find_one(q) is None:
-            return False
-        else:
-            return True
+        try:
+            q = dict()
+            q['JarMetadata'] = dict()
+            q['JarMetadata']['group_id'] = metadata['group_id']
+            q['JarMetadata']['artifact_id'] = metadata['artifact_id']
+            q['JarMetadata']['version'] = metadata['version']
+            if self.get_collection().find_one(q, timeout=False) is None:                
+                log.info('findone() -  False')
+                return False
+            else:
+                log.info('findone() - True')
+                return True
+        except pymongo.errors.AutoReconnect, ae:
+            log.warning('Mongo Connection is Down. Reconnecting! (record_exists, %s)' % (ae,))
+            return self.record_exists(metadata)
 
     def get_mongo_db(self):
         """

### 2013-01-03 data analysis/analyze.py
quering in a programming fashion.

@@ -1,0 +1,59 @@
+import pymongo
+
+
+MONGO_HOST   = '83.212.106.194'
+MONGO_DB     = 'findbugs'
+MONGO_COL    = 'findbugs'
+MONGO_UNAME  = 'findbugs'
+MONGO_PASSWD = 'findbags'
+
+
+def get_mongo_db():
+    """
+    Gets a connection to MongoDB
+    """
+    conn = pymongo.Connection(host=MONGO_HOST, max_pool_size=10, network_timeout=1)
+    mongo_db = conn[MONGO_DB]
+    mongo_db.authenticate(MONGO_UNAME, MONGO_PASSWD)
+    
+    return mongo_db
+
+def record_exists(col_obj, group_id, artifact_id):
+    try:
+        q = {'JarMetadata.group_id' : group_id,
+             'JarMetadata.artifact_id' : artifact_id}
+
+        for c in col_obj.find(q, timeout=False):
+            print c['JarMetadata']['version']
+    except pymongo.errors.AutoReconnect, ae:
+        print 'Mongo Connection is Down. Reconnecting! (record_exists, %s)' % (ae,)
+        return record_exists(col_obj, group_id, artifact_id)
+        
+def count_security_category_records(col_obj, skip=0):
+    counter = skip
+    try:     
+        q = {'BugCollection.BugInstance.category':'SECURITY'}
+        
+        for c in col_obj.find(q, timeout = False, skip=skip):
+            for bi in c['BugCollection']['BugInstance']:
+                if bi['category'] == 'SECURITY':                    
+                    counter += 1
+                    print counter
+            
+        print counter
+    except pymongo.errors.AutoReconnect, ae:
+        print 'Mongo Connection is Down. Reconnecting! (record_exists, %s)' % (ae,)
+        count_security_category_records(col_obj, skip=counter)
+                    
+            
+
+def main():
+    mongo_db = get_mongo_db()
+    col = mongo_db[MONGO_COL]
+    count_security_category_records(col)
+    #record_exists(col, 'org.apache.geronimo.modules', 'geronimo-j2ee-builder')
+    
+    
+
+if __name__ == "__main__":
+    main()

### 2013-01-04 data analysis/analyze.py
renamed folder

@@ -1,59 +1,0 @@
-import pymongo
-
-
-MONGO_HOST   = '83.212.106.194'
-MONGO_DB     = 'findbugs'
-MONGO_COL    = 'findbugs'
-MONGO_UNAME  = 'findbugs'
-MONGO_PASSWD = 'findbags'
-
-
-def get_mongo_db():
-    """
-    Gets a connection to MongoDB
-    """
-    conn = pymongo.Connection(host=MONGO_HOST, max_pool_size=10, network_timeout=1)
-    mongo_db = conn[MONGO_DB]
-    mongo_db.authenticate(MONGO_UNAME, MONGO_PASSWD)
-    
-    return mongo_db
-
-def record_exists(col_obj, group_id, artifact_id):
-    try:
-        q = {'JarMetadata.group_id' : group_id,
-             'JarMetadata.artifact_id' : artifact_id}
-
-        for c in col_obj.find(q, timeout=False):
-            print c['JarMetadata']['version']
-    except pymongo.errors.AutoReconnect, ae:
-        print 'Mongo Connection is Down. Reconnecting! (record_exists, %s)' % (ae,)
-        return record_exists(col_obj, group_id, artifact_id)
-        
-def count_security_category_records(col_obj, skip=0):
-    counter = skip
-    try:     
-        q = {'BugCollection.BugInstance.category':'SECURITY'}
-        
-        for c in col_obj.find(q, timeout = False, skip=skip):
-            for bi in c['BugCollection']['BugInstance']:
-                if bi['category'] == 'SECURITY':                    
-                    counter += 1
-                    print counter
-            
-        print counter
-    except pymongo.errors.AutoReconnect, ae:
-        print 'Mongo Connection is Down. Reconnecting! (record_exists, %s)' % (ae,)
-        count_security_category_records(col_obj, skip=counter)
-                    
-            
-
-def main():
-    mongo_db = get_mongo_db()
-    col = mongo_db[MONGO_COL]
-    count_security_category_records(col)
-    #record_exists(col, 'org.apache.geronimo.modules', 'geronimo-j2ee-builder')
-    
-    
-
-if __name__ == "__main__":
-    main()

### 2013-01-12 analysis/repo-statistics/data_helper.py
implemented find_projects

@@ -5,11 +5,17 @@ class ArrayCount(object):
         super(ArrayCount, self).__init__()
         self.__arrayDict = {}
 
-    def incr(self, counter):
-        self.__arrayDict[counter] = self.__arrayDict.get(counter, 0) + 1
+    def incr(self, item):
+        self.__arrayDict[item] = self.__arrayDict.get(item, 0) + 1
 
     def get_series(self):
         return self.__arrayDict
+
+    def item_count(self):
+        return len(self.__arrayDict)
+
+    def value_count(self):
+        return sum(self.__arrayDict.values())
 
 
 def save_to_file(filename, data):

### 2013-01-12 analysis/repo-statistics/find_projects.py

@@ -1,29 +1,24 @@
-import json
+import json, data_helper, mongo_helper
+
+
 
 def main():
-    results = {}
-    fp = open('maven_jars_only.text', 'r')
+    results = data_helper.ArrayCount()
+    miter = mongo_helper.MongoDocumentIterator()
 
-    for l in fp:
-        try:
-            data_arr = l.split(' maven/')[1].strip().split('/')
+    print 'Found %d Documents' % (miter.total(),)
 
-            group_id = data_arr[-4]
-            artifact_id = data_arr[-3]
+    while miter.has_next():
+        d = miter.next()
 
-            project_key = '%s.%s' % (group_id, artifact_id)
+        if d is not None:
+            group_id = d['JarMetadata']['group_id']
+            artifact_id = d['JarMetadata']['artifact_id']
+            ga = '%s||%s' % (group_id, artifact_id)
+            results.incr(ga)
+            print 'Working %d of %d' % (miter.count(), miter.total(), )
 
-            if project_key not in results:
-                results[project_key] = {'group_id':group_id, 'artifact_id':artifact_id}
-                print 'Found %d Projects' % (len(results,))
-        except (IndexError, ValueError), e:
-            print 'ERROR: %s' % (l.strip(),)
-
-    fp.close()
-
-    fp = open('projects.json', 'w')
-    fp.write(json.dumps(results.values()))
-    fp.close()
+    data_helper.save_to_file('new_projects.json', json.dumps(results.get_series()))
 
 
 if __name__ == "__main__":

### 2013-01-12 analysis/repo-statistics/mongo_helper.py

@@ -7,7 +7,47 @@ MONGO_UNAME  = 'findbugs'
 MONGO_PASSWD = 'findbags'
 
 
-def get_mongo_db():
+class MongoDocumentIterator(object):
+    def __init__(self):
+        super(MongoDocumentIterator, self).__init__()
+        self.__doc_count = 0
+        self.__total_count = 0
+        self.__connection = get_mongo_connection()
+        self.__collection = self.__connection[MONGO_COL]
+        self.__count_documents()
+
+    def __count_documents(self):
+        try:
+            self.__total_count = self.__collection.find(timeout=False).count()
+        except pymongo.errors.AutoReconnect, ar:
+            print '__count_documents() - %s (reconnecting)' % (ar,)
+
+    def reset(self):
+        self.__doc_count = 0
+
+    def has_next(self):
+        return self.__doc_count < self.__total_count
+
+    def next(self):
+        try:
+            d = None
+
+            for c in self.__collection.find(skip=self.__doc_count, limit=1):
+                d = c
+            self.__doc_count += 1
+            return d
+        except pymongo.errors.AutoReconnect, ar:
+            print 'next() - %s (reconnecting)' % (ar,)
+            return None
+
+    def total(self):
+        return self.__total_count
+
+    def count(self):
+        return self.__doc_count
+
+
+def get_mongo_connection():
     """
     Gets a connection to MongoDB
     """

### 2013-01-12 docs/msr.tex
quering in a programming fashion.
added paper title

@@
 
-\title{TBA - software evolution, security defects oriented}
+\title{Dismal Code: Studying the Evolution of Security Vulnerabilities}
 
@@
 
+A security-related bug is a programming error that introduces a potentially
+exploitable weakness into a computer system. This weakness could lead to a
+security breach with unfortunate consequences in different layers, like databases,
+native code, applications, libraries and others. One of the most common
+approaches to identify software vulnerabilities is {\it static analysis}. This
+kind of analysis is performed by automated tools either on the program's source
+or object code and without actually executing it.
+
 Cite this~\cite{MNN11}.
+
+\section{Related Work}
+
+Cite this~\cite{ZAH11}.
 
@@
 \subsection{Data Provenance and Processing}
+\label{sec:data}
 
 A snapshot of the maven repository - January 2012.
+
+\subsection{Experiment}
+\label{sec:exp}
 

### 2013-01-13 analysis/repo-statistics/mongo_helper.py
added project with version count.json

@@ -32,7 +32,7 @@ class MongoDocumentIterator(object):
         try:
             d = None
 
-            for c in self.__collection.find(skip=self.__doc_count, limit=1):
+            for c in self.__collection.find(skip=self.__doc_count, limit=1, fields=['JarMetadata.group_id', 'JarMetadata.artifact_id']):
                 d = c
             self.__doc_count += 1
             return d

### 2013-01-13 analysis/repo-statistics/create_statistics.py
sanitising repository

@@ -1,36 +1,0 @@
-import mongo_helper, json, data_helper
-
-
-def load_projects():
-    fp = open('projects.json', 'r')
-    buf = fp.read()
-    fp.close()
-
-    return json.loads(buf)
-
-def main():
-    mongo_db = mongo_helper.get_mongo_db()
-    col = mongo_db[mongo_helper.MONGO_COL]
-    arrayCount = data_helper.ArrayCount()
-    ga_projects = load_projects()
-    ga_project_count = len(ga_projects)
-    ga_counter = 0
-    ga_valid = 0
-
-    for ga in ga_projects:
-        group_id = ga['group_id']
-        artifact_id = ga['artifact_id']
-        versions = mongo_helper.get_project_versions(col, group_id, artifact_id)
-        no_versions = len(versions)
-        ga_counter += 1
-
-        if no_versions > 0:
-            ga_valid += 1
-            print '[%d:%d:%d] -> group_id: %s, artifact_id: %s, versions: %d' % (ga_counter, ga_valid, ga_project_count, group_id, artifact_id, no_versions)
-            arrayCount.incr(no_versions)
-
-    data = arrayCount.get_series()
-    data_helper.save_to_file('version_count.json', json.dumps(data))
-
-if __name__ == "__main__":
-    main()

### 2013-01-13 analysis/repo-statistics/find_projects.py

@@ -1,6 +1,11 @@
 import json, data_helper, mongo_helper
 
 
+#
+# This script generated the number of projects
+#
+
+__author__ = "Vassilios Karakoidas (vassilios.karakoidas@gmail.com)"
 
 def main():
     results = data_helper.ArrayCount()
@@ -16,7 +21,7 @@ def main():
             artifact_id = d['JarMetadata']['artifact_id']
             ga = '%s||%s' % (group_id, artifact_id)
             results.incr(ga)
-            print 'Working %d of %d' % (miter.count(), miter.total(), )
+            print 'Working %d of %d' % (miter.count(), miter.total(),)
 
     data_helper.save_to_file('new_projects.json', json.dumps(results.get_series()))
 

### 2013-01-13 analysis/repo-statistics/mongo_mr.py

@@ -1,31 +1,0 @@
-import mongo_helper
-
-from bson.code import Code
-
-
-def main():
-    mapper = Code("""
-                  function() {
-                    emit(this.JarMetadata.group_id + "||" + this.JarMetadata.artifact_id, 1);
-                  }""")
-
-    reducer = Code("""
-                   function(key, values) {
-                     var total = 0;
-
-                     for (var i = 0; i < values.length; i++) {
-                        total += values[i];
-                     }
-
-                     return total;
-                   }
-                   """)
-
-    print "Connecting ... to %s" % (mongo_helper.MONGO_DB,)
-    db = mongo_helper.get_mongo_db()
-    result = db[mongo_helper.MONGO_COL].map_reduce(mapper, reducer, "myresults")
-    print result
-
-
-if __name__ == "__main__":
-    main()

### 2013-01-13 analysis/repo-statistics/analyze_statistics.py
moved analyze.py to examples

@@ -1,16 +1,0 @@
-import json
-
-def main():
-    fp = open('version_count.json', 'r')
-    json_data = json.load(fp)
-    fp.close()
-
-    project_count = 0
-
-    for (k, v) in json_data.iteritems():
-        project_count += (int(k)*v)
-
-    print project_count
-
-if __name__ == "__main__":
-    main()

### 2013-01-13 analysis/repo-statistics/find_projects.py

@@ -23,7 +23,7 @@ def main():
             results.incr(ga)
             print 'Working %d of %d' % (miter.count(), miter.total(),)
 
-    data_helper.save_to_file('new_projects.json', json.dumps(results.get_series()))
+    data_helper.save_to_file('projects.json', json.dumps(results.get_series()))
 
 
 if __name__ == "__main__":

### 2013-01-13 analysis/repo-statistics/find_projects.py
refactored code to python modules

@@ -1,15 +1,18 @@
-import json, data_helper, mongo_helper
+import json
 
+from helpers.mongo_helper import MongoDocumentIterator
+from helpers.data_helper import ArrayCount, save_to_file
 
 #
-# This script generated the number of projects
+# This script generates the "data/projects.json", which is a json dict (object)
+# with
 #
 
 __author__ = "Vassilios Karakoidas (vassilios.karakoidas@gmail.com)"
 
 def main():
-    results = data_helper.ArrayCount()
-    miter = mongo_helper.MongoDocumentIterator()
+    results = ArrayCount()
+    miter = MongoDocumentIterator()
 
     print 'Found %d Documents' % (miter.total(),)
 
@@ -23,7 +26,7 @@ def main():
             results.incr(ga)
             print 'Working %d of %d' % (miter.count(), miter.total(),)
 
-    data_helper.save_to_file('projects.json', json.dumps(results.get_series()))
+    save_to_file('projects.json', json.dumps(results.get_series()))
 
 
 if __name__ == "__main__":

### 2013-01-13 analysis/repo-statistics/helpers/mongo_helper.py
removed dead code

@@ -58,10 +58,6 @@ def get_mongo_connection():
     return mongo_db
 
 
-#def get_mongo_client():
-#    pymongo.MongoClient(host=MONGO_HOST, )
-
-
 def get_project_versions(col_obj, group_id, artifact_id):
     try:
         result = []

### 2013-01-13 analysis/repo-statistics/helpers/data_helper.py
added loaded projects

@@ -1,3 +1,4 @@
+import os, json
 
 
 class ArrayCount(object):
@@ -22,3 +23,22 @@ def save_to_file(filename, data):
     fp = open(filename, 'w')
     fp.write(data)
     fp.close()
+
+
+def load_projects_json():
+    from models.project import Project
+
+    if not os.path.exists('data/projects.json'):
+        print '[ERROR]: data/projects.json does not exist!'
+        return []
+
+    project_list = []
+    fp = open('data/projects.json', 'r')
+    prj_json = json.load(fp)
+    fp.close()
+
+    for (k, v) in prj_json.iteritems():
+        project_list.append(Project.parse_project(k, v))
+
+    return project_list
+

### 2013-01-13 analysis/repo-statistics/models/project.py

@@ -1,0 +1,31 @@
+
+
+class Project(object):
+    def __init__(self, group_id, artifact_id):
+        super(Project, self).__init__()
+        self.__group_id = group_id
+        self.__artifact_id = artifact_id
+        self.__version_count = 0
+
+    def group_id(self):
+        return self.__group_id
+
+    def artifact_id(self):
+        return self.__artifact_id
+
+    def set_version_count(self, c):
+        self.__version_count = c
+
+    def version_count(self):
+        return self.__version_count
+
+    @staticmethod
+    def parse_project(project_key, version_count):
+        pk_arr = project_key.split('||')
+        prj_obj = Project(pk_arr[0].strip(), pk_arr[1].strip())
+        prj_obj.set_version_count(version_count)
+
+        return prj_obj
+
+
+

### 2013-01-13 analysis/repo-statistics/find_projects.py
added author information

@@ -5,7 +5,7 @@ from helpers.data_helper import ArrayCount, save_to_file
 
 #
 # This script generates the "data/projects.json", which is a json dict (object)
-# with
+# with the following structure {<group_id>||<artifact_id> : version_count}
 #
 
 __author__ = "Vassilios Karakoidas (vassilios.karakoidas@gmail.com)"

### 2013-01-13 analysis/repo-statistics/helpers/data_helper.py

@@ -1,5 +1,6 @@
 import os, json
 
+__author__ = "Vassilios Karakoidas (vassilios.karakoidas@gmail.com)"
 
 class ArrayCount(object):
     def __init__(self):

### 2013-01-13 analysis/repo-statistics/helpers/mongo_helper.py

@@ -6,6 +6,7 @@ MONGO_COL    = 'findbugs'
 MONGO_UNAME  = 'findbugs'
 MONGO_PASSWD = 'findbags'
 
+__author__ = "Vassilios Karakoidas (vassilios.karakoidas@gmail.com)"
 
 class MongoDocumentIterator(object):
     def __init__(self):

### 2013-01-13 analysis/repo-statistics/models/project.py
added author information

@@ -1,5 +1,7 @@
 
 
+__author__ = "Vassilios Karakoidas (vassilios.karakoidas@gmail.com)"
+
 class Project(object):
     def __init__(self, group_id, artifact_id):
         super(Project, self).__init__()

### 2013-01-13 analysis/repo-statistics/repository_statistics.py
initial repository statistics

@@ -1,0 +1,18 @@
+from helpers.data_helper import load_projects_json
+
+__author__ = 'Vassilios Karakoidas (vassilios.karakoidas@gmail.com)'
+
+
+def main():
+    project_list = load_projects_json()
+
+    project_count = len(project_list)
+    version_count = sum([x.version_count() for x in project_list])
+
+    print "Projects: %d" % (project_count,)
+    print "Versions (total): %d" % (version_count,)
+    print "Avg. version/project: %.2f" % (float(version_count)/float(project_count))
+
+
+if __name__ == "__main__":
+    main()

### 2013-01-13 analysis/repo-statistics/repository_statistics.py
added max, min version

@@ -7,11 +7,16 @@ def main():
     project_list = load_projects_json()
 
     project_count = len(project_list)
-    version_count = sum([x.version_count() for x in project_list])
+    version_list = [x.version_count() for x in project_list]
+    version_count = sum(version_list)
+    max_version = max(version_list)
+    min_version = min(version_list)
 
     print "Projects: %d" % (project_count,)
     print "Versions (total): %d" % (version_count,)
-    print "Avg. version/project: %.2f" % (float(version_count)/float(project_count))
+    print "Avg. Version/Project: %.2f" % (float(version_count)/float(project_count))
+    print "Max. Version Count: %d" % (max_version,)
+    print "Min. Version Count: %d" % (min_version,)
 
 
 if __name__ == "__main__":

### 2013-01-13 analysis/repo-statistics/maths/statistics.py
added statistics.py; exported basic measurements for version

@@ -1,0 +1,91 @@
+#
+#
+# Basic statistical measurements
+# includes:
+#
+#
+# * min, max range
+# * 1st, 2rd Quartile
+# * Median
+# * Arithmetic mean
+# * standard deviation
+# * z-test implementation to find outliers
+#
+
+import math
+
+
+# range
+def stat_range(input_data):
+	return stat_max(input_data) - stat_min(input_data)
+
+# maximum value
+def stat_max(input_data):
+	return max(input_data)
+
+# minimum value
+def stat_min(input_data):
+	return min(input_data)
+
+# third quartile
+def third_quartile(input_data):
+	_length = len(input_data)
+
+	if (3*_length) / 4 == 1:
+		return (3*_length) + 1
+
+	return 3*_length / 4
+
+# first quartile
+def first_quartile(input_data):
+	_length = len(input_data)
+
+	if _length % 4 == 1:
+		return (_length / 4) + 1
+
+	return _length / 4
+
+# median
+def median(input_data):
+	_length = len(input_data)
+
+	if _length % 2 == 1:
+		return (_length / 2) + 1
+	
+	return _length / 2
+
+# arithmetic mean
+def mean(input_data):
+	_length = len(input_data)
+	_total = 0
+	
+	for i in input_data:
+		_total = _total + i
+	
+	return float(_total) / float(_length)
+
+# standard deviation
+def stddev(input_data):
+	_length = len(input_data)
+	_mean = mean(input_data)
+	_total = 0
+	
+	for i in input_data:
+		_total = _total + math.pow((i - _mean), 2)
+	
+	_total = float(_total) / float(_length)
+	
+	return math.sqrt(_total)
+
+
+def ztest(input_data):
+	_result = []
+	_mean = mean(input_data)
+	_stddev = stddev(input_data)
+	
+	for i in input_data:
+		_z = float(math.fabs(float(i) - float(_mean))) / float(_stddev)
+		if _z < 3:
+			_result.append(i)
+	
+	return _result

### 2013-01-13 analysis/repo-statistics/repository_statistics.py

@@ -1,5 +1,7 @@
 from helpers.data_helper import load_projects_json
 
+from maths import statistics
+
 __author__ = 'Vassilios Karakoidas (vassilios.karakoidas@gmail.com)'
 
 
@@ -9,14 +11,18 @@ def main():
     project_count = len(project_list)
     version_list = [x.version_count() for x in project_list]
     version_count = sum(version_list)
-    max_version = max(version_list)
-    min_version = min(version_list)
+
+    version_list = sorted(version_list)
 
     print "Projects: %d" % (project_count,)
     print "Versions (total): %d" % (version_count,)
-    print "Avg. Version/Project: %.2f" % (float(version_count)/float(project_count))
-    print "Max. Version Count: %d" % (max_version,)
-    print "Min. Version Count: %d" % (min_version,)
+    print "Max. Version Count: %d" % (statistics.stat_max(version_list),)
+    print "Min. Version Count: %d" % (statistics.stat_min(version_list),)
+    print "Mean: %.2f" % (statistics.mean(version_list))
+    print "Median: %d" % (statistics.median(version_list))
+    print "Range: %d" % (statistics.stat_range(version_list))
+    print "1st Qrt: %d" % (version_list[statistics.first_quartile(version_list)])
+    print "3rd Qrt: %d" % (version_list[statistics.third_quartile(version_list)])
 
 
 if __name__ == "__main__":

### 2013-01-13 analysis/repo-statistics/repository_statistics.py
fix: median is now the median not the index

@@ -19,7 +19,7 @@ def main():
     print "Max. Version Count: %d" % (statistics.stat_max(version_list),)
     print "Min. Version Count: %d" % (statistics.stat_min(version_list),)
     print "Mean: %.2f" % (statistics.mean(version_list))
-    print "Median: %d" % (statistics.median(version_list))
+    print "Median: %d" % (version_list[statistics.median(version_list)])
     print "Range: %d" % (statistics.stat_range(version_list))
     print "1st Qrt: %d" % (version_list[statistics.first_quartile(version_list)])
     print "3rd Qrt: %d" % (version_list[statistics.third_quartile(version_list)])

### 2013-01-13 analysis/repo-statistics/repository_statistics.py
added repository statistics

@@ -24,6 +24,5 @@ def main():
     print "1st Qrt: %d" % (version_list[statistics.first_quartile(version_list)])
     print "3rd Qrt: %d" % (version_list[statistics.third_quartile(version_list)])
 
-
 if __name__ == "__main__":
     main()

### 2013-01-13 analysis/repo-statistics/maths/statistics.py
converted tabs to spaces; simplified expression

@@ -1,5 +1,4 @@
 #
-#
 # Basic statistical measurements
 # includes:
 #
@@ -17,75 +16,75 @@ import math
 
 # range
 def stat_range(input_data):
-	return stat_max(input_data) - stat_min(input_data)
+    return stat_max(input_data) - stat_min(input_data)
 
 # maximum value
 def stat_max(input_data):
-	return max(input_data)
+    return max(input_data)
 
 # minimum value
 def stat_min(input_data):
-	return min(input_data)
+    return min(input_data)
 
 # third quartile
 def third_quartile(input_data):
-	_length = len(input_data)
+    _length = len(input_data)
 
-	if (3*_length) / 4 == 1:
-		return (3*_length) + 1
+    if (3*_length) / 4 == 1:
+        return (3*_length) + 1
 
-	return 3*_length / 4
+    return 3*_length / 4
 
 # first quartile
 def first_quartile(input_data):
-	_length = len(input_data)
+    _length = len(input_data)
 
-	if _length % 4 == 1:
-		return (_length / 4) + 1
+    if _length % 4 == 1:
+        return (_length / 4) + 1
 
-	return _length / 4
+    return _length / 4
 
 # median
 def median(input_data):
-	_length = len(input_data)
+    _length = len(input_data)
 
-	if _length % 2 == 1:
-		return (_length / 2) + 1
-	
-	return _length / 2
+    if _length % 2 == 1:
+        return (_length / 2) + 1
+
+    return _length / 2
 
 # arithmetic mean
 def mean(input_data):
-	_length = len(input_data)
-	_total = 0
-	
-	for i in input_data:
-		_total = _total + i
-	
-	return float(_total) / float(_length)
+    _length = len(input_data)
+    _total = 0
+
+    for i in input_data:
+        _total = _total + i
+
+    return float(_total) / float(_length)
 
 # standard deviation
 def stddev(input_data):
-	_length = len(input_data)
-	_mean = mean(input_data)
-	_total = 0
-	
-	for i in input_data:
-		_total = _total + math.pow((i - _mean), 2)
-	
-	_total = float(_total) / float(_length)
-	
-	return math.sqrt(_total)
+    _length = len(input_data)
+    _mean = mean(input_data)
+    _total = 0
+
+    for i in input_data:
+        _total += math.pow((i - _mean), 2)
+
+    _total = float(_total) / float(_length)
+
+    return math.sqrt(_total)
 
 
[…]

### 2013-01-16 analysis/repo-statistics/project_counters.py
group by projects

@@ -6,7 +6,7 @@ from helpers.mongo_helper import MongoProjectIterator
 
 def main():
     projects = load_vuln_projects_json()
-    results = []
+    results = {}
     security_bugs = ['HRS_REQUEST_PARAMETER_TO_COOKIE',
                      'HRS_REQUEST_PARAMETER_TO_HTTP_HEADER',
                      'PT_ABSOLUTE_PATH_TRAVERSAL',
@@ -23,7 +23,9 @@ def main():
     for p in projects:
         piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.jar_size', 'JarMetadata.version_order', 'JarMetadata.jar_last_modification_date', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.priority'])
         doc_list = piter.documents_list()
+        documents = []
         count += 1
+
         print '[%d:%d] %s||%s: %d versions' % (count, total_projects, p.group_id(), p.artifact_id(), len(doc_list))
 
         for d in doc_list:
@@ -72,7 +74,15 @@ def main():
 
             doc_results['Counters'] = doc_array_count.get_series()
             doc_results['SecurityBugs'] = sec_instances
-            results.append(doc_results)
+            documents.append(doc_results)
+
+        key = '%s||%s' % (p.group_id(), p.artifact_id())
+        results[key] = {'group_id' : p.group_id(),
+                        'artifact_id' : p.artifact_id(),
+                        'version_count' : len(doc_list),
+                        'versions' : documents}
+
+        print results
 
     save_to_file('project_counters.json', json.dumps(results))
 

### 2013-01-17 docs/msr.tex
added table with descriptive statistics
fix: median is now the median not the index
simplified table data
small steps in writing.

@@
 Athens University of Economics and Business\\
-Email: \{dimitro, bkarak, gousiosg, louridas, dds\}@aueb.gr}
+Email: \{dimitro, bkarak, louridas, dds\}@aueb.gr}
 \and
@@
 \begin{IEEEkeywords}
-Software Vulnerabilities, Static Analysis, Software Evolution, Maven, FindBugs.
+Software Vulnerabilities, Static Analysis, Software Evolution, Software
+Security, Maven, FindBugs.
 \end{IEEEkeywords}
@@
 security breach with unfortunate consequences in different layers, like databases,
-native code, applications, libraries and others. One of the most common
-approaches to identify software vulnerabilities is {\it static analysis}. This
-kind of analysis is performed by automated tools either on the program's source
+native code, applications, libraries and others. Despite the significant
+effort to detect and eliminate such bugs, little attention has been paid to
+study them in relation to software evolution.
+
+One of the most common approaches to identify software vulnerabilities is {\it static analysis}.
+This kind of analysis is performed by automated tools either on the program's source
 or object code and without actually executing it.
@@
 
-A snapshot of the maven repository - January 2012.
+The subject of our study was a snapshot of the maven repository. Before
+analyzing the data of the repository we performed a number of functional fits
+on the data.
+
+First, we obtained the repository snapshot (January 2012) that was previously
+used by -- et. al~\cite{}.
+
+\begin{table}
+\centering
+\caption{Descriptive Statistics Measurements for the Maven Repository}
+\label{tbl:repository}
+\begin{tabular}{l r}
+ \hline
+Projects & 17,505\\
+Versions (total) & 114,399\\
+Min & 1\\
+Max & 337\\
+Mean & 6.54\\
+Median & 3\\
+Range & 336\\
+1$^{st}$ Quartile & 1\\
+3$^{rd}$ Quartile & 8\\
+\hline
+\end{tabular}
+\end{table}
 

### 2013-01-18 docs/msr.tex
more on the introduction.

@@
 native code, applications, libraries and others. Despite the significant
-effort to detect and eliminate such bugs, little attention has been paid to
-study them in relation to software evolution.
+effort to detect and eliminate such bugs~\cite{SZ12}, little attention has been paid to
+study them in relation to software evolution~\cite{L96, LRWPT97}. In this paper we present how we
+used a large software ecosystem to analyze how evolving software packages are
+related to the different types of software vulnerabilities.
 
-One of the most common approaches to identify software vulnerabilities is {\it static analysis}.
-This kind of analysis is performed by automated tools either on the program's source
-or object code and without actually executing it.
+One of the most common approaches to identify software vulnerabilities is
+{\it static analysis}~\cite{CW07}. This kind of analysis is performed by automated tools
+either on the program's source or object code and without actually executing
+it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
+an effective static analysis tool that has already been used in
+research~\cite{AP10, HP07}. Specifically, we ran FindBugs on all the project
+versions of all the projects that exist in the Maven repoistory (280GB of
+data). Then we observed the changes that involved the security bugs per project
+version.
 

### 2013-01-19 docs/msr.tex
more content

@@
 research~\cite{AP10, HP07}. Specifically, we ran FindBugs on all the project
-versions of all the projects that exist in the Maven repoistory (280GB of
-data). Then we observed the changes that involved the security bugs per project
-version.
+versions of all the projects that exist in the Maven repoistory (265GB of
+data). Then we observed the changes that involved the security bugs and their
+characteristics, per project version.
+
+We chose to focus our study on the security-related bugs rather than other
+software bugs for a number of reasons.
 

### 2013-01-21 docs/msr.tex
intro draft

--- 2013-01-18 docs/msr.tex
@@
 
-A security-related bug is a programming error that introduces a potentially
-exploitable weakness into a computer system. This weakness could lead to a
+A security bug is a programming error that introduces a potentially
+exploitable weakness into a computer system~\cite{SSL12}. This weakness could lead to a
 security breach with unfortunate consequences in different layers, like databases,
@@
 One of the most common approaches to identify software vulnerabilities is
-{\it static analysis}~\cite{CW07}. This kind of analysis is performed by automated tools
-either on the program's source or object code and without actually executing
+{\it static analysis}~\cite{CW07}. This kind of analysis involves the
+inspection of the program's source or object code without executing
 it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
-an effective static analysis tool that has already been used in
+a popular static analysis tool that has already been used in
 research~\cite{AP10, HP07}. Specifically, we ran FindBugs on all the project
-versions of all the projects that exist in the Maven repoistory (280GB of
-data). Then we observed the changes that involved the security bugs per project
-version.
+versions of all the projects that exist in the Maven\footnote{\url{http://maven.apache.org/}}
+repository (approximately 265GB of data). Then we observed the changes that
+involved the security bugs and their characteristics.
 
-Cite this~\cite{MNN11}.
+We chose to focus our study on the security bugs rather than other
+software bugs because compared to the other software bugs,
+security bugs have a distinct feature: they are critical. Specifically, a software bug can
+lead to a mulfunction of a software application that runs under specific
+requirements but a security bug can allow a malicious user to alter the
+execution of the entire application. In this case, such bugs could span a wide range
+of security and privacy issues, like viewing sensitive information, the destruction or
+modification of sensitive data, denial of service and others.
+Hence, one of the basic pursuits in every new software release should be the
+mitigation of such bugs.
 
-\section{Related Work}
+The main contributions of this research are:
 
-Cite this~\cite{ZAH11}.
+\begin{itemize}
+	\item the analysis of how security bugs evolve in time. To achieve
+this, we inspect every project per version.
+	\item the relation of security bugs to the component's size.
+	\item bug persistense between versions.
+	\item the correlation of security bugs with other bug categories.
+	\item the relation of dependencies and security bugs.
+\end{itemize}
+
+In the rest of this paper we
+describe the processing of our data and our experiment (Section \ref{sec:meth}),
+present and discuss the results we obtained (Section \ref{sec:res},
+outline related work (Section \ref{sec:rel}),
+and end up with an conclusion and directions for future work (Section \ref{sec:con}).
 
@@
 
-\section{Conclusion}
+\section{Related Work}
+\label{sec:rel}
+
+Cite this~\cite{ZAH11} and this~\cite{MNN11}.
+
+\section{Conclusions and Future Work}
 \label{sec:con}

### 2013-01-21 docs/msr.tex
minor change - one bib entry
started related work

@@
 repository (approximately 265GB of data). Then we observed the changes that
-involved the security bugs and their characteristics.
+involved the security bugs and their characteristics. This research builds upon
+our earlier work on the topic~\cite{MGS12}.
 
@@
 	\item the correlation of security bugs with other bug categories.
-	\item the relation of dependencies and security bugs.
+	\item the relation of software dependencies and security bugs.
 \end{itemize}
@@
 
+There are noumerous methods for mining software repositories in the context
+of software evolution~\cite{KCM07}. In this section we focus on the ones
+that highlight the relationship between software bugs and evolution.
+
 Cite this~\cite{ZAH11} and this~\cite{MNN11}.
@@
 \label{sec:con}
-The conclusion goes here.
+
+Our work could (?) aid bug-prediction models.
 

### 2013-01-23 analysis/repo-statistics/build_dep_graph.py
added build_dep_graph.py

@@ -1,0 +1,45 @@
+import json
+
+from helpers.mongo_helper import MongoDocumentIterator
+from helpers.data_helper import ArrayCount, save_to_file
+
+#
+# This script generates the "data/projects.json", which is a json dict (object)
+# with the following structure {<group_id>||<artifact_id> : version_count}
+#
+
+__author__ = "Vassilios Karakoidas (vassilios.karakoidas@gmail.com)"
+
+def main():
+    results = {}
+    miter = MongoDocumentIterator(fields=['JarMetadata'])
+
+    print 'Found %d Documents' % (miter.total(),)
+
+    while miter.has_next():
+        d = miter.next()
+
+        if d is not None:
+            print 'Working %d of %d' % (miter.count(), miter.total(),)
+            node_key = '%s||%s||%s' % (d['JarMetadata']['group_id'], d['JarMetadata']['artifact_id'], d['JarMetadata']['version'])
+
+            deps = []
+
+            for dep in d['JarMetadata']['dependencies']:
+                if isinstance(dep, dict):
+                    dep_group_id = dep['groupId']
+                    dep_artifact_id = dep['artifactId']
+                    dep_version = dep.get('version', None)
+
+                    if dep_version is None:
+                        deps.append('%s||%s' % (dep_group_id, dep_artifact_id))
+                    else:
+                        deps.append('%s||%s||%s' % (dep_group_id, dep_artifact_id, dep_version))
+
+            results[node_key] = deps
+
+    save_to_file('project_graph.json', json.dumps(results))
+
+
+if __name__ == "__main__":
+    main()

### 2013-01-24 analysis/repo-statistics/build_dep_graph.py
added project graph

@@ -19,24 +19,29 @@ def main():
     while miter.has_next():
         d = miter.next()
 
-        if d is not None:
-            print 'Working %d of %d' % (miter.count(), miter.total(),)
-            node_key = '%s||%s||%s' % (d['JarMetadata']['group_id'], d['JarMetadata']['artifact_id'], d['JarMetadata']['version'])
+        try:
+            if d is not None:
+                print 'Working %d of %d' % (miter.count(), miter.total(),)
+                node_key = '%s||%s||%s' % (d['JarMetadata']['group_id'], d['JarMetadata']['artifact_id'], d['JarMetadata']['version'])
+                deps = []
 
-            deps = []
+                for dep in d.get('JarMetadata', {}).get('dependencies', {}):
+                    if isinstance(dep, dict):
+                        dep_group_id = dep.get('groupId', None)
+                        dep_artifact_id = dep.get('artifactId', None)
+                        dep_version = dep.get('version', None)
 
-            for dep in d['JarMetadata']['dependencies']:
-                if isinstance(dep, dict):
-                    dep_group_id = dep['groupId']
-                    dep_artifact_id = dep['artifactId']
-                    dep_version = dep.get('version', None)
+                        if dep_group_id is None or dep_artifact_id is None:
+                            continue
 
-                    if dep_version is None:
-                        deps.append('%s||%s' % (dep_group_id, dep_artifact_id))
-                    else:
-                        deps.append('%s||%s||%s' % (dep_group_id, dep_artifact_id, dep_version))
+                        if dep_version is None:
+                            deps.append('%s||%s' % (dep_group_id, dep_artifact_id))
+                        else:
+                            deps.append('%s||%s||%s' % (dep_group_id, dep_artifact_id, dep_version))
 
-            results[node_key] = deps
+                results[node_key] = deps
+        except Exception, e:
+            print d
 
     save_to_file('project_graph.json', json.dumps(results))
 

### 2013-01-24 docs/msr.tex
more bibtex entries

@@
 effort to detect and eliminate such bugs~\cite{SZ12}, little attention has been paid to
-study them in relation to software evolution~\cite{L96, LRWPT97}. In this paper we present how we
+study them in relation to software evolution~\cite{L96, LRWPT97, IB06}. In this paper we present how we
 used a large software ecosystem to analyze how evolving software packages are
@@
 of software evolution~\cite{KCM07}. In this section we focus on the ones
-that highlight the relationship between software bugs and evolution.
+that highlight the relationship between software bugs and evolution. The key
+idea behind this concept is typically similar to ours: the combination of
+information like bug decriptions, documentation and others with the information
+retrieved from either the source or object code of a project version.
 

### 2013-01-26 docs/msr.tex
added two approaches in the related work section

@@
 of software evolution~\cite{KCM07}. In this section we focus on the ones
-that highlight the relationship between software bugs and evolution. The key
-idea behind this concept is typically similar to ours: the combination of
-information like bug decriptions, documentation and others with the information
-retrieved from either the source or object code of a project version.
+that highlight the relationship between software bugs and evolution and try to
+extract useful conclusions. The key idea behind this concept is
+similar to ours: the combination of information like bug decriptions,
+documentation and others with the information retrieved from either the source
+or object code of a project version.
+
+{\it Refactoring identification} through software evolution is an approach used to
+relate refactorings with software bugs. Weibgerber et al. found that a high
+ratio of refactorings is usually followed by an increasing ratio of bug
+reports~\cite{WD06}. In addition, they found that software bugs are sometimes introduced
+after an incomplete refactoring~\cite{GW05}.
+Ratzinger et al.~\cite{RSG08} found that the number of bugs decreases, when the number of
+refactorings increases. Finally, Kim M. et al.~\cite{KCK11} showed that {\sc api}-level
+refactorings aid bug fixes.
+
+Using {\it micro patterns} is an approach proposed by Kim et al.~\cite{KPW06}
+to detect bug-prone patterns among source code. Micro patterns describe programming
+idioms like inheritance, data management, immutability and others. The approach involved
+the examination of all revisions of three open-source projects to extract bug
+introduction rates for each pattern.
 

### 2013-01-27 docs/msr.tex
minor chnges

@@
 {\it Refactoring identification} through software evolution is an approach used to
-relate refactorings with software bugs. Weibgerber et al. found that a high
+relate refactorings with software bugs. Wei{\ss}gerber et al. found that a high
 ratio of refactorings is usually followed by an increasing ratio of bug
-reports~\cite{WD06}. In addition, they found that software bugs are sometimes introduced
+reports~\cite{WD06}. In addition, they indicated that software bugs are sometimes introduced
 after an incomplete refactoring~\cite{GW05}.
@@
 
-Using {\it micro patterns} is an approach proposed by Kim et al.~\cite{KPW06}
+Using {\it micro patterns} is a method proposed by Kim et al.~\cite{KPW06}
 to detect bug-prone patterns among source code. Micro patterns describe programming

### 2013-01-27 analysis/repo-statistics/bug_correlation.py
started the script that produces the data for the correlations between categories

@@ -1,0 +1,17 @@
+import json
+
+from helpers.data_helper import ArrayCount, save_to_file
+from helpers.mongo_helper import MongoDocumentIterator
+
+
+
+def main():
+
+miter = MongoDocumentIterator(query={''},fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.version_order', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.priority'])
+
+    print 'Found %d Documents' % (miter.total(),)
+    
+    while miter.has_next():
+
+if __name__ == "__main__":
+    main()

### 2013-01-27 analysis/repo-statistics/bug_correlation.py
now the bug instance loads all projects; cloned project_counters -> bug_correlation.py

@@ -1,17 +1,92 @@
 import json
 
-from helpers.data_helper import ArrayCount, save_to_file
-from helpers.mongo_helper import MongoDocumentIterator
-
+from helpers.data_helper import ArrayCount, save_to_file, load_projects_json
+from helpers.mongo_helper import MongoProjectIterator
 
 
 def main():
+    projects = load_projects_json()
+    results = {}
+    security_bugs = ['HRS_REQUEST_PARAMETER_TO_COOKIE',
+                     'HRS_REQUEST_PARAMETER_TO_HTTP_HEADER',
+                     'PT_ABSOLUTE_PATH_TRAVERSAL',
+                     'SQL_NONCONSTANT_STRING_PASSED_TO_EXECUTE',
+                     'SQL_PREPARED_STATEMENT_GENERATED_FROM_NONCONSTANT_STRING',
+                     'XSS_REQUEST_PARAMETER_TO_JSP_WRITER',
+                     'XSS_REQUEST_PARAMETER_TO_SEND_ERROR',
+                     'XSS_REQUEST_PARAMETER_TO_SERVLET_WRITER']
 
-miter = MongoDocumentIterator(query={''},fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.version_order', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.priority'])
+    total_projects = len(projects)
+    count = 0
 
-    print 'Found %d Documents' % (miter.total(),)
-    
-    while miter.has_next():
+    print 'Found %d Projects' % (total_projects,)
+
+    for p in projects:
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.jar_size', 'JarMetadata.version_order', 'JarMetadata.jar_last_modification_date', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.priority'])
+        doc_list = piter.documents_list()
+        documents = []
+        count += 1
+
+        print '[%d:%d] %s||%s: %d versions' % (count, total_projects, p.group_id(), p.artifact_id(), len(doc_list))
+
+        for d in doc_list:
+            doc_results = {'JarMetadata': d['JarMetadata']}
[…]

### 2013-01-27 analysis/repo-statistics/bug_correlation.py
removed security bug array

@@ -7,14 +7,6 @@ from helpers.mongo_helper import MongoProjectIterator
 def main():
     projects = load_projects_json()
     results = {}
-    security_bugs = ['HRS_REQUEST_PARAMETER_TO_COOKIE',
-                     'HRS_REQUEST_PARAMETER_TO_HTTP_HEADER',
-                     'PT_ABSOLUTE_PATH_TRAVERSAL',
-                     'SQL_NONCONSTANT_STRING_PASSED_TO_EXECUTE',
-                     'SQL_PREPARED_STATEMENT_GENERATED_FROM_NONCONSTANT_STRING',
-                     'XSS_REQUEST_PARAMETER_TO_JSP_WRITER',
-                     'XSS_REQUEST_PARAMETER_TO_SEND_ERROR',
-                     'XSS_REQUEST_PARAMETER_TO_SERVLET_WRITER']
 
     total_projects = len(projects)
     count = 0
@@ -22,7 +14,7 @@ def main():
     print 'Found %d Projects' % (total_projects,)
 
     for p in projects:
-        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.jar_size', 'JarMetadata.version_order', 'JarMetadata.jar_last_modification_date', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.priority'])
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.version_order', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.priority'])
         doc_list = piter.documents_list()
         documents = []
         count += 1
@@ -66,10 +58,6 @@ def main():
                         print 'Invalid Type!'
                         continue
 
-                    if bug_type in security_bugs:
-                        doc_array_count.incr('SECURITY_HIGH')
-                    else:
-                        doc_array_count.incr('SECURITY_LOW')
                 else:
                     doc_array_count.incr(bug_category)
 

### 2013-01-27 analysis/repo-statistics/bug_correlation.py
finalised bug correlation script

@@ -7,7 +7,6 @@ from helpers.mongo_helper import MongoProjectIterator
 def main():
     projects = load_projects_json()
     results = {}
-
     total_projects = len(projects)
     count = 0
 
@@ -16,16 +15,13 @@ def main():
     for p in projects:
         piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.version_order', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.priority'])
         doc_list = piter.documents_list()
-        documents = []
+        proj_array_count = ArrayCount()
+        bug_list = []
         count += 1
 
         print '[%d:%d] %s||%s: %d versions' % (count, total_projects, p.group_id(), p.artifact_id(), len(doc_list))
 
         for d in doc_list:
-            doc_results = {'JarMetadata': d['JarMetadata']}
-            doc_array_count = ArrayCount()
-            sec_instances = []
-
             for bi in d.get('BugCollection', {}).get('BugInstance', []):
                 if not isinstance(bi, dict):
                     print bi
@@ -33,47 +29,32 @@ def main():
 
                 bug_category = bi.get('category', '')
 
+                # get class names
+                classnames = bi['Class']
+                classresults = []
+
+                if isinstance(classnames, list):
+                    for c in classnames:
+                        classresults.append(c.get('classname', 'NotSet'))
+                elif isinstance(classnames, dict):
+                    classresults.append(classnames.get('classname', 'NotSet'))
+
+                type = bi['type']
+                signatures = ['%s||%s||%s' % (bug_category, type, c) for c in classresults]
+
                 # method
-                if bug_category == 'SECURITY' or bug_category == 'MALICIOUS_CODE':
-                    classnames = bi['Class']
-                    classresults = []
+                for s in signatures:
+                    if s not in bug_list:
+                        bug_list.append(s)
 
-                    if isinstance(classnames, list):
-                        for c in classnames:
-                            classresults.append(c.get('classname', 'NotSet'))
-                    elif isinstance(classnames, dict):
-                        classresults.append(classnames.get('classname', 'NotSet'))
+                        if bug_category == 'SECURITY' or bug_category == 'MALICIOUS_CODE':
+                            proj_array_count.incr('SECURITY')
+                        else:
[…]

### 2013-01-27 analysis/repo-statistics/helpers/data_helper.py
renamed projects.json -> project_version.json

@@ -48,7 +48,7 @@ def load_projects_json():
         return []
 
     project_list = []
-    fp = open('data/projects.json', 'r')
+    fp = open('data/project_versions.json', 'r')
     prj_json = json.load(fp)
     fp.close()
 

### 2013-01-27 analysis/repo-statistics/bug_correlation.py
fixed print out

@@ -24,7 +24,7 @@ def main():
         for d in doc_list:
             for bi in d.get('BugCollection', {}).get('BugInstance', []):
                 if not isinstance(bi, dict):
-                    print bi
+                    print 'Invalid BugInstance (%s)' % (bi,)
                     continue
 
                 bug_category = bi.get('category', '')

### 2013-01-27 analysis/repo-statistics/bug_correlation.py
added total counters also

@@ -24,7 +24,7 @@ def main():
         for d in doc_list:
             for bi in d.get('BugCollection', {}).get('BugInstance', []):
                 if not isinstance(bi, dict):
-                    print 'Invalid BugInstance (%s)' % (bi,)
+                    #print 'Invalid BugInstance (%s)' % (bi,)
                     continue
 
                 bug_category = bi.get('category', '')
@@ -52,6 +52,13 @@ def main():
                         else:
                             proj_array_count.incr(bug_category)
 
+                    if bug_category == 'SECURITY' or bug_category == 'MALICIOUS_CODE':
+                        proj_array_count.incr('TOTAL_SECURITY')
+                    else:
+                        proj_array_count.incr('TOTAL_' + bug_category)
+
+
+        print proj_array_count.get_series()
         results['%s||%s' % (p.group_id(), p.artifact_id())] = proj_array_count.get_series()
 
     save_to_file('bug_correlation_counters.json', json.dumps(results))

### 2013-01-27 analysis/repo-statistics/helpers/data_helper.py
simplified project_counter scripts; now malicious_code and security are calculated as one category; security bugs are not calculated here

@@ -7,8 +7,8 @@ class ArrayCount(object):
         super(ArrayCount, self).__init__()
         self.__arrayDict = {}
 
-    def incr(self, item):
-        self.__arrayDict[item] = self.__arrayDict.get(item, 0) + 1
+    def incr(self, item, delta=1):
+        self.__arrayDict[item] = self.__arrayDict.get(item, 0) + delta
 
     def get_series(self):
         return self.__arrayDict

### 2013-01-27 analysis/repo-statistics/project_counters.py

@@ -7,21 +7,13 @@ from helpers.mongo_helper import MongoProjectIterator
 def main():
     projects = load_vuln_projects_json()
     results = {}
-    security_bugs = ['HRS_REQUEST_PARAMETER_TO_COOKIE',
-                     'HRS_REQUEST_PARAMETER_TO_HTTP_HEADER',
-                     'PT_ABSOLUTE_PATH_TRAVERSAL',
-                     'SQL_NONCONSTANT_STRING_PASSED_TO_EXECUTE',
-                     'SQL_PREPARED_STATEMENT_GENERATED_FROM_NONCONSTANT_STRING',
-                     'XSS_REQUEST_PARAMETER_TO_JSP_WRITER',
-                     'XSS_REQUEST_PARAMETER_TO_SEND_ERROR',
-                     'XSS_REQUEST_PARAMETER_TO_SERVLET_WRITER']
 
     total_projects = len(projects)
     count = 0
     print 'Found %d Projects' % (total_projects,)
 
     for p in projects:
-        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.jar_size', 'JarMetadata.version_order', 'JarMetadata.jar_last_modification_date', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.priority'])
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.jar_size', 'JarMetadata.version_order', 'JarMetadata.jar_last_modification_date', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.priority'])
         doc_list = piter.documents_list()
         documents = []
         count += 1
@@ -31,49 +23,21 @@ def main():
         for d in doc_list:
             doc_results = {'JarMetadata': d['JarMetadata']}
             doc_array_count = ArrayCount()
-            sec_instances = []
 
             for bi in d.get('BugCollection', {}).get('BugInstance', []):
                 if not isinstance(bi, dict):
                     print bi
                     continue
 
-                bug_category = bi.get('category', '')
+                bug_category = bi.get('category', None)
 
-                # method
[…]

### 2013-01-27 analysis/repo-statistics/project_counters.py
commented on debug print

@@ -46,7 +46,8 @@ def main():
                         'version_count' : len(doc_list),
                         'versions' : documents}
 
-        print results
+        # TODO: uncomment this to print out each entry
+        #print results
 
     save_to_file('project_counters.json', json.dumps(results))
 

### 2013-01-29 analysis/repo-statistics/build_dep_graph.py
updated project_graph

@@ -1,7 +1,7 @@
 import json
 
 from helpers.mongo_helper import MongoDocumentIterator
-from helpers.data_helper import ArrayCount, save_to_file
+from helpers.data_helper import save_to_file
 
 #
 # This script generates the "data/projects.json", which is a json dict (object)
@@ -39,7 +39,7 @@ def main():
                         else:
                             deps.append('%s||%s||%s' % (dep_group_id, dep_artifact_id, dep_version))
 
-                results[node_key] = deps
+                results[node_key] = {'dependencies ' : deps, 'timestamp' : d['JarMetadata'].get('jar_last_modification_date', 0), 'version_order' : d['JarMetadata']['version_order']}
         except Exception, e:
             print d
 

### 2013-01-30 analysis/repo-statistics/bug_correlation.py
fixed problem with bug correlation script

@@ -13,7 +13,7 @@ def main():
     print 'Found %d Projects' % (total_projects,)
 
     for p in projects:
-        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.version_order', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.priority'])
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.version_order', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.Method.name', 'BugCollection.BugInstance.Field.name'])
         doc_list = piter.documents_list()
         proj_array_count = ArrayCount()
         bug_list = []
@@ -29,34 +29,51 @@ def main():
 
                 bug_category = bi.get('category', '')
 
-                # get class names
+                # create signature
+                signatures_ids = []
                 classnames = bi['Class']
-                classresults = []
 
                 if isinstance(classnames, list):
                     for c in classnames:
-                        classresults.append(c.get('classname', 'NotSet'))
+                        signatures_ids.append(c.get('classname', 'NotSet'))
                 elif isinstance(classnames, dict):
-                    classresults.append(classnames.get('classname', 'NotSet'))
+                    signatures_ids.append(classnames.get('classname', 'NotSet'))
+
+                # methods
+                methodnames = bi.get('Method', {})
+
+                if isinstance(methodnames, list):
+                    for m in methodnames:
+                        signatures_ids.append(m.get('name', 'NotSet'))
+                elif isinstance(methodnames, dict):
+                    signatures_ids.append(methodnames.get('name', 'NotSet'))
+
+                # fields
+                fieldnames = bi.get('Field', {})
+                if isinstance(fieldnames, list):
+                    for f in fieldnames:
+                        signatures_ids.append(f.get('name', 'NotSet'))
+                elif isinstance(fieldnames, dict):
+                    signatures_ids.append(fieldnames.get('name', 'NotSet'))
 
                 type = bi['type']
-                signatures = ['%s||%s||%s' % (bug_category, type, c) for c in classresults]
[…]

### 2013-01-30 docs/msr.tex
more on the related work

@@
 
-Using {\it micro patterns} is a method proposed by Kim et al.~\cite{KPW06}
+Using {\it Micro patterns} is a method proposed by Kim et al.~\cite{KPW06}
 to detect bug-prone patterns among source code. Micro patterns describe programming
@@
 introduction rates for each pattern.
+
+{\it Querying techniques} are used to answer a broad range of questions
+regarding the evolution history of a project~\cite{HG05}. Bhattacharya et al.~\cite{BN11}
+proposed a framework that is based upon recursively enumerable languages. The
+framework can correlate software bugs with developers in various ways.
+For instanse, return the list of bugs fixed by a specific developer.
+Fischer et al.~\cite{FPG03} proposed an approach for
+populating a release history database that combines code information
+with bug tracking data. In this way, a developer can couple files that contain
+common bugs, estimate code maturity with respect to the bugs and others.
 

### 2013-01-30 analysis/repo-statistics/bug_counter.py
removed bug counter

@@ -1,39 +1,0 @@
-from helpers.mongo_helper import MongoDocumentIterator
-
-__author__ = 'Vassilios Karakoidas (vassilios.karakoidas@gmail.com)'
-
-
-def main():
-    # miter = MongoDocumentIterator(query={'BugCollection.BugInstance.category':'SECURITY'}, fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version','BugCollection.BugInstance.category', 'BugCollection.BugInstance.type'])
-    # miter = MongoDocumentIterator(query={'$or': [{'BugCollection.BugInstance.category':'MALICIOUS_CODE'}, {'BugCollection.BugInstance.category':'SECURITY'}]}, fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version','BugCollection.BugInstance.category', 'BugCollection.BugInstance.type'])
-
-    miter = MongoDocumentIterator(query={'BugCollection.BugInstance.category':'MALICIOUS_CODE'},fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version','BugCollection.BugInstance.category', 'BugCollection.BugInstance.type'])
-
-    print 'Found %d Documents' % (miter.total(),)
-
-    sec_bug_counter = 0
-    mal_bug_counter = 0
-    total_counter = 0
-    
-    while miter.has_next():
-        d = miter.next()
-
-        for bi in d.get('BugCollection', {}).get('BugInstance', []):
-            total_counter += 1
-
-            if not isinstance(bi, dict):
-                print bi
-                continue
-
-            #if bi.get('category', '') == 'SECURITY':
-                #sec_bug_counter += 1
-                
-            if bi.get('category', '') == 'MALICIOUS_CODE':
-                mal_bug_counter += 1
-
-        #print '%s/%s-%s.jar: sec: %d mal: %d (total:%d)' % (d['JarMetadata']['group_id'], d['JarMetadata']['artifact_id'],             d['JarMetadata']['version'], sec_bug_counter, mal_bug_counter, total_counter)
-    print total_counter
-    print mal_bug_counter
-        
-if __name__ == "__main__":
-    main()

### 2013-01-30 analysis/repo-statistics/bug_correlation.py
added bug correlation json

@@ -59,8 +59,6 @@ def main():
                 type = bi['type']
                 signature = '%s||%s||%s' % (bug_category, type, '||'.join(signatures_ids))
 
-                print signature
-
                 # method
                 if signature not in bug_list:
                     bug_list.append(signature)

### 2013-01-30 docs/msr.tex
first draft of related work ready

@@
 a popular static analysis tool that has already been used in
-research~\cite{AP10, HP07}. Specifically, we ran FindBugs on all the project
+research~\cite{AP10, HP07, HP04}. Specifically, we ran FindBugs on all the project
 versions of all the projects that exist in the Maven\footnote{\url{http://maven.apache.org/}}
@@
 after an incomplete refactoring~\cite{GW05}.
-Ratzinger et al.~\cite{RSG08} found that the number of bugs decreases, when the number of
-refactorings increases. Finally, Kim M. et al.~\cite{KCK11} showed that {\sc api}-level
+Ratzinger et al.~\cite{RSG08} showed that the number of bugs decreases, when the number of
+refactorings increases. Finally, Kim M. et al.~\cite{KCK11} indicated that {\sc api}-level
 refactorings aid bug fixes.
 
-Using {\it Micro patterns} is a method proposed by Kim et al.~\cite{KPW06}
+Using {\it micro patterns} is a method proposed by Kim et al.~\cite{KPW06}
 to detect bug-prone patterns among source code. Micro patterns describe programming
@@
 the examination of all revisions of three open-source projects to extract bug
-introduction rates for each pattern.
+introduction rates for each pattern. Gil et al.~\cite{GM05} analyzed the
+prevalence of micro patterns across five Sun {\sc jdk} versions to conclude that
+pattern prevalence tends to be the same in software collections.
 
 {\it Querying techniques} are used to answer a broad range of questions
-regarding the evolution history of a project~\cite{HG05}. Bhattacharya et al.~\cite{BN11}
-proposed a framework that is based upon recursively enumerable languages. The
-framework can correlate software bugs with developers in various ways.
-For instanse, return the list of bugs fixed by a specific developer.
-Fischer et al.~\cite{FPG03} proposed an approach for
-populating a release history database that combines code information
-with bug tracking data. In this way, a developer can couple files that contain
-common bugs, estimate code maturity with respect to the bugs and others.
+regarding the evolution history of a project~\cite{HG05}. Bhattacharya et
+al.~\cite{BN11, B11} proposed a framework that is based upon
+recursively enumerable languages. The framework can correlate software
+bugs with developers in various ways. For instanse, return the list of
+bugs fixed by a specific developer. Fischer et al.~\cite{FPG03} proposed
+an approach for populating a release history database that combines code
+information with bug tracking data. In this way, a developer can couple files
+that contain common bugs, estimate code maturity with respect to the bugs
+and others. The ``Ultimate Debian Database''~\cite{NZ10} is an {\sc sql}-based
+framework that integrates information about the Debian project from various
+sources to answer queries related to software bugs and source code.
 
-Cite this~\cite{ZAH11} and this~\cite{MNN11}.
+D'Ambros et al. have used {\it bug history analysis} to detect
+the critical components of a project~\cite{D08}. This is done by using an
+evolutionary meta-model~\cite{DL08}. The same approach was
+also used by Zimmermann et al.~\cite{ZNA08} to check the correlation
+of bugs with software properties like code complexity, process quality and others
+and predict future properties.
+
+Contrary to the above, our work focuses on the subset of security bugs.
+Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
+the evolution of software defects by examining six major versions of Firefox.
+To achieve this they created a database schema that contained information
+coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
+list,~\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
+Bugzilla entries and others. Their findings indicated that security bugs are
+persistent over time. They also showed that there are many web users that use
+old versions of Firefox, meaning that old attacks will continue to work.
+Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
+security bugs with performance bugs. This was also done by analyzing the project's
+Bugzilla. Their research showed that security bugs require more experienced developers
+to be fixed. In addittion, security bug fixes are more complex than the
+fixes of performance and other bugs.
+Shahzad et al.~\cite{SSL12} analyzed large sets of vulnerability data-sets to observe
+various features of the vulnerabilities that they considered critical. Such features
+were the functionality and the criticality of the defects. Their analysis
+included the observation of vulnerability disclosures, the behavior of
+hackers in releasing exploits for vulnerabilities, patching and others. In
+their findings they highlighted the most exploited defects and showed that
+the percentage of remotely exploitable vulnerabilities has gradually increased
+over the years.
 
@@
 
-Our work could (?) aid bug-prediction models.
+Our work could (?) aid bug-prediction models in the same way as~\cite{BN11}.
 

### 2013-02-01 analysis/repo-statistics/create_version_count_graph.py
added version_count dat

@@ -1,0 +1,21 @@
+import StringIO
+from helpers.data_helper import load_projects_json, ArrayCount, save_to_file
+
+
+def main():
+    statistics = ArrayCount()
+
+    for p in load_projects_json():
+        statistics.incr(p.version_count())
+
+    strio = StringIO.StringIO()
+
+    for (k, v) in statistics.get_series().iteritems():
+        strio.write(str(k) + " - " + str(v) + "\n")
+
+    save_to_file('version_count.dat', strio.getvalue())
+
+
+if __name__ == "__main__":
+    main()
+

### 2013-02-01 analysis/repo-statistics/create_version_count_graph.py
added version_count.dat

@@ -11,7 +11,7 @@ def main():
     strio = StringIO.StringIO()
 
     for (k, v) in statistics.get_series().iteritems():
-        strio.write(str(k) + " - " + str(v) + "\n")
+        strio.write(str(k) + "," + str(v) + "\n")
 
     save_to_file('version_count.dat', strio.getvalue())
 

### 2013-02-01 analysis/repo-statistics/bug_correlation_calc.R
add correlation calculation

@@ -1,0 +1,12 @@
+# Calculates pairwise correlations from the data in
+# data/bug_correlation_counters.csv, which is produced
+# by bug_correlation_tab.py
+
+bug.counts <- read.csv("data/bug_correlation_counters.csv")
+
+for (i in (2:(ncol(bug.counts) - 1))) {
+  for (j in ((i + 1):(ncol(bug.counts) - 1))) {
+    print(paste(colnames(bug.counts)[i], ":", colnames(bug.counts[j])))
+    print(cor.test(bug.counts[, i], bug.counts[, j]))
+  }
+}

### 2013-02-01 docs/msr.tex
added version count graph
added categorisation from maven (table)

@@
 \author{
-\IEEEauthorblockN{Dimitris Mitropoulos \and Vassilios Karakoidas \and Panos Louridas \and Diomidis Spinellis}
+\IEEEauthorblockN{Dimitris Mitropoulos Vassilios Karakoidas Panos Louridas Diomidis Spinellis}
 \IEEEauthorblockA{Department of Management Science and Technology\\
@@
 
+\begin{figure*}
+	\centering
+	\includegraphics[scale=0.6]{version_count.pdf}
+	\caption{Distribution of version count amongst project population}
+	\label{fig:version-count}
+\end{figure*}
+
 \begin{table}
@@
 \begin{tabular}{l r}
+\hline
+Measurement & Value\\
  \hline
@@
 \label{sec:res}
+
+\subsection{Bug Categorisation and Overview}
+\label{sec:bug}
+
+\begin{table}
+\centering
+\caption{Bug Categorisation according to FindBugs}
+\label{tbl:bug-categorisation}
+\begin{tabular}{l r}
+ \hline
+Category & Description\\
+\hline
+Bad Practice & \\
+Correctness & \\
+Experimental & \\
+Internationalisation & \\
+Multi-Threaded Correctness & \\
+Performance & \\
+Style & \\
+Security & \\
+\hline
+\end{tabular}
+\end{table}
 

### 2013-02-01 analysis/repo-statistics/helpers/data_helper.py
added percent graph

@@ -63,3 +63,4 @@ def load_projects_json():
 
     return project_list
 
+

### 2013-02-01 docs/msr.tex
added percent graph
category description

@@
 
-\subsection{Bug Categorisation and Overview}
-\label{sec:bug}
+\subsection{Overview and Initial Results}
+\label{sec:overview}
+
+\begin{figure*}
+	\centering
+	\includegraphics[scale=0.6]{bug_percent}
+	\caption{Bug Percentage in Maven Repository}
+	\label{fig:bug-percentage}
+\end{figure*}
 
@@
 \centering
-\caption{Bug Categorisation according to FindBugs}
+\caption{Bug categorisation according to FindBugs}
 \label{tbl:bug-categorisation}
-\begin{tabular}{l r}
+\begin{tabular}{l p{15em}}
 \hline
@@
 \hline
-Bad Practice & \\
-Correctness & \\
+Bad Practice & Violations of recommended and essential
+coding practice. \\
+Correctness & Involves coding mistakes resulting in code
+that was probably not what the developer intended. \\
 Experimental & \\
-Internationalisation & \\
-Multi-Threaded Correctness & \\
-Performance & \\
-Style & \\
-Security & \\
+Internationalisation & Indicates the use of non-localized methods \\
+Multi-Threaded Correctness & Thread synchronization issues. \\
+Performance & Involves inefficient memory usageallocation, usage 
+of non-static classes \\
+Style & Code that is confusing, or
+written in a way that leads to errors.\\
+Security & Contains two subcategories, namely: {\it Security} and {\it
+Malicious Code}. Involves code that could lead to security breach. \\
 \hline

### 2013-02-01 docs/msr.tex
almost fixed authors

--- 2013-02-01 docs/msr.tex
@@
 
-\hyphenation{op-tical net-works semi-conduc-tor}
-
 \begin{document}
@@
 \author{
-\IEEEauthorblockN{Dimitris Mitropoulos Vassilios Karakoidas Panos Louridas Diomidis Spinellis}
+\IEEEauthorblockN{Dimitris Mitropoulos}
 \IEEEauthorblockA{Department of Management Science and Technology\\
 Athens University of Economics and Business\\
-Email: \{dimitro, bkarak, louridas, dds\}@aueb.gr}
+Email: dimitro@aueb.gr}
+\and
+\IEEEauthorblockN{Vassilios Karakoidas}
+\IEEEauthorblockA{Department of Management Science and Technology\\
+Athens University of Economics and Business\\
+Email: bkarak@aueb.gr}\\
+\and
+\IEEEauthorblockN{Panos Louridas}
+\IEEEauthorblockA{Department of Management Science and Technology\\
+Athens University of Economics and Business\\
+Email: louridas@aueb.gr}
+\and
+\IEEEauthorblockN{Diomidis Spinellis}
+\IEEEauthorblockA{Department of Management Science and Technology\\
+Athens University of Economics and Business\\
+Email: dds@aueb.gr}
 \and
@@
 \IEEEauthorblockA{Department of Software and Computer Technology\\
-Delft University of Technology \\
+Delft University of Technology\\
 Email: G.Gousios@tudelft.nl}
@@
 \centering
-\caption{Bug Categorisation according to FindBugs}
+\caption{Bug categorisation according to FindBugs}
 \label{tbl:bug-categorisation}

### 2013-02-01 docs/msr.tex

@@
 \label{tbl:bug-categorisation}
-\begin{tabular}{l r}
+\begin{tabular}{l p{15em}}
 \hline

### 2013-02-01 analysis/repo-statistics/bug_correlation_calc.py
add python implementation

@@ -1,0 +1,22 @@
+# Calculates pairwise correlations from the data in
+# data/bug_correlation_counters.json
+
+
+import json
+import pandas as pd
+import numpy as np
+import scipy.stats as st
+from itertools import izip
+import sys
+
+with open("data/bug_correlation_counters.json") as infile:
+    json_input = json.load(infile)
+
+data = pd.DataFrame(json_input).T
+
+for i in xrange(len(data.columns) - 1):
+    for j in xrange(i + 1, (len(data.columns) - 1)):
+        frm = data.ix[:, [i, j]].dropna()
+        (corr, pvalue) = st.pearsonr(frm.ix[:, 0], frm.ix[:, 1])
+        print data.columns[i], data.columns[j], corr, pvalue
+

### 2013-02-01 docs/msr.tex
tighten up authors (no effect)
description of categories ready

@@
 Athens University of Economics and Business\\
-Email: dimitro@aueb.gr}
+Email: dimitro@aueb.gr}\\
 \and
@@
 \and
+\IEEEauthorblockN{Georgios Gousios}
+\IEEEauthorblockA{Department of Software and Computer Technology\\
+Delft University of Technology\\
+Email: G.Gousios@tudelft.nl}\\
+\and
 \IEEEauthorblockN{Panos Louridas}
@@
 Athens University of Economics and Business\\
-Email: louridas@aueb.gr}
+Email: louridas@aueb.gr}\\
 \and
@@
 Athens University of Economics and Business\\
-Email: dds@aueb.gr}
-\and
-\IEEEauthorblockN{Georgios Gousios}
-\IEEEauthorblockA{Department of Software and Computer Technology\\
-Delft University of Technology\\
-Email: G.Gousios@tudelft.nl}
-}
+Email: dds@aueb.gr}}
 
@@
 	\includegraphics[scale=0.6]{version_count.pdf}
-	\caption{Distribution of version count amongst project population}
+	\caption{Distribution of version count among project population}
 	\label{fig:version-count}
@@
 that was probably not what the developer intended. \\
-Experimental & \\
+Experimental & Includes unsatisfied obligations. For instance,
+forgetting to close a file \\
 Internationalisation & Indicates the use of non-localized methods \\
@@
 \end{table}
+
+\subsection{Analysis}
+\label{sec:analysis}
 

### 2013-02-02 docs/msr.tex
more on the introduction plus the subsubsections of the Analysis section

@@
 security bugs have a distinct feature: they are critical. Specifically, a software bug can
-lead to a mulfunction of a software application that runs under specific
+lead to a mulfunction of a software artifact that runs under specific
 requirements but a security bug can allow a malicious user to alter the
@@
 \begin{itemize}
-	\item the analysis of how security bugs evolve in time. To achieve
-this, we inspect every project per version.
-	\item the relation of security bugs to the component's size.
-	\item bug persistense between versions.
-	\item the correlation of security bugs with other bug categories.
-	\item the relation of software dependencies and security bugs.
+	\item The analysis of how security bugs evolve in time. To achieve
+this, we inspect every project per version. Our hypothesis is that security
+bugs must decrease as a project evolves since they are critical and developers
+should eliminate them.
+	\item The relation of security bugs to the artifact's size.  Here, size is
+defined in terms of bytecode.
+	\item Security bug persistense between versions. We check if specific bugs are
+eliminated between versions.
+	\item The correlation of security bugs with other bug categories. We
+present how such bugs are correlated with bugs that have to do with
+performance, coding practices and others.
+	\item The relation of software dependencies and security bugs. Our
+hypothesis is that an artifact that is a dependency of many other artifacts
+should have a low rate of security bugs. 
 \end{itemize}
@@
 
+\subsubsection{How Security Bugs Evolve Over Time}
+
+\subsubsection{The Relation of Defects with the size of an Artifact}
+
+\subsubsection{Persistense of Security Bugs}
+
+\subsubsection{Security Bugs {\sc vs} Other Bug Categories}
+
+\subsubsection{Critical Artifacts and their Defects}
+
 \section{Related Work}

### 2013-02-03 docs/msr.tex
more content

@@
 
-First, we obtained the repository snapshot (January 2012) that was previously
-used by -- et. al~\cite{}.
+First, we obtained a snapshot (January 2012) of the maven repository and
+handled it locally to retreive a list of all the names of the artifacts that existed in the
+repository.
 
@@
 \label{sec:exp}
+
+Our experiment involved three entities: a Rabbit{\sc mq}
+server,\footnote{\url{http://www.rabbitmq.com/}} a Python pool of worker
+processes and a mongo{\sc db}.\footnote{\url{http://www.mongodb.org/}}
 

### 2013-02-03 docs/msr.tex
added motivation on the intro section

@@
 
+The motivation behind our work is to validate if programmers tend to care for
+such high-risk bugs when they release a new version of their software. In
+addition, we want to investigate other critical aspects associated with such
+vulnerabilities. For instance, we want to elaborate more on the relation of security
+bugs not only with performance bugs (as Zaman et al.~\cite{ZAH11} have already
+did) but also with other bug categories. In the same manner, we want to check
+if the relation between an artifact's size and its' software bugs applies 
+to security bugs (citation needed). Finally, the structure of the Maven ecosystem,
+gives us the oportunity to see if artifacts that is a dependency to a high
+number of other artifacts contains a high rate of security bugs. In this case
+we can strenghten the relationship between Linus' Law and software security as
+Meneely et al. have already showed~\cite{MW10}.
+
 The main contributions of this research are:
@@
 should eliminate them.
-	\item The relation of security bugs to the artifact's size.  Here, size is
+	\item We show evidence of the relation between security bugs and the artifact's size.  Here, size is
 defined in terms of bytecode.
-	\item Security bug persistense between versions. We check if specific bugs are
-eliminated between versions.
+	\item Security bug persistense between versions. We show evidence that specific bugs are
+not eliminated between versions.
 	\item The correlation of security bugs with other bug categories. We
-present how such bugs are correlated with bugs that have to do with
+show evidence that such bugs are correlated with bugs that have to do with
 performance, coding practices and others.

### 2013-02-03 docs/msr.tex
Introduction: some changes - fixes

@@
 used a large software ecosystem to analyze how evolving software packages are
-related to the different types of software vulnerabilities.
+related to the different types of security vulnerabilities.
 
-One of the most common approaches to identify software vulnerabilities is
+One of the most common approaches to identify security bugs is
 {\it static analysis}~\cite{CW07}. This kind of analysis involves the
@@
 We chose to focus our study on the security bugs rather than other
-software bugs because compared to the other software bugs,
-security bugs have a distinct feature: they are critical. Specifically, a software bug can
+software bugs. This is because compared to other bug categories,
+the category of security bugs has a distinct feature: it is critical. Specifically, a software bug can
 lead to a mulfunction of a software artifact that runs under specific
@@
 to security bugs (citation needed). Finally, the structure of the Maven ecosystem,
-gives us the oportunity to see if artifacts that is a dependency to a high
+gives us the oportunity to see if an artifact that is a dependency to a large
 number of other artifacts contains a high rate of security bugs. In this case
 we can strenghten the relationship between Linus' Law and software security as
-Meneely et al. have already showed~\cite{MW10}.
+Meneely et al. have already indicated~\cite{MW10}.
 
@@
 \begin{itemize}
-	\item The analysis of how security bugs evolve in time. To achieve
+	\item The analysis of how security bugs evolve over time. To achieve
 this, we inspect every project per version. Our hypothesis is that security

### 2013-02-03 docs/msr.tex
added experiment section

@@
 
-\subsection{Data Provenance and Processing}
+\subsection{Experiment}
+\label{sec:exp}
+
+Our experiment goal was to collect the metric results of the findbugs tool.
+The process involved three entities: a number of \textit{workers}, a \textit{task queue} mechanism,
+a \textit{data repository}, and the \textit{code repository}, which in our case it was the public Maven 
+repository\footnote{\url{http://mvnrepository.com}}.
+
+\begin{table}
+\centering
+\caption{Experiment software and versions}
+\label{tbl:soft-version}
+\begin{tabular}{r r r}
+\hline
+ & Software Package & version\\
+ \hline
+worker & Custom Python Script & 2.7\\
+task queue & RabbitMQ\footnote{\url{http://www.rabbitmq.com/}} & \\
+data repository & MongoDB\footnote{\url{http://www.mongodb.org/}} & \\
+code repository & Maven Repository & \\
+\hline
+\end{tabular}
+\end{table}
+
+First, we scanned the Maven repository for appropriate jars. We discuss the the jar selection process in the next 
+section. With this list we created a series of processing tasks and added them to the \textit{task queue}. Then we
+executed 25 (unix-based) workers that checked out tasks from the queue, processed the data and stored the results to the \textit{data repository}.
+
+A typical processing cycle included the following steps:
+
+\begin{enumerate}
+	\item The worker spawns,
+	\item then it requests a task from the queue,
+	\begin{enumerate}
+		\item the tasks contains the {\sc jar}, which is typically a project version and it is downloaded,
+		\item and the {\sc jar} metadata and statistics are also analysed and stored,
+		\item then findbugs is executed,
+		\item and the results are stored in the data repository,
+		\item the queue is also notified that this task is completed,
+	\end{enumerate}
+	\item then the next task is requested from the queue.
+\end{enumerate}
+
+This process was executed for all the available {\sc jar}s in the \textit{task queue}. The experiment was executed 5 times in order to iron out various bugs in our scripts and validate the results.
+
+\subsection{Data Provenance}
 \label{sec:data}
@@
 \end{table}
-
-\subsection{Experiment}
-\label{sec:exp}
-
-Our experiment involved three entities: a Rabbit{\sc mq}
-server,\footnote{\url{http://www.rabbitmq.com/}} a Python pool of worker
-processes and a mongo{\sc db}.\footnote{\url{http://www.mongodb.org/}}
 

### 2013-02-03 docs/msr.tex
more on the ecperiment section

--- 2013-02-03 docs/msr.tex
@@
 
-\subsection{Data Provenance and Processing}
+\subsection{Experiment}
+\label{sec:exp}
+
+Our experiment goal was to collect the metric results of the FindBugs tool.
+The process involved four entities: a number of {\it workers}, a
+{\it task queue} mechanism,\footnote{\url{http://www.rabbitmq.com/}}
+a {\it data repository},\footnote{\url{http://www.mongodb.org/}}
+and the {\it code repository}, which in our case it was the public Maven 
+repository\footnote{\url{http://mvnrepository.com}}.
+
+\begin{table}
+\centering
+\caption{Experiment software and versions}
+\label{tbl:soft-version}
+\begin{tabular}{r r r}
+\hline
+ & Software Package & version\\
+ \hline
+worker & Custom Python Script & 2.7\\
+task queue & RabbitMQ\footnote{\url{http://www.rabbitmq.com/}} & \\
+data repository & MongoDB\footnote{\url{http://www.mongodb.org/}} & \\
+code repository & Maven Repository & \\
+\hline
+\end{tabular}
+\end{table}
+
+First, we scanned the Maven repository for appropriate {\sc jar}s.
+We discuss the {\sc jar} selection process in the next 
+section. With this list we created a series of processing tasks
+and added them to the task queue. Then we
+executed 25 (Unix-based) workers that checked out tasks from the queue,
+processed the data and stored the results to the data repository.
+
+A typical processing cycle of a worker included the following steps: after
+the worker spawns, it requests a task from the queue. This task contains
+the {\sc jar} name, which is typically a project version that is downloaded locally.
+First, specific {\sc jar} metadata are calculated and stored. Such metadata include the
+last modification date of the {\sc jar}, its size and dependencies and a number that
+represents the chronological order of the release. This order is derived from an {\sc xml} file that
+accompanies every project in the Maven repository called {\it
+maven-metadata.xml}. Then FindBugs is executed and its' results are also stored
+in the data repository. When the task is completed the queue is notified and
+the next task is requested.
+
+This process was executed for all the available {\sc jar}s in the task queue.
+The experiment was executed five times in order to iron out various bugs in
+our scripts and validate the results.
+
+\subsection{Data Provenance}
 \label{sec:data}

### 2013-02-03 docs/msr.tex
work in progress

--- 2013-02-03 docs/msr.tex
@@
 
-First, we obtained a snapshot (January 2012) of the maven repository and
-handled it locally to retreive a list of all the names of the artifacts that existed in the
+Initially, we obtained a snapshot (January 2012) of the maven repository and
+handled it locally to retreive a list of all the names of the project versions that existed in the
 repository.
+Our first problem was that Maven repository hosts projects from languages other than Java, typically languages that produce executable code for the {\sc jvm} (Java Virtual Machine), such as Scala, Groovy, Clojure etc.
+These projects were filtered out by a series of filter and checks in the repository data and metadata.
 
-\begin{figure*}
-	\centering
-	\includegraphics[scale=0.6]{version_count.pdf}
-	\caption{Distribution of version count among project population}
-	\label{fig:version-count}
-\end{figure*}
+In addition, we implemented a series of checks in the \textit{worker} scripts that checked if the jars are valid in terms of language implementation.
+After the project filtering we narrowed down our data set to 17,055 projects with 114,399 versions.
+Table \ref{tbl:repository} summarises the data set information and in addition provides the basic descriptive statistic measurements
 
@@
 \end{table}
+
+We aforementioned that the Maven repository hosts software projects, typically libraries that are downloaded as dependencies with the maven tool. Each project has a series of versions.
+
+\begin{figure*}
+	\centering
+	\includegraphics[scale=0.6]{version_count.pdf}
+	\caption{Distribution of version count among project population}
+	\label{fig:version-count}
+\end{figure*}
 

### 2013-02-03 docs/msr.tex
added data provenance sections

@@
 After the project filtering we narrowed down our data set to 17,055 projects with 114,399 versions.
-Table \ref{tbl:repository} summarises the data set information and in addition provides the basic descriptive statistic measurements
+Table \ref{tbl:repository} summarises the data set information and in addition provides the basic descriptive statistic measurements.
+The distribution of version count among the selected projects is presented in Figure \ref{fig:version-count}.
 
@@
 
-We aforementioned that the Maven repository hosts software projects, typically libraries that are downloaded as dependencies with the maven tool. Each project has a series of versions.
-
 \begin{figure*}
@@
 \end{figure*}
+
+It was quite expected that the repository has many project with a few number of versions, than many projects with many versions each.
+The statistical mesurements presented in Table \ref{tbl:repository} indicate that we have 17,505 projects total and the data sets median is 3, which means that almost 50\% (8,753 projects) of the project population has 1 to 3 versions.
+There are a few projects with tens of versions and only a few with hundreds.
+The maximum number of versions for a project is 337.
+The 3$^{rd}$ quartile measurement also indicated that 75\% (13,129) of the projects have a maximum of 8 versions.
 

### 2013-02-04 analysis/maven-repo-graph/src/main/scala/gr/aueb/Mavenrepograph.scala
Remove scala based analysis

@@ -1,38 +1,0 @@
-package gr.aueb
-
-import com.mongodb.casbah._
-import com.mongodb.casbah.Implicits._
-import com.mongodb.casbah.commons.MongoDBObject
-import com.mongodb.casbah.commons.MongoDBList
-import com.mongodb.DBObject
-import com.mongodb.BasicDBObject
-import com.mongodb.BasicDBList
-
-object Mavenrepograph extends App {
-
-  val coll = MongoConnection("83.212.106.194")("findbugs")("findbugs")
-
-  println("Building adjacency matrix....")
-
-  coll.find(MongoDBObject.empty, MongoDBObject("JarMetadata" -> 1)).limit(500).foldLeft(List[(String, String)]()) {
-    (acc, x) =>
-      val group_id = x.expand[String]("JarMetadata.group_id").get
-      val artifact_id = x.expand[String]("JarMetadata.artifact_id").get
-      val version = x.expand[String]("JarMetadata.version").get
-      
-      val name = new StringBuilder(group_id).append(".").append(artifact_id).append("-").append(version)
-      
-      val b = x.get("JarMetadata").asInstanceOf[DBObject].get("dependencies")
-      val dependencies = x.get("JarMetadata").asInstanceOf[DBObject].get("dependencies") match {
-        case l : BasicDBObject => List(l)
-        case l : BasicDBList => l.toList.asInstanceOf[List[BasicDBObject]]
-      }
-      dependencies.filter(a => a.expand[String]("scope") != "test").foldLeft(List[(String, String)]()){
-        (acc1, y) =>
-          
-      }
-
-      acc ::: List()
-  }
-
-}

### 2013-02-04 analysis/repo-statistics/graph.rb
Script to process the dependency graph
For the moment, it partitions the graph based on a provided timestamp

@@ -1,0 +1,41 @@
+#!/usr/bin/env ruby
+
+require 'json'
+require 'zlib'
+
+file  = ARGV[0]       || fail("No file to parse")
+ts    = ARGV[1].to_i  || fail("No timestamp to construct graph at")
+
+puts "Reading file #{file}"
+puts "Using timestamp filter #{Time.at(ts)}"
+
+f = File.open(file)
+gz = Zlib::GzipReader.new(f).read
+js = JSON.parse(gz)
+
+#js.each{|e| e[1]['timestamp'] = rand(1044347625..1359966825)}
+js.each{|e| e[1]['timestamp'] = e[1]['timestamp'].to_i}
+
+processed = 0
+subgraph = js.reduce([]) { |acc, e|
+  STDERR.print "\rProcessed #{processed += 1} nodes"
+  if e[1]['timestamp'] < ts
+    acc << e
+  end
+  acc
+}
+
+STDERR.puts
+STDERR.puts "Reduced to #{subgraph.size} nodes"
+
+#def dfs(graph, deps)
+#  deps.map{|d| }
+#end
+#
+#subgraph.each { |x|
+#  x[1]['dependencies '].map{ |d|
+#    dep = subgraph.find{|e| e[0] == d}
+#    "#{x[0]} -> #{dep[0]}"
+#  }
+#}
+

### 2013-02-04 docs/msr.tex
some chenges in the data provenance section. Additions in the introduction

@@
 A security bug is a programming error that introduces a potentially
-exploitable weakness into a computer system~\cite{SSL12}. This weakness could lead to a
+exploitable weakness into a computer system~\cite{SSL12, TJBD11}. This weakness could lead to a
 security breach with unfortunate consequences in different layers, like databases,
@@
 effort to detect and eliminate such bugs~\cite{SZ12}, little attention has been paid to
-study them in relation to software evolution~\cite{L96, LRWPT97, IB06}. In this paper we present how we
-used a large software ecosystem to analyze how evolving software packages are
-related to the different types of security vulnerabilities.
+study them in relation to software evolution~\cite{L96, LRWPT97, IB06, RGMA06}.
+In this paper we present how we used a large software ecosystem to analyze
+how evolving software packages are related to the different types of security
+vulnerabilities.
 
@@
 software bugs. This is because compared to other bug categories,
-the category of security bugs has a distinct feature: it is critical. Specifically, a software bug can
+the category of security bugs has two distinct features: it is critical~\cite{SZ12}
+and it costs~\cite{BCL08}. Specifically, a software bug can
 lead to a mulfunction of a software artifact that runs under specific
-requirements but a security bug can allow a malicious user to alter the
-execution of the entire application. In this case, such bugs could span a wide range
-of security and privacy issues, like viewing sensitive information, the destruction or
+requirements but a security bug can allow a malicious user to alter the execution
+of the entire application. In this case, such bugs could span a wide
+range of security and privacy issues, like viewing sensitive information, the destruction or
 modification of sensitive data, denial of service and others.
-Hence, one of the basic pursuits in every new software release should be the
-mitigation of such bugs.
+Moreover, security bug disclosures lead to a negative and significant change
+in market value for a software vendor~\cite{TW07}.
+Hence, one of the basic pursuits in every new software release should
+be the mitigation of such bugs.
 
@@
 
-The subject of our study was a snapshot of the maven repository. Before
-analyzing the data of the repository we performed a number of functional fits
-on the data.
+The subject of our study was the Maven repository. Before
+analyzing the data of the repository we performed a
+number of functional fits on the data.
 
 Initially, we obtained a snapshot (January 2012) of the maven repository and
-handled it locally to retreive a list of all the names of the project versions that existed in the
-repository.
-Our first problem was that Maven repository hosts projects from languages other than Java, typically languages that produce executable code for the {\sc jvm} (Java Virtual Machine), such as Scala, Groovy, Clojure etc.
-These projects were filtered out by a series of filter and checks in the repository data and metadata.
+handled it locally to retreive a list of all the names of the project versions
+that existed in it. Our first problem was that the Maven repository
+hosts projects from languages other than Java, typically languages that produce
+executable code for the {\sc jvm} (Java Virtual Machine), such as Scala, Groovy,
+Clojure etc. These projects were filtered out by a series of checks in
+the repository data and metadata.
 
-In addition, we implemented a series of checks in the \textit{worker} scripts that checked if the jars are valid in terms of language implementation.
-After the project filtering we narrowed down our data set to 17,055 projects with 114,399 versions.
-Table \ref{tbl:repository} summarises the data set information and in addition provides the basic descriptive statistic measurements.
-The distribution of version count among the selected projects is presented in Figure \ref{fig:version-count}.
+In addition, we implemented a series of checks in the worker scripts that
+checked if the {\sc jar}s are valid in terms of implementation. For instance,
+for every {\sc jar} the worker checked if there were any {\it .class} files
+before invoking FindBugs. After the project filtering we narrowed down
+our data set to 17,055 projects with 114,399 versions.
+Table \ref{tbl:repository} summarises the data set information and
+provides the basic descriptive statistic measurements. The distribution of version
+count among the selected projects is presented in Figure \ref{fig:version-count}.
 
@@
 
-It was quite expected that the repository has many project with a few number of versions, than many projects with many versions each.
-The statistical mesurements presented in Table \ref{tbl:repository} indicate that we have 17,505 projects total and the data sets median is 3, which means that almost 50\% (8,753 projects) of the project population has 1 to 3 versions.
-There are a few projects with tens of versions and only a few with hundreds.
-The maximum number of versions for a project is 337.
-The 3$^{rd}$ quartile measurement also indicated that 75\% (13,129) of the projects have a maximum of 8 versions.
+The repository has many project with a
+few number of versions. On the contrary, there are numerous projects with a
+number of versions that is less than ten.
+The statistical mesurements presented in Table \ref{tbl:repository}
+indicate that we have 17,505 projects total and the data sets median
+is 3, which means that almost 50\% (8,753 projects) of the project
+population has 1 to 3 versions. There are a few projects containing ten
+versions and only a few with hundreds of versions. The maximum number of
+versions for a project is 337. The 3$^{rd}$ quartile measurement
+also indicated that 75\% (13,129) of the projects have a maximum of 8 versions.
 

### 2013-02-05 analysis/repo-statistics/graph.rb
Graph processing script and results

@@ -2,40 +2,123 @@
 
 require 'json'
 require 'zlib'
+require 'pp'
 
-file  = ARGV[0]       || fail("No file to parse")
-ts    = ARGV[1].to_i  || fail("No timestamp to construct graph at")
+file = ARGV[0] || fail("No file to parse")
 
-puts "Reading file #{file}"
-puts "Using timestamp filter #{Time.at(ts)}"
+STDERR.puts "Reading file #{file}"
 
 f = File.open(file)
 gz = Zlib::GzipReader.new(f).read
 js = JSON.parse(gz)
 
-#js.each{|e| e[1]['timestamp'] = rand(1044347625..1359966825)}
-js.each{|e| e[1]['timestamp'] = e[1]['timestamp'].to_i}
+STDERR.puts "Building graph"
 
-processed = 0
-subgraph = js.reduce([]) { |acc, e|
-  STDERR.print "\rProcessed #{processed += 1} nodes"
-  if e[1]['timestamp'] < ts
-    acc << e
+graph = js.map do |e|
+  e[1]['dependencies '].map do |d|
+    [e[0], d]
   end
+end.flat_map { |i| i }
+
+STDERR.puts "Build graph - number of edges: #{graph.size}"
+STDERR.puts "Collecting all versions for all artifacts"
+all_versions = js.reduce(Hash.new { |hash, key| hash[key] = [] }) do |acc, e|
+  group, artifact, version = e[0].split(/\|\|/)
+
+  if e[1]['version_order'].nil?
+    STDERR.puts "Name: #{e[0]} no version order"
+  else
+    acc["#{group}.#{artifact}"] << [version, e[1]['version_order']]
+  end
+  acc
+end
+
+STDERR.puts "Computing the latest version for each artifact"
+latest_versions = all_versions.reduce(Hash.new {}) do |acc, e|
+  k = e[0]
+  v = e[1]
+  max_version = v.max { |a, b| a[1] <=> b[1] }
+  acc[k] = max_version[0]
+  acc
+end
+
+STDERR.puts "Resolving dependency versions"
+processed = resolved = not_found = 0
+graph = graph.reduce([]) do |acc, edge|
+  processed += 1
+  group, artifact, version = edge[1].split(/\|\|/)
+  name = "#{group}.#{artifact}"
+
+  if version.nil?
+    latest = latest_versions[name]
+
+    if latest.nil?
+      not_found += 1
+      acc
+    else
+      resolved += 1
[…]

### 2013-02-06 docs/msr.tex
bib entries for the size/bugs issue

@@
 did) but also with other bug categories. In the same manner, we want to check
-if the relation between an artifact's size and its' software bugs applies 
-to security bugs (citation needed). Finally, the structure of the Maven ecosystem,
-gives us the oportunity to see if an artifact that is a dependency to a large
-number of other artifacts contains a high rate of security bugs. In this case
+the relation between an artifact's size and its' security bugs knowing the
+that research has been contradictory on the the issue~\cite{BP84, SYTP85,
+NBZ06, GKMS00}.
+Finally, the structure of the Maven ecosystem, gives us the oportunity to see
+if an artifact that is a dependency to a large number of other artifacts
+contains a high rate of security bugs. In this case
 we can strenghten the relationship between Linus' Law and software security as

### 2013-02-06 docs/msr.tex
first draft of the abstract

@@
 %\boldmath
-The abstract goes here.
+Security bugs are critical programming errors that can lead to serious
+vulnerabilities in software. Such bugs may allow an attacker to take over
+an application, steal data or prevent the application from working at all.
+In this paper, we present how we used the Maven repository to study the
+characteristics of security bugs individually and in relation to other software
+bugs. In particular, we analyzed every artifact of the repository by using a
+popular static analysis tool. Then by taking advantage of the various features of
+the repository (multiple versions for every project, dependencies) we studied
+the evolution of security bugs through time and their relationship with the
+size of the corresponding artifact and other categories. Also, based on the
+dependencies of artifacts we constructed the graph of the repository and
+studied the most popular nodes in terms of their PageRank. 
 \end{abstract}
@@
 that research has been contradictory on the the issue~\cite{BP84, SYTP85,
-NBZ06, GKMS00}.
-Finally, the structure of the Maven ecosystem, gives us the oportunity to see
-if an artifact that is a dependency to a large number of other artifacts
-contains a high rate of security bugs. In this case
-we can strenghten the relationship between Linus' Law and software security as
-Meneely et al. have already indicated~\cite{MW10}.
+NBZ06, GKMS00}. Finally, the structure of the Maven ecosystem,
+gives us the oportunity to see if an artifact that is a dependency to
+a large number of other artifacts contains a high rate of security bugs.
+In this case we can strenghten the relationship between Linus' Law and
+software security as Meneely et al. have already indicated~\cite{MW10}.
 

### 2013-02-06 docs/msr.tex
minor change

@@
 the evolution of security bugs through time and their relationship with the
-size of the corresponding artifact and other categories. Also, based on the
+size of the corresponding artifact and other bug categories. Also, based on the
 dependencies of artifacts we constructed the graph of the repository and

### 2013-02-06 docs/msr.tex
work on the inital results subsection

--- 2013-02-06 docs/msr.tex
@@
 
-\title{Dismal Code: Studying the Evolution of Security Vulnerabilities}
+\title{Dismal Code: Studying the Evolution of Security Bugs}
 
@@
 popular static analysis tool. Then by taking advantage of the various features of
-the repository (multiple versions for every project, dependencies) we studied
-the evolution of security bugs through time and their relationship with the
-size of the corresponding artifact and other categories. Also, based on the
+the repository (multiple versions for every project, dependencies and others) we studied
+the evolution of security bugs through time and their relationship with a) the
+size of the corresponding artifact and b) other bug categories. Also, based on the
 dependencies of artifacts we constructed the graph of the repository and
-studied the most popular nodes in terms of their PageRank. 
+examined the most popular nodes based on their PageRank. 
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Software Vulnerabilities, Static Analysis, Software Evolution, Software
+Software Bugs, Static Analysis, Software Evolution, Software
 Security, Maven, FindBugs.
@@
 it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
-a popular static analysis tool that has already been used in
+a static analysis tool that examines bytecode to detect software bugs and has already been used in
 research~\cite{AP10, HP07, HP04}. Specifically, we ran FindBugs on all the project
@@
 and added them to the task queue. Then we
-executed 25 (Unix-based) workers that checked out tasks from the queue,
+executed twenty five (Unix-based) workers that checked out tasks from the queue,
 processed the data and stored the results to the data repository.
@@
 our data set to 17,055 projects with 114,399 versions.
-Table \ref{tbl:repository} summarises the data set information and
+Table~\ref{tbl:repository} summarises the data set information and
 provides the basic descriptive statistic measurements. The distribution of version
@@
 number of versions that is less than ten.
-The statistical mesurements presented in Table \ref{tbl:repository}
+The statistical mesurements presented in Table~\ref{tbl:repository}
 indicate that we have 17,505 projects total and the data sets median
@@
 
+Our findings can be analyzed at two levels. First, we discuss some
+primary observations concerning the security bugs of the Maven repository as a whole.
+Then, we provide a comprehensive analysis of the results and highlight our key findings.
+
 \subsection{Overview and Initial Results}
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[scale=0.6]{bug_percent}
-	\caption{Bug Percentage in Maven Repository}
-	\label{fig:bug-percentage}
-\end{figure*}
+FindBugs separates software bugs into seven categories (see
+Table~\ref{tbl:bug-cat}). Two of them involve security: {\it Security} and {\it
+Malicious Code}. Our early findings indicated that from the total number of the
+artifacts, 4,270 of them contained at least one bug coming from the first category
+and 45,145 from the second.
 
@@
 \caption{Bug categorisation according to FindBugs}
-\label{tbl:bug-categorisation}
+\label{tbl:bug-cat}
 \begin{tabular}{l p{15em}}
@@
 \end{tabular}
-\end{table}
+\end{table}\begin{figure*}
+	\centering
+	\includegraphics[scale=0.6]{bug_percent}
+	\caption{Bug Percentage in Maven Repository}
+	\label{fig:bug-per}
+\end{figure*}
+
+Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
+repository. Together with the {\it Bad Practice} bugs and the {\it Style} bugs,
+security bugs (the sum of the {\it Security} and {\it Malicious Code}
+categories) are the most popular in the repository.
+
+\begin{figure*}
+	\centering
+	\includegraphics[scale=0.6]{bug_percent}
+	\caption{Bug Percentage in Maven Repository}
+	\label{fig:bug-percentage}4,270 
+\end{figure*}
 
@@
 
-{\it Querying techniques} are used to answer a broad range of questions
+{\it findbugs Querying techniques} are used to answer a broad range of questions
 regarding the evolution history of a project~\cite{HG05}. Bhattacharya et

### 2013-02-06 analysis/repo-statistics/count_bugless_projects.py
added count bugless project scripts

@@ -1,0 +1,23 @@
+import json
+
+
+def main():
+    fp_two = open('data/project_versions.json', 'r')
+    project_json = json.load(fp_two)
+    fp = open('data/bugless_projects.json', 'r')
+
+    total_projects = 0
+    version_count = 0
+
+    for l in fp:
+        version_count += project_json.get(l.strip(), 0)
+        total_projects += 1
+
+    fp.close()
+    fp_two.close()
+
+    print 'Total Projects: %d, Version: %d' % (total_projects, version_count)
+
+
+if __name__ == "__main__":
+    main()

### 2013-02-06 docs/msr.tex
arch figure
playing with the authors

@@
 
+\author{
+\IEEEauthorblockN{Dimitris Mitropoulos, Vassilios Karakoidas, Georgios Gousios, Panagiotis Louridas, Diomidis Spinellis}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Management Science and Technology\\
+Athens University of Economics and Business\\
+\{dimitro, bkarak, louridas, dds\}@aueb.gr}\\ \\
+\IEEEauthorblockA{TODO: Add Affiliation here\\
+Delft University of Technology\\
+Email: G.Gousios@tudelft.nl}
+}
+
 \title{Dismal Code: Studying the Evolution of Security Bugs}
-
-\author{
-\IEEEauthorblockN{Dimitris Mitropoulos}
-\IEEEauthorblockA{Department of Management Science and Technology\\
-Athens University of Economics and Business\\
-Email: dimitro@aueb.gr}\\
-\and
-\IEEEauthorblockN{Vassilios Karakoidas}
-\IEEEauthorblockA{Department of Management Science and Technology\\
-Athens University of Economics and Business\\
-Email: bkarak@aueb.gr}\\
-\and
-\IEEEauthorblockN{Georgios Gousios}
-\IEEEauthorblockA{Department of Software and Computer Technology\\
-Delft University of Technology\\
-Email: G.Gousios@tudelft.nl}\\
-\and
-\IEEEauthorblockN{Panos Louridas}
-\IEEEauthorblockA{Department of Management Science and Technology\\
-Athens University of Economics and Business\\
-Email: louridas@aueb.gr}\\
-\and
-\IEEEauthorblockN{Diomidis Spinellis}
-\IEEEauthorblockA{Department of Management Science and Technology\\
-Athens University of Economics and Business\\
-Email: dds@aueb.gr}}
 

### 2013-02-06 docs/msr.tex
fixed authors

@@
 \author{
-\IEEEauthorblockN{Dimitris Mitropoulos, Vassilios Karakoidas, Georgios Gousios, Panagiotis Louridas, Diomidis Spinellis}
+\IEEEauthorblockN{Dimitris Mitropoulos\IEEEauthorrefmark{1}, Vassilios Karakoidas\IEEEauthorrefmark{1}, Georgios Gousios\IEEEauthorrefmark{2}, Panagiotis Louridas\IEEEauthorrefmark{1}, Diomidis Spinellis\IEEEauthorrefmark{1}}\\
 \IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Management Science and Technology\\
 Athens University of Economics and Business\\
-\{dimitro, bkarak, louridas, dds\}@aueb.gr}\\ \\
-\IEEEauthorblockA{TODO: Add Affiliation here\\
+\{dimitro, bkarak, louridas, dds\}@aueb.gr}\\
+\IEEEauthorblockA{\IEEEauthorrefmark{2}TODO: Add Affiliation here\\
 Delft University of Technology\\
-Email: G.Gousios@tudelft.nl}
-}
+G.Gousios@tudelft.nl}}
 
@@
 \end{tabular}
-\end{table}\begin{figure*}
-	\centering
-	\includegraphics[scale=0.6]{bug_percent}
-	\caption{Bug Percentage in Maven Repository}
-	\label{fig:bug-per}
-\end{figure*}
+\end{table}
 
@@
 
+5,601 - jar size - 17,505. Total Projects: 5601, Versions: 32689.
+
 \begin{figure*}
@@
 	\caption{Bug Percentage in Maven Repository}
-	\label{fig:bug-percentage}4,270 
+	\label{fig:bug-per} 
 \end{figure*}
@@
 
-{\it findbugs Querying techniques} are used to answer a broad range of questions
+{\it Querying techniques} are used to answer a broad range of questions
 regarding the evolution history of a project~\cite{HG05}. Bhattacharya et

### 2013-02-07 docs/msr.tex
added another observation about bugless projects
added some measurements for severe security bugs

@@
 \author{
-\IEEEauthorblockN{Dimitris Mitropoulos\IEEEauthorrefmark{1}, Vassilios Karakoidas\IEEEauthorrefmark{1}, Georgios Gousios\IEEEauthorrefmark{2}, Panagiotis Louridas\IEEEauthorrefmark{1}, Diomidis Spinellis\IEEEauthorrefmark{1}}\\
+\IEEEauthorblockN{Dimitris Mitropoulos\IEEEauthorrefmark{1}, Vassilios Karakoidas\IEEEauthorrefmark{1},
+Georgios Gousios\IEEEauthorrefmark{2}, Panagiotis Louridas\IEEEauthorrefmark{1},
+Diomidis Spinellis\IEEEauthorrefmark{1}}\\
 \IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Management Science and Technology\\
@@
 
-Our findings can be analyzed at two levels. First, we discuss some
-primary observations concerning the security bugs of the Maven repository as a whole.
-Then, we provide a comprehensive analysis of the results and highlight our key findings.
-
-\subsection{Overview and Initial Results}
-\label{sec:overview}
-
-FindBugs separates software bugs into seven categories (see
-Table~\ref{tbl:bug-cat}). Two of them involve security: {\it Security} and {\it
-Malicious Code}. Our early findings indicated that from the total number of the
-artifacts, 4,270 of them contained at least one bug coming from the first category
-and 45,145 from the second.
-
 \begin{table}
@@
 
+Our findings can be analyzed at two levels. First, we discuss some
+primary observations concerning the security bugs of the Maven repository as a whole.
+Then, we provide a comprehensive analysis of the results and highlight our key findings.
+
+\subsection{Overview and Initial Results}
+\label{sec:overview}
+
+\begin{table*}
+\centering
+\begin{center}
+\leavevmode
+	\begin{tabular}{l r}
+	\hline
+	Bug Description & Number of Artifacts\\
+ 	\hline
+	{\sc hrs}: {\sc http} cookie formed from untrusted input & 149\\
+	{\sc hrs}: {\sc http} response splitting vulnerability & 1564\\
+	{\sc pt}: absolute path traversal in servlet  & 92\\
+	{\sc pt}: relative path traversal in servlet & 50\\
+	{\sc sql}: nonconstant string passed to execute method on an {\sc sql} & 1817\\
+	{\sc sql}: a prepared statement is generated from a nonconstant String & 1438\\
+	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 17\\
+	{\sc xss}: Servlet reflected cross site scripting vulnerability in error page & 88\\
+	{\sc xss}: Servlet reflected cross site scripting vulnerability & 140\\
+	\hline
+	\end{tabular}
+\caption{Number of Artifacts that Contain at Least One Severe Security Bug}
+\label{tbl:sev}
+\end{center}
+\end{table*}
+
+FindBugs separates software bugs into seven categories (see
+Table~\ref{tbl:bug-cat}). Two of them involve security: {\it Security} and {\it
+Malicious Code}. From the total number of the artifacts, 4,270 of them contained
+at least one bug coming from the first category
+and 45,145 from the second. Another observation involves bugs that we call {\it
+severe}. Such bugs are related to vulnerabilities due to the lack of user-input
+validation. Table~\ref{tbl:sev}) presents the number of artifacts where at
+least one of these bugs exists.
+
 Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
@@
 
-5,601 - jar size - 17,505. Total Projects: 5601, Versions: 32689.
+An interesting observation is that 5,601 (31.99\%) projects, containing 32,689
+artifacts (28.57\%), did not had any bugs at all. These cases involved small artifacts
+with a minimum number of classes.
 

### 2013-02-07 docs/msr.tex
more on the methodology and the initial results sections

--- 2013-02-06 docs/msr.tex
@@
 
-First, we scanned the Maven repository for appropriate {\sc jar}s.
-We discuss the {\sc jar} selection process in the next 
-section. With this list we created a series of processing tasks
-and added them to the task queue. Then we
-executed twenty five (Unix-based) workers that checked out tasks from the queue,
-processed the data and stored the results to the data repository.
+First, we scanned the Maven repository for appropriate {\sc jar}s and created a
+list that included them. We discuss the {\sc jar} selection process in the next 
+section. With the {\sc jar} list at hand, we created a series of processing tasks
+and added them to the task queue. Then we executed twenty five (Unix-based)
+workers that checked out tasks from the queue, processed the data and stored the
+results to the data repository.
 
@@
 the {\sc jar} name, which is typically a project version that is downloaded locally.
-First, specific {\sc jar} metadata are calculated and stored. Such metadata include the
-last modification date of the {\sc jar}, its size and dependencies and a number that
-represents the chronological order of the release. This order is derived from an {\sc xml} file that
+First, specific {\sc jar} metadata are calculated and stored. Such metadata include
+its size, its dependencies, and a number that represents the chronological order of the
+release. This order is derived from an {\sc xml} file that
 accompanies every project in the Maven repository called {\it
-maven-metadata.xml}. Then FindBugs is executed and its' results are also stored
+maven-metadata.xml}. Then FindBugs is executed and its results are also stored
 in the data repository. When the task is completed the queue is notified and
@@
 
-The subject of our study was the Maven repository. Before
-analyzing the data of the repository we performed a
-number of functional fits on the data.
+The subject of our study was the Maven repository. Before analyzing the data of the
+repository we performed a number of functional fits on the data.
 
@@
 handled it locally to retreive a list of all the names of the project versions
-that existed in it. Our first problem was that the Maven repository
-hosts projects from languages other than Java, typically languages that produce
-executable code for the {\sc jvm} (Java Virtual Machine), such as Scala, Groovy,
-Clojure etc. These projects were filtered out by a series of checks in
+that existed in it. Since FindBugs analyzes applications written in the Java
+programming language, and the Maven repository
+hosts projects from languages other than Java such as Scala, Groovy,
+Clojure etc. we filtered out such projects by performing a series of checks in
 the repository data and metadata.
 
-In addition, we implemented a series of checks in the worker scripts that
+In addition, we implemented a series of audits in the worker scripts that
 checked if the {\sc jar}s are valid in terms of implementation. For instance,
@@
 
-The repository has many project with a
-few number of versions. On the contrary, there are numerous projects with a
-number of versions that is less than ten.
 The statistical mesurements presented in Table~\ref{tbl:repository}
@@
 is 3, which means that almost 50\% (8,753 projects) of the project
-population has 1 to 3 versions. There are a few projects containing ten
+population has 1 to 3 versions.
+Note that the Maven repository has many projects with a
+few number of versions. For instance, there are numerous projects with a
+number of versions that is less than ten.
+There are a few projects containing ten
 versions and only a few with hundreds of versions. The maximum number of
@@
 \label{sec:res}
-
-Our findings can be analyzed at two levels. First, we discuss some
-primary observations concerning the security bugs of the Maven repository as a whole.
-Then, we provide a comprehensive analysis of the results and highlight our key findings.
-
-\subsection{Overview and Initial Results}
-\label{sec:overview}
-
-FindBugs separates software bugs into seven categories (see
-Table~\ref{tbl:bug-cat}). Two of them involve security: {\it Security} and {\it
-Malicious Code}. Our early findings indicated that from the total number of the
-artifacts, 4,270 of them contained at least one bug coming from the first category
-and 45,145 from the second.
 
@@
 
+Our findings can be analyzed at two levels. First, we discuss some
+primary observations concerning the security bugs of the Maven repository as a whole.
+Then, we provide a comprehensive analysis of the results and highlight our key findings.
+
+\subsection{Overview and Initial Results}
+\label{sec:overview}
+
+\begin{table*}
+\centering
+\begin{center}
+\leavevmode
+	\begin{tabular}{l r}
+	\hline
+	Bug Description & Number of Artifacts\\
+ 	\hline
+	{\sc hrs}: {\sc http} cookie formed from untrusted input & 149\\
+	{\sc hrs}: {\sc http} response splitting vulnerability & 1,564\\
+	{\sc pt}: absolute path traversal in servlet  & 92\\
+	{\sc pt}: relative path traversal in servlet & 50\\
+	{\sc sql}: nonconstant string passed to execute method on an {\sc sql} & 1,817\\
+	{\sc sql}: a prepared statement is generated from a nonconstant String & 1,438\\
+	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 17\\
+	{\sc xss}: Servlet reflected cross site scripting vulnerability in error page & 88\\
+	{\sc xss}: Servlet reflected cross site scripting vulnerability & 140\\
+	\hline
+	\end{tabular}
+\caption{Number of Artifacts that Contain at Least One Severe Security Bug}
+\label{tbl:sev}
+\end{center}
+\end{table*}
+
+FindBugs separates software bugs into seven categories (see
+Table~\ref{tbl:bug-cat}). Two of them involve security: {\it Security} and {\it
+Malicious Code}. From the total number of the artifacts, 4,270 of them contained
+at least one bug coming from the first category
+and 45,145 coming from the second.
+
+Another observation involves bugs that we could call {\it
+severe}. Such bugs are related to vulnerabilities that appear due to the lack of user-input
+validation and can lead to damaging attacks like {\sc sql} injection and
+Cross-Site Scripting. Note that to exploit such vulnerabilities, a malicious user does
+not have to know anything about the applications internals. For all the other
+bugs, another program should be written either to incorporate references to
+mutable objects, access non-final fields and others. In addition, as
+bug descriptions indicate,\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
+if an application has bugs like these, it might have more vulnerabilities that FindBugs doesn't
+report. Table~\ref{tbl:sev} presents the number of artifacts where at least one of these
+bugs exists. In the following section we provide results separately for this
+subcategory.
+
 Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
@@
 security bugs (the sum of the {\it Security} and {\it Malicious Code}
-categories) are the most popular in the repository.
-
-5,601 - jar size - 17,505. Total Projects: 5601, Versions: 32689.
+categories) are the most popular in the repository. In the following section we
+show the correlation of security bugs with all the other categories. An interesting observation is
+that 5,601 (31.99\%) projects, containing 32,689 artifacts (28.57\%), did not
+have any bugs at all. These cases involved small artifacts with a minimum number of classes.
+This consorts with the relationship between the size of an artifact and it's
+bugs that is presented in the upcoming section.
 

### 2013-02-07 docs/msr.tex
minor fixes

@@
 Experimental & Includes unsatisfied obligations. For instance,
-forgetting to close a file \\
-Internationalisation & Indicates the use of non-localized methods \\
+forgetting to close a file. \\
+Internationalisation & Indicates the use of non-localized methods. \\
 Multi-Threaded Correctness & Thread synchronization issues. \\
 Performance & Involves inefficient memory usageallocation, usage 
-of non-static classes \\
+of non-static classes. \\
 Style & Code that is confusing, or
@@
 
-There are noumerous methods for mining software repositories in the context
+There are numerous methods for mining software repositories in the context
 of software evolution~\cite{KCM07}. In this section we focus on the ones
@@
 Bugzilla. Their research showed that security bugs require more experienced developers
-to be fixed. In addittion, security bug fixes are more complex than the
+to be fixed. In addittion, they suggested that security bug fixes are more complex than the
 fixes of performance and other bugs.

### 2013-02-08 docs/msr.tex
more changes

@@
 defined in terms of bytecode.
-	\item Security bug persistense between versions. We show evidence that specific bugs are
-not eliminated between versions.
+%	\item Security bug persistense between versions. We show evidence that specific bugs are
+%not eliminated between versions.
 	\item The correlation of security bugs with other bug categories. We
@@
 describe the processing of our data and our experiment (Section \ref{sec:meth}),
-present and discuss the results we obtained (Section \ref{sec:res},
+present and discuss the results we obtained (Section \ref{sec:res}),
 outline related work (Section \ref{sec:rel}),
-and end up with an conclusion and directions for future work (Section \ref{sec:con}).
+and end up with a conclusion and directions for future work (Section \ref{sec:con}).
 
@@
 
-The subject of our study was the Maven repository. Before analyzing the data of the
-repository we performed a number of functional fits on the data.
-
-Initially, we obtained a snapshot (January 2012) of the maven repository and
-handled it locally to retreive a list of all the names of the project versions
-that existed in it. Since FindBugs analyzes applications written in the Java
-programming language, and the Maven repository
-hosts projects from languages other than Java such as Scala, Groovy,
-Clojure etc. we filtered out such projects by performing a series of checks in
-the repository data and metadata.
-
-In addition, we implemented a series of audits in the worker scripts that
-checked if the {\sc jar}s are valid in terms of implementation. For instance,
-for every {\sc jar} the worker checked if there were any {\it .class} files
-before invoking FindBugs. After the project filtering we narrowed down
-our data set to 17,055 projects with 114,399 versions.
-Table~\ref{tbl:repository} summarises the data set information and
-provides the basic descriptive statistic measurements. The distribution of version
-count among the selected projects is presented in Figure \ref{fig:version-count}.
-
 \begin{table}
@@
 
+The subject of our study was the Maven repository. Before analyzing the data of the
+repository we performed a number of functional fits on the data.
+
+Initially, we obtained a snapshot (January 2012) of the maven repository and
+handled it locally to retreive a list of all the names of the project versions
+that existed in it. Since FindBugs analyzes applications written in the Java
+programming language, and the Maven repository
+hosts projects from languages other than Java such as Scala, Groovy,
+Clojure etc. we filtered out such projects by performing a series of checks in
+the repository data and metadata.
+
+In addition, we implemented a series of audits in the worker scripts that
+checked if the {\sc jar}s are valid in terms of implementation. For instance,
+for every {\sc jar} the worker checked if there were any {\it .class} files
+before invoking FindBugs. After the project filtering we narrowed down
+our data set to 17,055 projects with 114,399 versions.
+Table~\ref{tbl:repository} summarises the data set information and
+provides the basic descriptive statistic measurements. The distribution of version
+count among the selected projects is presented in Figure \ref{fig:version-count}.
+
 \begin{figure*}
@@
 	\includegraphics[scale=0.6]{version_count.pdf}
-	\caption{Distribution of version count among project population}
+	\caption{Distribution of
+Version Count Among Project Population}
 	\label{fig:version-count}
@@
 
+FindBugs separates software bugs into seven categories (see
+Table~\ref{tbl:bug-cat}). Two of them involve security: {\it Security} and {\it
+Malicious Code}. From the total number of the artifacts, 4,270 of them contained
+at least one bug coming from the first category
+and 45,145 coming from the second.
+
+Another observation involves bugs that we could call {\it
+severe}. Such bugs are related to vulnerabilities that appear due to the lack of user-input
+validation and can lead to damaging attacks like {\sc sql} injection and
+Cross-Site Scripting. Note that to exploit such vulnerabilities, a malicious user does
+not have to know anything about the applications internals. For all the other
+bugs, another program should be written either to incorporate references to
+mutable objects, access non-final fields and others. In addition, as
+bug descriptions indicate,\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
+if an application has bugs like these, it might have more vulnerabilities that FindBugs doesn't
+report. Table~\ref{tbl:sev} presents the number of artifacts where at least one of these
+bugs exists. In the following section we provide results separately for this
+subcategory.
+
 \begin{table*}
@@
 
-FindBugs separates software bugs into seven categories (see
-Table~\ref{tbl:bug-cat}). Two of them involve security: {\it Security} and {\it
-Malicious Code}. From the total number of the artifacts, 4,270 of them contained
-at least one bug coming from the first category
-and 45,145 coming from the second.
-
-Another observation involves bugs that we could call {\it
-severe}. Such bugs are related to vulnerabilities that appear due to the lack of user-input
-validation and can lead to damaging attacks like {\sc sql} injection and
-Cross-Site Scripting. Note that to exploit such vulnerabilities, a malicious user does
-not have to know anything about the applications internals. For all the other
-bugs, another program should be written either to incorporate references to
-mutable objects, access non-final fields and others. In addition, as
-bug descriptions indicate,\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
-if an application has bugs like these, it might have more vulnerabilities that FindBugs doesn't
-report. Table~\ref{tbl:sev} presents the number of artifacts where at least one of these
-bugs exists. In the following section we provide results separately for this
-subcategory.
-
 Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
@@
 security bugs (the sum of the {\it Security} and {\it Malicious Code}
-categories) are the most popular in the repository. In the following section we
+categories) are the most popular in the repository. This could be an indication
+that programmers write code that implements the required functionality without considering
+its many security aspects. In the following section we
 show the correlation of security bugs with all the other categories. An interesting observation is
@@
 have any bugs at all. These cases involved small artifacts with a minimum number of classes.
-This consorts with the relationship between the size of an artifact and it's
+This goes along with the relationship between the size of an artifact and it's
 bugs that is presented in the upcoming section.

### 2013-02-08 analysis/repo-statistics/check_missing.py
added cross validity script

@@ -1,0 +1,50 @@
+import os
+import xmldict
+
+from helpers.mongo_helper import get_version, get_mongo_connection, MONGO_COL
+
+def main():
+    base_url = '/Users/bkarak/devel/repositories/maven/maven/'
+    col_obj = get_mongo_connection()[MONGO_COL]
+    fp = open('data/missing_versions.txt', 'r')
+
+    total_jars = 0
+    missing = 0
+    really_missing = 0
+
+    for line in fp:
+        (group_id, artifact_id) = line.strip().split('||')
+        maven_base_url = '%s%s/%s/' % (base_url, group_id.replace('.', '/'), artifact_id)
+        maven_metadata_name = '%smaven-metadata.xml' % (maven_base_url,)
+
+        if not os.path.exists(maven_metadata_name):
+            continue
+
+        json_xml = xmldict.parse(open(maven_metadata_name, 'r').read())
+        versions = json_xml.get('metadata', {}).get('versioning', {}).get('versions', {}).get('version')
+        version_list = []
+
+        if isinstance(versions, list):
+            version_list.extend(versions)
+        else:
+            version_list.append(versions)
+
+        for v in version_list:
+            docs = get_version(col_obj, group_id, artifact_id, v)
+            total_jars += 1
+
+            if len(docs) == 0:
+                missing += 1
+                print '[%d]: Missing %s||%s||%s' % (total_jars, group_id, artifact_id, v)
+                local_jar_path = '%s%s/%s-%s.jar' % (maven_base_url, v, artifact_id, v)
+
+                if not os.path.exists(local_jar_path):
+                    really_missing += 1
+
+    fp.close()
+
+    print 'Total: %d, Missing: %d (%d)' % (total_jars, missing - really_missing, missing)
+
+
+if __name__ == "__main__":
+    main()

### 2013-02-08 analysis/repo-statistics/helpers/mongo_helper.py

@@ -65,8 +65,8 @@ class MongoDocumentIterator(object):
 
 class MongoProjectIterator(MongoDocumentIterator):
     def __init__(self, group_id, artifact_id, query=None, fields=None):
-        __q = {'JarMetadata.group_id' : group_id,
-               'JarMetadata.artifact_id' : artifact_id}
+        __q = {'JarMetadata.group_id': group_id,
+               'JarMetadata.artifact_id': artifact_id}
 
         __f = ['JarMetadata.version_order']
 
@@ -116,3 +116,21 @@ def get_project_versions(col_obj, group_id, artifact_id):
     except pymongo.errors.AutoReconnect, ae:
         print 'Mongo Connection is Down. Reconnecting! (record_exists, %s)' % (ae,)
         return get_project_versions(col_obj, group_id, artifact_id)
+
+
+def get_version(col_obj, group_id, artifact_id, version):
+    try:
+        result = []
+
+        q = {'JarMetadata.group_id': group_id,
+             'JarMetadata.artifact_id': artifact_id,
+             'JarMetadata.version': version}
+
+        for c in col_obj.find(q, fields=[], timeout=False):
+            result.append(c)
+
+        return result
+    except pymongo.errors.AutoReconnect, ae:
+        print 'Mongo Connection is Down. Reconnecting! (record_exists, %s)' % (ae,)
+        return get_project_versions(col_obj, group_id, artifact_id)
+

### 2013-02-08 analysis/repo-statistics/check_missing.py
added online version of check_utility

@@ -1,10 +1,20 @@
-import os
 import xmldict
+import httplib
+
+from urllib2 import urlopen
 
 from helpers.mongo_helper import get_version, get_mongo_connection, MONGO_COL
 
+def url_exists(base_url, path):
+    conn = httplib.HTTPConnection(base_url)
+    conn.request('HEAD', path)
+    response = conn.getresponse()
+    conn.close()
+    return response.status == 200
+
+
 def main():
-    base_url = '/Users/bkarak/devel/repositories/maven/maven/'
+    base_url = 'http://mirrors.ibiblio.org/maven2'
     col_obj = get_mongo_connection()[MONGO_COL]
     fp = open('data/missing_versions.txt', 'r')
 
@@ -14,32 +24,35 @@ def main():
 
     for line in fp:
         (group_id, artifact_id) = line.strip().split('||')
-        maven_base_url = '%s%s/%s/' % (base_url, group_id.replace('.', '/'), artifact_id)
+        maven_base_url = '%s/%s/%s/' % (base_url, group_id.replace('.', '/'), artifact_id)
         maven_metadata_name = '%smaven-metadata.xml' % (maven_base_url,)
 
-        if not os.path.exists(maven_metadata_name):
+        try:
+            fp = urlopen(maven_metadata_name)
+            json_xml = xmldict.parse(fp.read())
+            versions = json_xml.get('metadata', {}).get('versioning', {}).get('versions', {}).get('version')
+            version_list = []
+
+            if isinstance(versions, list):
+                version_list.extend(versions)
+            else:
+                version_list.append(versions)
+
+            for v in version_list:
+                docs = get_version(col_obj, group_id, artifact_id, v)
+                total_jars += 1
+
+                if len(docs) == 0:
+                    missing += 1
+                    print '[%d]: Missing %s||%s||%s' % (total_jars, group_id, artifact_id, v)
+                    url_jar_path = '/maven2/%s/%s/%s/%s-%s.jar' % (group_id.replace('.', '/'), artifact_id, v, artifact_id, v)
+
+                    if not url_exists('mirrors.ibiblio.org', url_jar_path):
+                        really_missing += 1
+                        print '%s%s' % ('mirrors.ibiblio.org', url_jar_path)
+        except Exception, e:
+            print '[%d] ERROR: %s (%s)' % (total_jars, maven_metadata_name, e)
             continue
-
-        json_xml = xmldict.parse(open(maven_metadata_name, 'r').read())
[…]

### 2013-02-08 analysis/repo-statistics/project_bugs_counts.py
more bug counting for pythonistas

@@ -1,0 +1,57 @@
+import json
+import sys
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy.stats as st
+import math
+
+bugs_per_version = {
+    'SECURITY_HIGH': [],
+    'SECURITY_LOW': [],
+    'MALICIOUS_CODE': [],
+    'STYLE': [],
+    'CORRECTNESS': [],
+    'BAD_PRACTICE': [],
+    'MT_CORRECTNESS': [],
+    'I18N': [],
+    'PERFORMANCE': [],
+    'EXPERIMENTAL': []
+    }
+
+with open("data/project_counters.json", "r") as json_file:
+    json_input = json.load(json_file)
+    for project, data in json_input.iteritems():
+        if len(data['versions']) > 100:
+            continue
+        for version in data['versions']:
+            version_order = version['JarMetadata']['version_order']
+            if version_order == 0 or version_order > 100:
+                continue
+            counters = version['Counters']
+            for counter in bugs_per_version.keys():
+                value = counters.get(counter, 0)
+                if value > 1000:
+                    print project, version_order, counter, value
+                bugs_per_version[counter].append((version_order, value))
+
+                
+plt.figure(1, figsize=(16, 10))
+num_plots = len(bugs_per_version.keys())
+num_cols = 4
+num_rows = num_plots / num_cols
+if num_rows % num_cols != 0:
+    num_rows += 1
+num_plot = 1
+for counter, counter_list in bugs_per_version.iteritems():
+    bugs_per_version_arr = np.array(counter_list).transpose()
+    plt.subplot(num_rows, num_cols, num_plot)
+    plt.xlim((0, 100))
+    ymax = math.ceil(1.1 * bugs_per_version_arr[1].max())
+    plt.ylim((0, ymax))
+    plt.scatter(bugs_per_version_arr[0], bugs_per_version_arr[1])
+    plt.title(counter)
+    num_plot += 1
+
+plt.show()
+
+    

### 2013-02-08 analysis/repo-statistics/project_counters_diffs.py

@@ -1,0 +1,105 @@
+import json
+import sys
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy.stats as st
+import math
+
+bug_types_diffs = {
+    'SECURITY_HIGH': [],
+    'SECURITY_LOW': [],
+    'MALICIOUS_CODE': [],
+    'STYLE': [],
+    'CORRECTNESS': [],
+    'BAD_PRACTICE': [],
+    'MT_CORRECTNESS': [],
+    'I18N': [],
+    'PERFORMANCE': [],
+    'EXPERIMENTAL': []
+    }
+
+
+with open("data/project_counters.json", "r") as json_file:
+    json_input = json.load(json_file)
+    diffs = {}
+    for project, data in json_input.iteritems():
+        project_count = []
+        diffs[project] = {}
+        bad_project = False
+        for version in data['versions']:
+            if bad_project == True:
+                diffs[project] = {}
+                break
+            version_order = version['JarMetadata']['version_order']
+            if version_order == 0:
+                bad_project = True
+                continue
+            project_count.append({})
+            counters = version['Counters']
+            for counter, value in counters.iteritems():
+                cur =  version_order - 1
+                if version_order != len(project_count):
+                    bad_project = True
+                    break
+                else:
+                    project_count[cur][counter] = value
+            if version_order > 1:
+                counters_to_check = set()
+                last_couple = project_count[cur-1:cur+1]
+                counters_to_check = reduce(lambda x, y: x.union(y.keys()),
+                                           last_couple,
+                                           set())
+                for counter_to_check in counters_to_check:
+                    prev_counts = project_count[cur - 1] 
+                    prev_value = prev_counts.get(counter_to_check, 0)
+                    cur_counts = project_count[cur]
+                    cur_value = cur_counts.get(counter_to_check, 0)
+                    diff = cur_value - prev_value
+                    if not (diff == 0 and cur_value == 0):
+                        d = diffs[project].setdefault(counter_to_check, [])
+                        d.append(diff)
+                    # if counter_to_check not in diffs[project]:
[…]

### 2013-02-11 analysis/repo-statistics/top_nodes_counters.py
successfully retrieveing the bugs of the top 50 nodes of the maven graph

@@ -12,19 +12,27 @@ def main():
             counter = counter + 1
             try:
                 (group_id,artifact,version) = row[0].split("||")
-                print "%s %s %s" % (group_id,artifact,version)
-                print row[1]
-                print row[2]
-                print row[3]
-            
-            my_key = ''.join([group_id,"||",artifact]) 
-            if my_key in data:
-                print "exists"
-
+                #print "%s %s %s" % (group_id,artifact,version)
+                #print row[1]
+                #print row[2]
+                #print row[3]
+        
+                my_key = ''.join([group_id,"||",artifact]) 
+                if my_key in data:
+                    #print data.get(my_key)
+                    #json_object = json.load(data.get(my_key))
+                    obj = data.get(my_key)
+                    for my_version in obj[u'versions']:
+                        if my_version[u'JarMetadata'][u'version'] == version:
+                            print "%s %s %s" % (group_id,artifact,version)
+                            print row[1]
+                            print row[2]
+                            print row[3]
+                            print my_version[u'Counters']
             except:
                 pass
             if counter == 50:
                 break
-
+            
 if __name__== "__main__":
  main()

### 2013-02-11 analysis/repo-statistics/helpers/mongo_helper.py
added missing bugs script

@@ -103,11 +103,24 @@ def get_mongo_connection():
     return mongo_db
 
 
+def get_collection():
+    return get_mongo_connection()[MONGO_COL]
+
+
+def store_to_mongo(json):
+    try:
+        mongo_id = get_collection().insert(json)
+        print "Stored with ID: " + str(mongo_id)
+    except pymongo.errors.AutoReconnect, ae:
+        print 'Mongo Connection is Down. Reconnecting! (store_to_mongo, %s)' % (ae,)
+        store_to_mongo(json)
+
+
 def get_project_versions(col_obj, group_id, artifact_id):
     try:
         result = []
-        q = {'JarMetadata.group_id' : group_id,
-             'JarMetadata.artifact_id' : artifact_id}
+        q = {'JarMetadata.group_id': group_id,
+             'JarMetadata.artifact_id': artifact_id}
 
         for c in col_obj.find(q, timeout=False):
             result.append(c)

### 2013-02-11 analysis/repo-statistics/local_worker.py

@@ -1,5 +1,6 @@
 import os
 import zipfile
+from helpers import mongo_helper
 
 
 def has_classes(filename):
@@ -36,58 +37,45 @@ def get_jar_size(filename):
         return 0
 
 
-def get_metadata_from_url(url):
-    url_arr = url.split('/')
-    # -1: jar, -2: version, -3: artifact_id, remaining up to /maven2 -> groupId
-    metadata = dict()
-    metadata['jar_filename'] = url_arr[-1]
-    metadata['version'] = url_arr[-2]
-    metadata['artifact_id'] = url_arr[-3]
-    metadata['group_id'] = reduce(lambda acc, x: acc + "." + x, url_arr[4:-3], "")[1:]
-    return metadata
-
-
-def convert_findbugs_xml(url, findbugs_xml):
+def convert_findbugs_xml(findbugs_xml):
     import xmldict
     import json
 
-    result_json = json.loads(json.dumps(xmldict.parse(findbugs_xml)).replace('"@','"'))
-    url_arr = get_metadata_from_url(url)
+    xml_data = open(findbugs_xml, 'r').read()
+    result_json = json.loads(json.dumps(xmldict.parse(xml_data)).replace('"@', '"'))
 
     # -1: jar, -2: version, -3: artifact_id, -4: group_id
-    _jar_filename = metadata['jar_filename']
-    _version = metadata['version']
-    _artifact_id = metadata['artifact_id']
-    _group_id = metadata['group_id']
+    _full_name = result_json.get('BugCollection', {}).get('Project', {}).get('Jar', None)
 
-    # get pom information
-    _pom_url = url.replace('.jar', '.pom')
-    _pom_filename = _jar_filename.replace('.jar', '.pom')
+    if _full_name is None:
+        raise Exception('Jar tag is not found (%s)' % (result_json,))
 
-    log.info('Downloading POM: %s -> %s' % (_pom_url, _pom_filename))
-    urllib.urlretrieve(_pom_url, _pom_filename)
+    print 'Processing ... %s' % (_full_name,)
+
+    _jar_filename = os.path.basename(_full_name)
+    _pom_filename = _full_name.replace('.jar', '.pom')
+    _metadata_filename = '%s/maven-metadata.xml' % ('/'.join(_full_name.split('/')[:-2]),)
     _dependencies = []
+    _versions = []
+
+    _version = None
+    _artifact_id = None
+    _group_id = None
+    _version_order = 0
 
     if os.path.exists(_pom_filename):
         try:
[…]

### 2013-02-11 analysis/repo-statistics/get_persistence.py
added get_persistence

@@ -1,0 +1,74 @@
+import json
+
+from helpers.data_helper import ArrayCount, save_to_file, load_projects_json
+from helpers.mongo_helper import MongoProjectIterator
+
+
+def main():
+    projects = load_projects_json()
+    results = {}
+    total_projects = len(projects)
+    count = 0
+
+    print 'Found %d Projects' % (total_projects,)
+
+    for p in projects:
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.version_order', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.Method.name', 'BugCollection.BugInstance.Field.name'])
+        doc_list = piter.documents_list()
+        count += 1
+
+        print '[%d:%d] %s||%s: %d versions' % (count, total_projects, p.group_id(), p.artifact_id(), len(doc_list))
+
+        for d in doc_list:
+            proj_array_count = ArrayCount()
+            signatures = []
+
+            for bi in d.get('BugCollection', {}).get('BugInstance', []):
+                if not isinstance(bi, dict):
+                    #print 'Invalid BugInstance (%s)' % (bi,)
+                    continue
+
+                bug_category = bi.get('category', '')
+
+                # create signature
+                signatures_ids = []
+                classnames = bi['Class']
+
+                if isinstance(classnames, list):
+                    for c in classnames:
+                        signatures_ids.append(c.get('classname', 'NotSet'))
+                elif isinstance(classnames, dict):
+                    signatures_ids.append(classnames.get('classname', 'NotSet'))
+
+                # methods
+                methodnames = bi.get('Method', {})
+
+                if isinstance(methodnames, list):
+                    for m in methodnames:
+                        signatures_ids.append(m.get('name', 'NotSet'))
+                elif isinstance(methodnames, dict):
+                    signatures_ids.append(methodnames.get('name', 'NotSet'))
+
+                # fields
+                fieldnames = bi.get('Field', {})
+                if isinstance(fieldnames, list):
+                    for f in fieldnames:
+                        signatures_ids.append(f.get('name', 'NotSet'))
+                elif isinstance(fieldnames, dict):
[…]

### 2013-02-12 docs/msr.tex
table captions should be on top
added graph results description

@@
 defined in terms of bytecode.
-%	\item Security bug persistense between versions. We show evidence that specific bugs are
-%not eliminated between versions.
+	\item Security bug persistense between versions. We show evidence that specific bugs are
+not eliminated between versions.
 	\item The correlation of security bugs with other bug categories. We
@@
 Our experiment goal was to collect the metric results of the FindBugs tool.
-The process involved four entities: a number of {\it workers}, a
-{\it task queue} mechanism,\footnote{\url{http://www.rabbitmq.com/}}
+The process involved four entities (see Table~\ref{tbl:exp}):
+a number of {\it workers}, a {\it task queue}
+mechanism,\footnote{\url{http://www.rabbitmq.com/}}
 a {\it data repository},\footnote{\url{http://www.mongodb.org/}}
@@
 \centering
-\caption{Experiment software and versions}
-\label{tbl:soft-version}
+\caption{Experiment Entities}
+\label{tbl:exp}
 \begin{tabular}{r r r}
@@
  \hline
-worker & Custom Python Script & 2.7\\
-task queue & RabbitMQ\footnote{\url{http://www.rabbitmq.com/}} & \\
-data repository & MongoDB\footnote{\url{http://www.mongodb.org/}} & \\
-code repository & Maven Repository & \\
+Worker & Custom Python Script & 2.7\\
+Task Queue & RabbitMQ & 3.0.1 \\
+Data Repository & MongoDB & 2.2 \\
+Code Repository & Maven Repository & January 2012 \\
 \hline
@@
 if an application has bugs like these, it might have more vulnerabilities that FindBugs doesn't
-report. Table~\ref{tbl:sev} presents the number of artifacts where at least one of these
+report. Table~\ref{tbl:sev} presents the number of {\sc jar}s where at least one of these
 bugs exists. In the following section we provide results separately for this
@@
 \centering
-\begin{center}
+\caption{Number of Artifacts that Contain at Least One Severe Security Bug}
+\label{tbl:sev}
 \leavevmode
@@
 	\end{tabular}
-\caption{Number of Artifacts that Contain at Least One Severe Security Bug}
-\label{tbl:sev}
-\end{center}
 \end{table*}
@@
 
+As we mentioned earlier, during the experiment we managed to retrieve the
+dependencies of every version. Based on this information we created a graph
+that represented the snapshot of the repository that we were analyzing. The
+nodes of the graph represented the versions and the vertices their dependencies.
+We have to mention here that the graph is not representative. For instance, if
+a dependency was pointing only to a project (and not to a specific version), we chose to
+select the latest version found on the repository. Also, this graph is not
+complete. This is because threre were missing versions.
+Practically, the corresponding {\it pom}, or {\it war} files existed on the
+repository, but the {\sc jar} file did not. From the 56,5680 vertices, 191,433
+belonged to the first category while 16,4234 belonged to the second. Finally,
+the graph contained 80,354 nodes. Obviously the number does not correspond to
+the number of the total versions (see Section~\ref{sec:data}). This is because
+some versions did not contain any information about their dependencies so they
+are not represented in the graph. After creating the graph, we ran the PageRank
+algorithm~\cite{BP98} on it and retrieved all PageRanks for every node. Then we
+examined the security bugs of the 50 most popular nodes based on their PageRank.
+33 of them contained security bugs while two of them contained severe bugs.
+Finally, 25 of them were latest versions at the time.
+
 \subsection{Analysis}
@@
 \subsubsection{Critical Artifacts and their Defects}
+
+\section{Discussion}
+\label{sec:dis}
 

### 2013-02-12 analysis/repo-statistics/project_counters.py
project_counter updated - now has the missing versions

@@ -49,7 +49,7 @@ def main():
         # TODO: uncomment this to print out each entry
         #print results
 
-    save_to_file('project_counters.json', json.dumps(results))
+    save_to_file('project_counters_2.json', json.dumps(results))
 
 
 if __name__ == "__main__":

### 2013-02-12 analysis/repo-statistics/find_vulnerable_projects.py
recalculated bug_correlation_counters

@@ -4,7 +4,6 @@ from helpers.data_helper import save_to_file
 from helpers.mongo_helper import MongoDocumentIterator
 
 
-
 def main():
     project_list = []
 
@@ -24,7 +23,7 @@ def main():
             if project_key not in project_list:
                 project_list.append(project_key)
 
-    miter = MongoDocumentIterator(query={'BugCollection.BugInstance.category':'MALICIOUS_CODE'},fields=['JarMetadata.group_id',  'JarMetadata.artifact_id', 'JarMetadata.version','BugCollection.BugInstance.category', 'BugCollection.BugInstance.type'])
+    miter = MongoDocumentIterator(query={'BugCollection.BugInstance.category':'MALICIOUS_CODE'},fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version','BugCollection.BugInstance.category', 'BugCollection.BugInstance.type'])
 
     print 'Found %d documents with MALICIOUS_CODE bugs' % (miter.total(),)
 

### 2013-02-13 docs/msr.tex
some changes - fixes

@@
 characteristics of security bugs individually and in relation to other software
-bugs. In particular, we analyzed every artifact of the repository by using a
+bugs. In particular, we analyzed every project version of the repository by using a
 popular static analysis tool. Then by taking advantage of the various features of
 the repository (multiple versions for every project, dependencies and others) we studied
-the evolution of security bugs through time and their relationship with a) the
-size of the corresponding artifact and b) other bug categories. Also, based on the
+the evolution of security bugs through time, their persistence and their relationship with a) the
+size of the corresponding version and b) other bug categories. Also, based on the
 dependencies of artifacts we constructed the graph of the repository and
@@
 
-The motivation behind our work is to validate if programmers tend to care for
+The motivation behind our work was to validate if programmers tend to care for
 such high-risk bugs when they release a new version of their software. In
-addition, we want to investigate other critical aspects associated with such
-vulnerabilities. For instance, we want to elaborate more on the relation of security
+addition, we wanted to investigate other critical features associated with such
+vulnerabilities like the persistency of a bug. In essence, to check if specific bugs stay
+unresolved for a long time. Also, we wanted to elaborate more on the relation of security
 bugs not only with performance bugs (as Zaman et al.~\cite{ZAH11} have already
-did) but also with other bug categories. In the same manner, we want to check
-the relation between an artifact's size and its' security bugs knowing the
+did) but also with other bug categories. In the same manner, we tried to check
+the relation between a version's size and its' security bugs knowing the
 that research has been contradictory on the the issue~\cite{BP84, SYTP85,
-NBZ06, GKMS00}. Finally, the structure of the Maven ecosystem,
-gives us the oportunity to see if an artifact that is a dependency to
-a large number of other artifacts contains a high rate of security bugs.
+NBZ06, GKMS00}. Finally, we examined the Maven ecosystem as a whole from a security
+perspective. Its structure, gave us the oportunity to see if a project version that is a dependency to
+a large number of others contains a high rate of security bugs.
 In this case we can strenghten the relationship between Linus' Law and
@@
 should eliminate them.
-	\item We show evidence of the relation between security bugs and the artifact's size.  Here, size is
-defined in terms of bytecode.
-	\item Security bug persistense between versions. We show evidence that specific bugs are
-not eliminated between versions.
+	\item Security bug persistense between versions. We show evidence that
+specific bugs are not eliminated between versions.
+	\item We show evidence of the relation between security bugs and a project
+version's size.  Here, size is defined in terms of bytecode.
 	\item The correlation of security bugs with other bug categories. We
@@
 performance, coding practices and others.
-	\item The relation of software dependencies and security bugs. Our
-hypothesis is that an artifact that is a dependency of many other artifacts
-should have a low rate of security bugs. 
+%	\item The relation of software dependencies and security bugs. Our
+%hypothesis is that an artifact that is a dependency of many other artifacts
+%should have a low rate of security bugs. 
 \end{itemize}
@@
 
-Initially, we obtained a snapshot (January 2012) of the maven repository and
+Initially, we obtained a snapshot (January 2012) of the Maven repository and
 handled it locally to retreive a list of all the names of the project versions
-that existed in it. Since FindBugs analyzes applications written in the Java
+that existed in it. A project version can be uniquely identified by the triplet:
+{\it group id}, {\it artifact id} and {\it version}.
+Since FindBugs analyzes applications written in the Java
 programming language, and the Maven repository
@@
 The statistical mesurements presented in Table~\ref{tbl:repository}
-indicate that we have 17,505 projects total and the data sets median
+indicate that we have 17,505 projects and the data set's median
 is 3, which means that almost 50\% (8,753 projects) of the project
@@
 \centering
-\caption{Bug categorisation according to FindBugs}
+\caption{Bug Categorisation According to FindBugs}
 \label{tbl:bug-cat}
@@
 severe}. Such bugs are related to vulnerabilities that appear due to the lack of user-input
-validation and can lead to damaging attacks like {\sc sql} injection and
-Cross-Site Scripting. Note that to exploit such vulnerabilities, a malicious user does
+validation and can lead to damaging attacks like {\sc sql} injection~\cite{RL12} and
+Cross-Site Scripting~\cite{WS08}. Note that to exploit such vulnerabilities, a malicious user does
 not have to know anything about the applications internals. For all the other
@@
 \centering
-\caption{Number of Artifacts that Contain at Least One Severe Security Bug}
+\caption{Number of Versions that Contain at Least One Severe Security Bug}
 \label{tbl:sev}
@@
 	\hline
-	Bug Description & Number of Artifacts\\
+	Bug Description & Number of Versions\\
  	\hline
@@
 
+\subsubsection{Persistense of Security Bugs}
+
 \subsubsection{The Relation of Defects with the size of an Artifact}
 
-\subsubsection{Persistense of Security Bugs}
-
 \subsubsection{Security Bugs {\sc vs} Other Bug Categories}
-
-\subsubsection{Critical Artifacts and their Defects}
 

### 2013-02-13 analysis/repo-statistics/project_counters.py
project counters is correct

@@ -7,13 +7,21 @@ from helpers.mongo_helper import MongoProjectIterator
 def main():
     projects = load_vuln_projects_json()
     results = {}
+    security_bugs = ['HRS_REQUEST_PARAMETER_TO_COOKIE',
+                     'HRS_REQUEST_PARAMETER_TO_HTTP_HEADER',
+                     'PT_ABSOLUTE_PATH_TRAVERSAL',
+                     'SQL_NONCONSTANT_STRING_PASSED_TO_EXECUTE',
+                     'SQL_PREPARED_STATEMENT_GENERATED_FROM_NONCONSTANT_STRING',
+                     'XSS_REQUEST_PARAMETER_TO_JSP_WRITER',
+                     'XSS_REQUEST_PARAMETER_TO_SEND_ERROR',
+                     'XSS_REQUEST_PARAMETER_TO_SERVLET_WRITER']
 
     total_projects = len(projects)
     count = 0
     print 'Found %d Projects' % (total_projects,)
 
     for p in projects:
-        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.jar_size', 'JarMetadata.version_order', 'JarMetadata.jar_last_modification_date', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.priority'])
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.jar_size', 'JarMetadata.version_order', 'JarMetadata.jar_last_modification_date', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.priority'])
         doc_list = piter.documents_list()
         documents = []
         count += 1
@@ -23,21 +31,49 @@ def main():
         for d in doc_list:
             doc_results = {'JarMetadata': d['JarMetadata']}
             doc_array_count = ArrayCount()
+            sec_instances = []
 
             for bi in d.get('BugCollection', {}).get('BugInstance', []):
                 if not isinstance(bi, dict):
                     print bi
                     continue
 
-                bug_category = bi.get('category', None)
+                bug_category = bi.get('category', '')
 
-                if bug_category is not None:
[…]

### 2013-02-13 analysis/repo-statistics/get_persistence.py
added version order

@@ -62,7 +62,8 @@ def main():
                 signatures.append(signature)
                 proj_array_count.incr('bug_category')
 
-            results['%s||%s||%s' % (p.group_id(), p.artifact_id(), d['JarMetadata']['version'])] = {'Counters': proj_array_count.get_series(), 'Bugs': signatures}
+            print d['JarMetadata']['version_order']
+            results['%s||%s||%s' % (p.group_id(), p.artifact_id(), d['JarMetadata']['version'])] = {'Counters': proj_array_count.get_series(), 'Bugs': signatures, 'version_order': d['JarMetadata']['version_order']}
 
     save_to_file('bug_persistence.json', json.dumps(results))
 

### 2013-02-17 analysis/repo-statistics/build_dep_graph.py
added project versions

@@ -4,7 +4,7 @@ from helpers.mongo_helper import MongoDocumentIterator
 from helpers.data_helper import save_to_file
 
 #
-# This script generates the "data/projects.json", which is a json dict (object)
+# This script generates the "data/project_versions.json", which is a json dict (object)
 # with the following structure {<group_id>||<artifact_id> : version_count}
 #
 

### 2013-02-17 analysis/repo-statistics/find_projects.py

@@ -4,7 +4,7 @@ from helpers.mongo_helper import MongoDocumentIterator
 from helpers.data_helper import ArrayCount, save_to_file
 
 #
-# This script generates the "data/projects.json", which is a json dict (object)
+# This script generates the "data/project_versions.json", which is a json dict (object)
 # with the following structure {<group_id>||<artifact_id> : version_count}
 #
 
@@ -26,7 +26,7 @@ def main():
             results.incr(ga)
             print 'Working %d of %d' % (miter.count(), miter.total(),)
 
-    save_to_file('projects.json', json.dumps(results.get_series()))
+    save_to_file('project_versions.json', json.dumps(results.get_series()))
 
 
 if __name__ == "__main__":

### 2013-02-17 analysis/repo-statistics/helpers/data_helper.py

@@ -50,7 +50,7 @@ def load_projects_json():
     from models.project import Project
 
     if not os.path.exists('data/project_versions.json'):
-        print '[ERROR]: data/projects.json does not exist!'
+        print '[ERROR]: data/project_versions.json does not exist!'
         return []
 
     project_list = []

### 2013-02-17 analysis/repo-statistics/check_missing_local.py
added valid projects (for evolution) json list

@@ -1,10 +1,28 @@
 import os
+import zipfile
 import xmldict
 import sys
 
 from helpers.data_helper import load_projects_json
 
 from helpers.mongo_helper import get_version, get_mongo_connection, MONGO_COL
+
+
+def has_classes(filename):
+    try:
+        if zipfile.is_zipfile(filename):
+            z = zipfile.ZipFile(filename)
+            for f in z.namelist():
+                if f.endswith('.class'):
+                    print 'Valid JAR file: %s' % (filename,)
+                    return True
+        else:
+            print '%s is not a zipfile (has_classes)' % (filename,)
+
+        return False
+    except Exception, e:
+        return False
+
 
 def main():
     base_url = '/Users/bkarak/devel/repositories/maven/maven/'
@@ -48,6 +66,7 @@ def main():
                 else:
                     sys.stderr.write('ADDED: Total: %d, Missing: %d (%d)\n' % (total_jars, missing - really_missing, missing))
                     print "findbugs -textui -xml -output `basename %s`-findbugs.xml %s" % (local_jar_path, local_jar_path)
+
 
     sys.stderr.write('Total: %d, Missing: %d (%d)\n' % (total_jars, missing - really_missing, missing))
 

### 2013-02-17 analysis/repo-statistics/helpers/mongo_helper.py

@@ -76,7 +76,8 @@ class MongoProjectIterator(MongoDocumentIterator):
         if fields is not None:
             __f.extend(fields)
 
-        super(MongoProjectIterator, self).__init__(query=__q,fields=__f)
+        super(MongoProjectIterator, self).__init__(query=__q, fields=__f)
+        self.__documents = []
 
     def documents_list(self):
         docs = []
@@ -89,7 +90,21 @@ class MongoProjectIterator(MongoDocumentIterator):
 
         docs.sort(key=lambda doc: doc['JarMetadata']['version_order'])
 
-        return docs
+        for d in docs:
+            if d['JarMetadata']['version_order'] == 0:
+                self.__documents.append(d)
+
+        return self.__documents
+
+    def valid(self):
+        c = 1
+
+        for d in self.__documents:
+            if d['JarMetadata']['version_order'] != c:
+                return False
+            c += 1
+
+        return True
 
 
 def get_mongo_connection():

### 2013-02-17 analysis/repo-statistics/valid_projects.py

@@ -1,0 +1,33 @@
+import json
+from helpers.data_helper import load_projects_json, save_to_file
+from helpers.mongo_helper import MongoProjectIterator
+
+
+def main():
+    projects = load_projects_json()
+    valid_projects = []
+    total = len(projects)
+    valid = 0
+    counter = 0
+
+    for p in projects:
+        counter += 1
+        key = '%s||%s' % (p.group_id(), p.artifact_id())
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.version_order'])\
+
+        piter.documents_list()
+        print '[%d:%d:%d] Checking ... %s' % (counter, valid, total, key),
+
+        if piter.valid():
+            valid_projects.append(key)
+            print ' ... Valid'
+            valid += 1
+        else:
+            print ' ... Invalid'
+
+    print 'Total: %d, Valid: %d' % (total, valid)
+    save_to_file('valid_projects.json', json.dumps(valid_projects))
+
+
+if __name__ == "__main__":
+    main()

### 2013-02-17 analysis/repo-statistics/helpers/data_helper.py
added mongo helper

@@ -64,3 +64,22 @@ def load_projects_json():
     return project_list
 
 
+def load_evolution_projects_json():
+    from models.project import Project
+
+    if not os.path.exists('data/valid_projects.json'):
+        print '[ERROR]: data/valid_projects.json does not exist!'
+        return []
+
+    project_list = []
+    fp = open('data/valid_projects.json', 'r')
+    prj_json = json.load(fp)
+    fp.close()
+
+    for p in prj_json:
+        project_list.append(Project.parse_project(p, 0))
+
+    return project_list
+
+
+

### 2013-02-17 analysis/repo-statistics/helpers/mongo_helper.py

@@ -91,7 +91,7 @@ class MongoProjectIterator(MongoDocumentIterator):
         docs.sort(key=lambda doc: doc['JarMetadata']['version_order'])
 
         for d in docs:
-            if d['JarMetadata']['version_order'] == 0:
+            if d['JarMetadata']['version_order'] != 0:
                 self.__documents.append(d)
 
         return self.__documents

### 2013-02-17 analysis/repo-statistics/helpers/mongo_helper.py
updated version of valid projects

@@ -77,9 +77,13 @@ class MongoProjectIterator(MongoDocumentIterator):
             __f.extend(fields)
 
         super(MongoProjectIterator, self).__init__(query=__q, fields=__f)
+        self.__evol_documents = []
         self.__documents = []
 
-    def documents_list(self):
+    def evolution_list(self):
+        if len(self.__evol_documents) > 0:
+            return self.__evol_documents
+
         docs = []
 
         while self.has_next():
@@ -92,11 +96,30 @@ class MongoProjectIterator(MongoDocumentIterator):
 
         for d in docs:
             if d['JarMetadata']['version_order'] != 0:
+                self.__evol_documents.append(d)
+
+        return self.__evol_documents
+
+    def documents_list(self):
+        if len(self.__documents) > 0:
+            return self.__documents
+
+        self.__documents = []
+
+        while self.has_next():
+            d = self.next()
+
+            if d is not None:
                 self.__documents.append(d)
+
+        self.__documents.sort(key=lambda doc: doc['JarMetadata']['version_order'])
 
         return self.__documents
 
     def valid(self):
+        if len(self.__evol_documents) == 0:
+            return False
+
         c = 1
 
         for d in self.__documents:

### 2013-02-17 analysis/repo-statistics/valid_projects.py

@@ -15,15 +15,15 @@ def main():
         key = '%s||%s' % (p.group_id(), p.artifact_id())
         piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.version_order'])\
 
-        piter.documents_list()
+        piter.evolution_list()
         print '[%d:%d:%d] Checking ... %s' % (counter, valid, total, key),
 
         if piter.valid():
             valid_projects.append(key)
-            print ' ... Valid'
+            print ' ... Valid (%d versions)' % (len(piter.evolution_list()))
             valid += 1
         else:
-            print ' ... Invalid'
+            print ' ... Invalid (%d versions)' % (len(piter.evolution_list()))
 
     print 'Total: %d, Valid: %d' % (total, valid)
     save_to_file('valid_projects.json', json.dumps(valid_projects))

### 2013-03-10 docs/msr.tex
updated numbers in data provenance

@@
 \{dimitro, bkarak, louridas, dds\}@aueb.gr}\\
-\IEEEauthorblockA{\IEEEauthorrefmark{2}TODO: Add Affiliation here\\
+\IEEEauthorblockA{\IEEEauthorrefmark{2}
+Software Engineering Research Group\\
 Delft University of Technology\\
@@
 Projects & 17,505\\
-Versions (total) & 114,399\\
+Versions (total) & 115,214\\
 Min & 1\\
-Max & 337\\
-Mean & 6.54\\
+Max & 338\\
+Mean & 6.58\\
 Median & 3\\
-Range & 336\\
+Range & 337\\
 1$^{st}$ Quartile & 1\\
@@
 before invoking FindBugs. After the project filtering we narrowed down
-our data set to 17,055 projects with 114,399 versions.
+our data set to 17,055 projects with 115,214 versions.
 Table~\ref{tbl:repository} summarises the data set information and
@@
 versions and only a few with hundreds of versions. The maximum number of
-versions for a project is 337. The 3$^{rd}$ quartile measurement
+versions for a project is 338. The 3$^{rd}$ quartile measurement
 also indicated that 75\% (13,129) of the projects have a maximum of 8 versions.

### 2013-03-10 analysis/repo-statistics/bug_correlation.py
fixed bug in correlation counters

@@ -84,7 +84,8 @@ def main():
                 if signature not in bug_list:
                     bug_list.append(signature)
                     proj_array_count.incr(bug_category)
-                    proj_array_count.incr('TOTAL_' + bug_category)
+                
+                proj_array_count.incr('TOTAL_' + bug_category)
 
         print proj_array_count.get_series()
         results['%s||%s' % (p.group_id(), p.artifact_id())] = proj_array_count.get_series()

### 2013-03-10 analysis/repo-statistics/create_category_totals.py
added bug_correlation_counters_full.json

@@ -14,7 +14,13 @@ def main():
             for (key, value) in v.iteritems():
                 totals.incr(key, delta=value)
 
-    total = 7008859
+    total = 0
+
+    for (k, v) in totals.get_series().iteritems():
+        if k.startswith('TOTAL_'):
+            total += v
+
+    print 'Total: %d' % (total,)
 
     for (k, v) in totals.get_series().iteritems():
         if k.startswith('TOTAL_'):

### 2013-03-11 analysis/repo-statistics/create_category_totals.py
updated figure

@@ -3,7 +3,7 @@ from helpers.data_helper import ArrayCount
 
 
 def main():
-    fp = open('data/bug_correlation_counters.json', 'r')
+    fp = open('data/bug_correlation_counters_full.json', 'r')
     json_corr = json.load(fp)
     fp.close()
 

### 2013-03-11 docs/evol.tex
added evol files; moved data in data directory
updated figure
some rearrangements, new citations

--- 2013-03-10 docs/msr.tex
@@
 a static analysis tool that examines bytecode to detect software bugs and has already been used in
-research~\cite{AP10, HP07, HP04}. Specifically, we ran FindBugs on all the project
+research~\cite{AP10, HP07, HP04, HW08}. Specifically, we ran FindBugs on all the project
 versions of all the projects that exist in the Maven\footnote{\url{http://maven.apache.org/}}
@@
 \label{sec:meth}
+
+%\begin{figure}
+%	\includegraphics{arch.pdf}
+%\end{figure}
 
@@
 
-Another observation involves bugs that we could call {\it
-severe}. Such bugs are related to vulnerabilities that appear due to the lack of user-input
-validation and can lead to damaging attacks like {\sc sql} injection~\cite{RL12} and
-Cross-Site Scripting~\cite{WS08}. Note that to exploit such vulnerabilities, a malicious user does
-not have to know anything about the applications internals. For all the other
-bugs, another program should be written either to incorporate references to
-mutable objects, access non-final fields and others. In addition, as
-bug descriptions indicate,\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
-if an application has bugs like these, it might have more vulnerabilities that FindBugs doesn't
-report. Table~\ref{tbl:sev} presents the number of {\sc jar}s where at least one of these
-bugs exists. In the following section we provide results separately for this
-subcategory.
-
 \begin{table*}
@@
 bugs that is presented in the upcoming section.
+
+Another observation involves bugs that we could call {\it
+severe}. Such bugs are related to vulnerabilities that appear due to the lack of user-input
+validation and can lead to damaging attacks like {\sc sql} injection~\cite{RL12} and
+Cross-Site Scripting~\cite{WS08}. Note that to exploit such vulnerabilities, a malicious user does
+not have to know anything about the applications internals. For all the other
+bugs, another program should be written either to incorporate references to
+mutable objects, access non-final fields and others. In addition, as
+bug descriptions indicate,\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
+if an application has bugs like these, it might have more vulnerabilities that FindBugs doesn't
+report. Table~\ref{tbl:sev} presents the number of {\sc jar}s where at least one of these
+bugs exists. In the following section we provide results separately for this
+subcategory.
 
@@
 \bibliographystyle{IEEEtran}
-\bibliography{msr}
+\bibliography{evol}
 

### 2013-03-23 docs/evol.tex
add bug correlation discussion

@@
 \usepackage{subfigure}
+\usepackage{threeparttable}
 
@@
 
+To see whether bugs flock together we performed pairwise correlations
+between all bug categories. We calculated the correlations between the
+number of distinct bugs that appeared in a project throughout its
+lifetime. The resulting correlation plot can be seen in
+Figure~\ref{fig:corrplot}. We found significant correlations between
+all pairs apart from those involving the {\it Security Low} category,
+due to the small number of bugs in that category (19). The results
+show then that bugs do flock together: we do not find projects with
+only a certain kind of bug; bugs come upon projects in swarms of
+different kinds. Since the correlations with the {\it Security High}
+category are particularly high, the presence of other bugs should be a
+strong indicator to have a better look at security aspects of code.
+\begin{table}
+  \begin{threeparttable}
+    \centering
+    \caption{Correlation matrix}
+    \label{tbl:corrmatrix}
+    \input{corrmatrix.tex}
+    \begin{tablenotes}
+      \footnotesize
+      \item The matrix presents pairwise correlations between the
+        following bug categories in order: Security High, Security
+        Low, Style, Bad Practice, Correctness, MT Correctness,
+        Performance, i18n, Experimental
+    \end{tablenotes}
+  \end{threeparttable}
+\end{table}
+
+\begin{figure*}
+  \centering
+  \includegraphics[scale=0.6]{corrplot.pdf}
+  \caption{Correlation matrix plot for bug categories}
+  \label{fig:corrplot}
+\end{figure*}
+
 \section{Discussion}

### 2013-03-23 analysis/repo-statistics/bug_correlation_calc.py

@@ -41,8 +41,25 @@ for i in xrange(num_bug_types):
         jcolumn = bug_types[j]
         data_pair = data[[icolumn, jcolumn]].dropna()
         (corr, pvalue) = st.pearsonr(data_pair[icolumn], data_pair[jcolumn])
-        print icolumn, jcolumn, corr, pvalue
+        print icolumn, jcolumn, corr, pvalue        
         corrmatrix[i, j] = corrmatrix[j, i] = corr
         pvalues[i, j] = pvalues[j, i] = pvalue
 
-corrplot(corrmatrix, pvalues, bug_types)
+
+print r"""
+\begin{tabular}{ccccccccc}
+\hline \\
+"""
+
+for row in corrmatrix:
+    print ' & '.join(map('{:.2f}'.format, row)), r'\\'
+
+print r"""
+\hline \\
+\end{tabular}
+"""
+plot = corrplot(corrmatrix, pvalues, bug_types)
+
+plot.tight_layout()
+plot.savefig('corrplot.pdf', format='pdf')
+plot.show()

### 2013-03-23 docs/evol.tex
minor corrections

@@
 number of distinct bugs that appeared in a project throughout its
-lifetime. The resulting correlation plot can be seen in
+lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
 Figure~\ref{fig:corrplot}. We found significant correlations between
@@
         Low, Style, Bad Practice, Correctness, MT Correctness,
-        Performance, i18n, Experimental
+        Performance, i18n, Experimental.
     \end{tablenotes}

### 2013-03-27 docs/evol.tex
correlation following correct security categories

@@
 Figure~\ref{fig:corrplot}. We found significant correlations between
-all pairs apart from those involving the {\it Security Low} category,
-due to the small number of bugs in that category (19). The results
-show then that bugs do flock together: we do not find projects with
-only a certain kind of bug; bugs come upon projects in swarms of
-different kinds. Since the correlations with the {\it Security High}
-category are particularly high, the presence of other bugs should be a
-strong indicator to have a better look at security aspects of code.
+all pairs apart from two pairs involving the {\it Security High}
+category. In general, the {\it Security High} category showed the
+weekest correlations with the other categories. In general though, the
+results show then that bugs do flock together: we do not find projects
+with only a certain kind of bug; bugs come upon projects in swarms of
+different kinds.
 \begin{table}

### 2013-03-27 analysis/repo-statistics/bug_correlation_calc.py

@@ -13,6 +13,7 @@ from corrplot import corrplot
 bug_types = [
     'SECURITY_HIGH',
     'SECURITY_LOW',
+    'MALICIOUS_CODE',
     'STYLE',
     'BAD_PRACTICE',
     'CORRECTNESS',
@@ -21,15 +22,34 @@ bug_types = [
     'I18N',
     'EXPERIMENTAL'
     ]
-    
+
+labels = []
+for bug_type in bug_types:
+    if bug_type == 'I18N':
+        labels.append(bug_type.lower())
+    elif bug_type == 'MT_CORRECTNESS':
+        labels.append('MT Correctness')
+    elif bug_type == 'MALICIOUS_CODE':
+        pass
+    else:
+        labels.append(bug_type.title().replace('_', ' '))
+
 with open("data/bug_correlation_counters.json") as infile:
     json_input = json.load(infile)
 
 data = pd.DataFrame(json_input).T
-data['SECURITY_HIGH'] = data['SECURITY_HIGH'] + data['MALICIOUS_CODE']
-data['TOTAL_SECURITY_HIGH'] = (data['TOTAL_SECURITY_HIGH']
-                               + data['TOTAL_MALICIOUS_CODE'])
+
+for bug_type in bug_types:
+    print bug_type, data[bug_type].count()
+
+print "MALICIUS_CODE & SECURITY_LOW ", len(data[data['MALICIOUS_CODE']
+                                                * data['SECURITY_LOW'] > 0])
+    
+data['SECURITY_LOW'] = (data['MALICIOUS_CODE'].fillna(0)
+                        + data['SECURITY_LOW'].fillna(0)).replace(0, np.nan)
+data['TOTAL_SECURITY_LOW'] += data['TOTAL_MALICIOUS_CODE']
 data = data.drop(['MALICIOUS_CODE', 'TOTAL_MALICIOUS_CODE'], axis=1)
+bug_types.remove('MALICIOUS_CODE')
 
 num_bug_types = len(bug_types)
 corrmatrix = np.identity(num_bug_types)
@@ -41,7 +61,9 @@ for i in xrange(num_bug_types):
         jcolumn = bug_types[j]
         data_pair = data[[icolumn, jcolumn]].dropna()
         (corr, pvalue) = st.pearsonr(data_pair[icolumn], data_pair[jcolumn])
-        print icolumn, jcolumn, corr, pvalue        
+        print "{} ({}) {} ({}) {} {}".format(icolumn, data[icolumn].count(),
[…]

### 2013-03-27 docs/evol.tex
correct correlation matrix

@@
 category. In general, the {\it Security High} category showed the
-weekest correlations with the other categories. In general though, the
-results show then that bugs do flock together: we do not find projects
-with only a certain kind of bug; bugs come upon projects in swarms of
-different kinds.
+weekest correlations with the other categories. Our results show that
+in general bugs do flock together. We do not find projects with only a
+certain kind of bug; bugs come upon projects in swarms of different
+kinds. Bugs of the {\it Security High} category, though, are
+different: they are either not associated with other bugs, or only
+weakly so. Perhaps it takes a special kind of blunder to make it a
+security hazard.
 \begin{table}

### 2013-04-01 docs/evol.tex
new style

@@
-\documentclass[conference]{IEEEtran}
+\documentclass[conference]{llncs}
 
@@
 
-\author{
-\IEEEauthorblockN{Dimitris Mitropoulos\IEEEauthorrefmark{1}, Vassilios Karakoidas\IEEEauthorrefmark{1},
-Georgios Gousios\IEEEauthorrefmark{2}, Panagiotis Louridas\IEEEauthorrefmark{1},
-Diomidis Spinellis\IEEEauthorrefmark{1}}\\
-\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Management Science and Technology\\
+\title{Dismal Code: Studying the Evolution of Security Bugs}
+
+\author{Dimitris Mitropoulos    \and
+       Vassilios Karakoidas	\and
+       Georgios Gousios         \and
+       Panos Louridas		\and
+       Diomidis Spinellis
+}
+\institute{
+       	Department of Management Science and Technology\\
 	Athens University of Economics and Business\\
-\{dimitro, bkarak, louridas, dds\}@aueb.gr}\\
-\IEEEauthorblockA{\IEEEauthorrefmark{2}
+      	\email{\{dimitro, bkarak, louridas, dds\}@aueb.gr}\\
 	Software Engineering Research Group\\
 	Delft University of Technology\\
-G.Gousios@tudelft.nl}}
-
-\title{Dismal Code: Studying the Evolution of Security Bugs}
+	\email{G.Gousios@tudelft.nl}
+}
 
@@
 
-\begin{IEEEkeywords}
+\begin{keywords}
 Software Bugs, Static Analysis, Software Evolution, Software
 Security, Maven, FindBugs.
-\end{IEEEkeywords}
-
-\IEEEpeerreviewmaketitle
+\end{keywords}
 
@@
 A security bug is a programming error that introduces a potentially
-exploitable weakness into a computer system~\cite{SSL12, TJBD11}. This weakness could lead to a
+exploitable weakness into a computer system~\cite{SSL12}\cite{TJBD11}. This weakness could lead to a
 security breach with unfortunate consequences in different layers, like databases,
@@
 effort to detect and eliminate such bugs~\cite{SZ12}, little attention has been paid to
-study them in relation to software evolution~\cite{L96, LRWPT97, IB06, RGMA06}.
+study them in relation to software evolution~\cite{L96}\cite{LRWPT97}\cite{IB06}\cite{RGMA06}.
 In this paper we present how we used a large software ecosystem to analyze
@@
 a static analysis tool that examines bytecode to detect software bugs and has already been used in
-research~\cite{AP10, HP07, HP04, HW08}. Specifically, we ran FindBugs on all the project
+research~\cite{AP10}\cite{HP07}\cite{HP04}\cite{HW08}. Specifically, we ran FindBugs on all the project
 versions of all the projects that exist in the Maven\footnote{\url{http://maven.apache.org/}}
@@
 the relation between a version's size and its' security bugs knowing the
-that research has been contradictory on the the issue~\cite{BP84, SYTP85,
-NBZ06, GKMS00}. Finally, we examined the Maven ecosystem as a whole from a security
+that research has been contradictory on the the issue~\cite{BP84}\cite{SYTP85},
+\cite{NBZ06}\cite{GKMS00}. Finally, we examined the Maven ecosystem as a whole from a security
 perspective. Its structure, gave us the oportunity to see if a project version that is a dependency to
@@
 number of distinct bugs that appeared in a project throughout its
-lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
+lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} andsplncs.bst
 Figure~\ref{fig:corrplot}. We found significant correlations between
@@
 regarding the evolution history of a project~\cite{HG05}. Bhattacharya et
-al.~\cite{BN11, B11} proposed a framework that is based upon
+al.~\cite{BN11}\cite{B11} proposed a framework that is based upon
 recursively enumerable languages. The framework can correlate software
@@
 
-\bibliographystyle{IEEEtran}
+\bibliographystyle{splncs}
 \bibliography{evol}

### 2013-04-02 docs/evol.tex
more on the paper

@@
 requirements but a security bug can allow a malicious user to alter the execution
-of the entire application. In this case, such bugs could span a wide
+of the entire application for his or her own gain. In this case, such bugs could span a wide
 range of security and privacy issues, like viewing sensitive information, the destruction or
@@
 addition, we wanted to investigate other critical features associated with such
-vulnerabilities like the persistency of a bug. In essence, to check if specific bugs stay
+vulnerabilities like the persistency of a bug. In essence, to check if critical bugs stay
 unresolved for a long time. Also, we wanted to elaborate more on the relation of security
@@
 the relation between a version's size and its' security bugs knowing the
-that research has been contradictory on the the issue~\cite{BP84}\cite{SYTP85},
-\cite{NBZ06}\cite{GKMS00}. Finally, we examined the Maven ecosystem as a whole from a security
+that research has been contradictory on the the
+issue~\cite{BP84}\cite{SYTP85}\cite{NBZ06}\cite{GKMS00}.
+Finally, we examined the Maven ecosystem as a whole from a security
 perspective. Its structure, gave us the oportunity to see if a project version that is a dependency to
@@
 The main contributions of this research are:
-
 \begin{itemize}
@@
 	\item Security bug persistense between versions. We show evidence that
-specific bugs are not eliminated between versions.
+security bugs are not eliminated between versions.
 	\item We show evidence of the relation between security bugs and a project
@@
 	\item The correlation of security bugs with other bug categories. We
-show evidence that such bugs are correlated with bugs that have to do with
+show evidence on how such bugs are correlated with bugs that have to do with
 performance, coding practices and others.
@@
 
-In the rest of this paper we
-describe the processing of our data and our experiment (Section \ref{sec:meth}),
-present and discuss the results we obtained (Section \ref{sec:res}),
-outline related work (Section \ref{sec:rel}),
-and end up with a conclusion and directions for future work (Section \ref{sec:con}).
+% In the rest of this paper we
+% describe the processing of our data and our experiment (Section \ref{sec:meth}),
+% present and discuss the results we obtained (Section \ref{sec:res}),
+% outline related work (Section \ref{sec:rel}),
+% and end up with a conclusion and directions for future work (Section \ref{sec:con}).
 
@@
 
+Our experiment involved the collection of the metric results of the FindBugs
+tool. Before and during the experiment, we performed a number of functional
+fits on the data for reasons that we will describe below.
+
 \subsection{Experiment}
@@
 
-Our experiment goal was to collect the metric results of the FindBugs tool.
-The process involved four entities (see Table~\ref{tbl:exp}):
+Our experiment involved four entities (see Table~\ref{tbl:exp}):
 a number of {\it workers}, a {\it task queue}
@@
 \hline
- & Software Package & version\\
+Entity & Software Package & Version\\
 \hline
@@
 A typical processing cycle of a worker included the following steps: after
-the worker spawns, it requests a task from the queue. This task contains
-the {\sc jar} name, which is typically a project version that is downloaded locally.
-First, specific {\sc jar} metadata are calculated and stored. Such metadata include
-its size, its dependencies, and a number that represents the chronological order of the
-release. This order is derived from an {\sc xml} file that
+the worker spawned, it requested a task from the queue. This task contained
+the {\sc jar} name, which was typically a project version that was downloaded locally.
+First, specific {\sc jar} metadata were calculated and stored. Such metadata included
+its size, its dependencies, and a number that represented the chronological order of the
+release. This order was derived from an {\sc xml} file that
 accompanies every project in the Maven repository called {\it
-maven-metadata.xml}. Then FindBugs is executed and its results are also stored
-in the data repository. When the task is completed the queue is notified and
-the next task is requested.
+maven-metadata.xml}. Then, FindBugs was executed and its results were also stored
+in the data repository. When the task was completed the queue was notified and
+the next task was requested.
 
@@
 
-The subject of our study was the Maven repository. Before analyzing the data of the
-repository we performed a number of functional fits on the data.
-
 Initially, we obtained a snapshot (January 2012) of the Maven repository and
@@
 for every {\sc jar} the worker checked if there were any {\it .class} files
-before invoking FindBugs. After the project filtering we narrowed down
+before invoking FindBugs. After the project filtering, we narrowed down
 our data set to 17,055 projects with 115,214 versions.
@@
 Table~\ref{tbl:bug-cat}). Two of them involve security: {\it Security} and {\it
-Malicious Code}. From the total number of the artifacts, 4,270 of them contained
+Malicious Code}. From the total number of the {\sc jar}s, 4,353 of them contained
 at least one bug coming from the first category
-and 45,145 coming from the second.
+and 45,559 coming from the second.
 
@@
 that programmers write code that implements the required functionality without considering
-its many security aspects. In the following section we
-show the correlation of security bugs with all the other categories. An interesting observation is
-that 5,601 (31.99\%) projects, containing 32,689 artifacts (28.57\%), did not
-have any bugs at all. These cases involved small artifacts with a minimum number of classes.
-This goes along with the relationship between the size of an artifact and it's
-bugs that is presented in the upcoming section.
+its many security aspects.
+% An interesting observation is that 4,908 projects did not
+% have any bugs at all. These cases involved small artifacts with a minimum number of classes.
+% This goes along with the relationship between the size of an artifact and it's
+% bugs that is presented in the upcoming section.
 
+% dimitro@dds: maybe you want to add something here?
 Another observation involves bugs that we could call {\it
-severe}. Such bugs are related to vulnerabilities that appear due to the lack of user-input
+severe} and they are a subset of the {\it Security} category.
+Such bugs are related to vulnerabilities that appear due to the lack of user-input
 validation and can lead to damaging attacks like {\sc sql} injection~\cite{RL12} and
@@
 bugs exists. In the following section we provide results separately for this
-subcategory.
+subcategory which we call {\it Security High}. The remaining bugs of the {\it Security} category
+are grouped together with the bugs of the {\it Malicious Code} category in another subcategory that
+we call {\it Security Low}.
 
@@
 dependencies of every version. Based on this information we created a graph
-that represented the snapshot of the repository that we were analyzing. The
+that represented the snapshot of the Maven repository. The
 nodes of the graph represented the versions and the vertices their dependencies.
-We have to mention here that the graph is not representative. For instance, if
+We have to mention here that the graph was not representative. For instance, if
 a dependency was pointing only to a project (and not to a specific version), we chose to
@@
 complete. This is because threre were missing versions.
-Practically, the corresponding {\it pom}, or {\it war} files existed on the
-repository, but the {\sc jar} file did not. From the 56,5680 vertices, 191,433
-belonged to the first category while 16,4234 belonged to the second. Finally,
-the graph contained 80,354 nodes. Obviously the number does not correspond to
+% Practically, the corresponding {\it pom}, or {\it war} files existed on the
+% repository, but the {\sc jar} file did not.
+From the 56,5680 vertices, 191,433
+belonged to the first case while 16,4234 belonged to the second.
+The graph contained 80,354 nodes. Obviously, the number does not correspond to
 the number of the total versions (see Section~\ref{sec:data}). This is because
@@
 algorithm~\cite{BP98} on it and retrieved all PageRanks for every node. Then we
-examined the security bugs of the 50 most popular nodes based on their PageRank.
-33 of them contained security bugs while two of them contained severe bugs.
-Finally, 25 of them were latest versions at the time.
+examined the security bugs of the fifty most popular nodes based on their PageRank.
+Thirty three of them contained bugs coming from the {\it Security Low} subcategory,
+while two of them contained severe bugs. Twenty five of them were latest
+versions at the time.
+% what can we say about this?
 
@@
 \subsubsection{The Relation of Defects with the size of an Artifact}
+% in a recent paper, Spacco et al.~\cite{SHP06} showed the relation of bugs
+% in general, with the size of every version of Sun's {\sc jdk}.
 
@@
 security hazard.
+
 \begin{table}
-  \begin{threeparttable}
     \centering
@@
     \end{tablenotes}
-  \end{threeparttable}
 \end{table}
@@
 
-The project is being co-financed by the European Regional Development Fund (ERDF)
+This research has been co-financed by the European Union (European Social Fund
+--– {\sc esf}) and Greek national funds through the Operational Program
+``Education and Lifelong Learning'' of the National Strategic Reference Framework –
+Research Funding Program: Heracleitus II. Investing in knowledge society
+through the {\sc esf}.
+
+The project has been also co-financed by the European Regional Development Fund ({\sc erdf})
 and national funds and is a part of the Operational Programme ``Competitiveness \&
-Entrepreneurship" (OPCE II), Measure ``COOPERATION" (Action I).
+Entrepreneurship" ({\sc opce} II), Measure ``{\sc cooperation}" (Action I).
 

### 2013-04-02 docs/evol.tex
info about Maven - minor changes

@@
 research~\cite{AP10}\cite{HP07}\cite{HP04}\cite{HW08}. Specifically, we ran FindBugs on all the project
-versions of all the projects that exist in the Maven\footnote{\url{http://maven.apache.org/}}
-repository (approximately 265GB of data). Then we observed the changes that
+versions of all the projects that exist in the
+{\it Maven Central Repository}\footnote{\url{http://search.maven.org/}}
+(approximately 265GB of data). Then we observed the changes that
 involved the security bugs and their characteristics. This research builds upon
@@
 bugs must decrease as a project evolves since they are critical and developers
-should eliminate them.
+should eliminate them.http://search.maven.org/
 	\item Security bug persistense between versions. We show evidence that
@@
 tool. Before and during the experiment, we performed a number of functional
-fits on the data for reasons that we will describe below.
+fits on the data coming from the Maven repository,
+http://search.maven.org/for reasons that we will describe below.
 
@@
 a number of {\it workers}, a {\it task queue}
-mechanism,\footnote{\url{http://www.rabbitmq.com/}}
-a {\it data repository},\footnote{\url{http://www.mongodb.org/}}
-and the {\it code repository}, which in our case it was the public Maven 
-repository\footnote{\url{http://mvnrepository.com}}.
+mechanism, a {\it data repository}, and the {\it code repository},
+which in our case it was the public Maven repository.
 
@@
 \centering
+\begin{threeparttable}
 \caption{Experiment Entities}
 \label{tbl:exp}
-\begin{tabular}{r r r}
+\begin{tabular}{l r r}
 \hline
@@
 Worker & Custom Python Script & 2.7\\
-Task Queue & RabbitMQ & 3.0.1 \\
-Data Repository & MongoDB & 2.2 \\
-Code Repository & Maven Repository & January 2012 \\
+Task Queue & RabbitMQ\tnote{1} & 3.0.1 \\
+Data Repository & MongoDB\tnote{2} & 2.2 \\
+Code Repository & Maven Central Repository\tnote{3} & January 2012 \\
 \hline
 \end{tabular}
+ \begin{tablenotes}
+       	\item[1] \url{http://www.rabbitmq.com/}
+       	\item[2] \url{http://www.mongodb.org/}
+	\item[3] \url{http://mvnrepository.com}
+   \end{tablenotes}
+\end{threeparttable}
 \end{table}
@@
 accompanies every project in the Maven repository called {\it
-maven-metadata.xml}. Then, FindBugs was executed and its results were also stored
-in the data repository. When the task was completed the queue was notified and
-the next task was requested.
+maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
+also stored in the data repository. When the task was completed the queue
+was notified and the next task was requested.
 
@@
 \end{table}
+
+Maven is a build automation tool used primarily for Java projects and it is
+hosted by the Apache Software Foundation.\footnote{\url{http://www.apache.org/}}
+To describe the software project being built, its dependencies
+on other external modules, the build order, and required plug-ins Maven uses
+{\sc xml}. To build a software component, it dynamically downloads Java libraries
+and Maven plug-ins from the Maven Central Repository,
+and stores them in a local cache. The repository can also be updated with new
+new projects but also with new versions of existing ones.
 

### 2013-04-02 docs/evol.tex
minor changes - fixes

@@
 {\it Maven Central Repository}\footnote{\url{http://search.maven.org/}}
-(approximately 265GB of data). Then we observed the changes that
-involved the security bugs and their characteristics. This research builds upon
-our earlier work on the topic~\cite{MGS12}.
+(approximately 265GB of data - see Section~\ref{sec:data}).
+Then we observed the changes that involved the security bugs and their characteristics.
+This research builds upon our earlier work on the topic~\cite{MGS12}.
 
@@
 bugs must decrease as a project evolves since they are critical and developers
-should eliminate them.http://search.maven.org/
+should eliminate them.
 	\item Security bug persistense between versions. We show evidence that
@@
 {\sc xml}. To build a software component, it dynamically downloads Java libraries
-and Maven plug-ins from the Maven Central Repository,
-and stores them in a local cache. The repository can also be updated with new
-new projects but also with new versions of existing ones.
+and Maven plug-ins from the Maven central repository,
+and stores them in a local cache. The repository can be updated with
+new projects and also with new versions of existing projects.
 
@@
 written in a way that leads to errors.\\
-Security & Contains two subcategories, namely: {\it Security} and {\it
-Malicious Code}. Involves code that could lead to security breach. \\
+Malicious Code & Involves variables or fields exposed to classes that should
+not be using them. \\
+Security & Involves input validation issues, unauthorized database connections
+and others. \\
 \hline
@@
 
-FindBugs separates software bugs into seven categories (see
-Table~\ref{tbl:bug-cat}). Two of them involve security: {\it Security} and {\it
-Malicious Code}. From the total number of the {\sc jar}s, 4,353 of them contained
+FindBugs separates software bugs into nine categories (see
+Table~\ref{tbl:bug-cat}). Two of them involve security issues: {\it Security} and {\it
+Malicious Code}. From the total number of versions, 4,353 of them contained
 at least one bug coming from the first category

### 2013-04-02 analysis/repo-statistics/bug_correlation_calc.py
save latex table to file

@@ -68,18 +68,20 @@ for i in xrange(num_bug_types):
         pvalues[i, j] = pvalues[j, i] = pvalue
 
 
-print r"""
+with open("corrmatrix.tex", "w") as corrmatrix_tex:
+    start = r"""
 \begin{tabular}{ccccccccc}
 \hline \\
 """
-
-for row in corrmatrix:
-    print ' & '.join(map('{:.2f}'.format, row)), r'\\'
-
-print r"""
+    corrmatrix_tex.write(start)
+    for row in corrmatrix:
+        table_row = ' & '.join(map('{:.2f}'.format, row)) +  r'\\' + '\n'
+        corrmatrix_tex.write(table_row)
+    end = r"""
 \hline \\
 \end{tabular}
 """
+    corrmatrix_tex.write(end)
 
 plot = corrplot(corrmatrix, pvalues, labels)
 

### 2013-04-02 analysis/repo-statistics/bug_correlation_calc.py
minor corrections

@@ -42,12 +42,14 @@ data = pd.DataFrame(json_input).T
 for bug_type in bug_types:
     print bug_type, data[bug_type].count()
 
-print "MALICIUS_CODE & SECURITY_LOW ", len(data[data['MALICIOUS_CODE']
+print "MALICIUS_CODE | SECURITY_LOW ", len(data[data['MALICIOUS_CODE']
                                                 * data['SECURITY_LOW'] > 0])
     
 data['SECURITY_LOW'] = (data['MALICIOUS_CODE'].fillna(0)
                         + data['SECURITY_LOW'].fillna(0)).replace(0, np.nan)
-data['TOTAL_SECURITY_LOW'] += data['TOTAL_MALICIOUS_CODE']
+data['TOTAL_SECURITY_LOW'] = (data['TOTAL_MALICIOUS_CODE'].fillna(0)
+                              + data['TOTAL_SECURITY_LOW'].fillna(0)
+                              ).replace(0, np.nan)
 data = data.drop(['MALICIOUS_CODE', 'TOTAL_MALICIOUS_CODE'], axis=1)
 bug_types.remove('MALICIOUS_CODE')
 

### 2013-04-02 docs/evol.tex
more changes

@@
 a static analysis tool that examines bytecode to detect software bugs and has already been used in
-research~\cite{AP10}\cite{HP07}\cite{HP04}\cite{HW08}. Specifically, we ran FindBugs on all the project
+research~\cite{AP10}\cite{HP07}\cite{HP04}\cite{HW08}\cite{SHP06}.
+Specifically, we ran FindBugs on all the project
 versions of all the projects that exist in the
@@
 forgetting to close a file. \\
-Internationalisation & Indicates the use of non-localized methods. \\
-Multi-Threaded Correctness & Thread synchronization issues. \\
+Internationalization (i18n) & Indicates the use of non-localized methods. \\
+Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
 Performance & Involves inefficient memory usageallocation, usage 
@@
 
-\subsubsection{The Relation of Defects with the size of an Artifact}
-% in a recent paper, Spacco et al.~\cite{SHP06} showed the relation of bugs
-% in general, with the size of every version of Sun's {\sc jdk}.
+\subsubsection{The Relation of Defects with the size of a {\sc jar}}
 
@@
     \input{corrmatrix.tex}
-    \begin{tablenotes}
-      \footnotesize
-      \item The matrix presents pairwise correlations between the
+    \small The matrix presents pairwise correlations between the
         following bug categories in order: Security High, Security
-        Low, Style, Bad Practice, Correctness, MT Correctness,
+        Low, Style, Bad Practice, Correctness, {\sc mt} Correctness,
         Performance, i18n, Experimental.
-    \end{tablenotes}
 \end{table}
@@
 
+% in a recent paper, Spacco et al.~\cite{SHP06} showed the relation of bugs
+% in general, with the size of every version of Sun's {\sc jdk}.
+
+The evolution of software artifacts has also been analyzed to {\it reduce the false
+alarms} of the various static analysis tools.
+% dimitro: more to come.
+
 Contrary to the above, our work focuses on the subset of security bugs.

### 2013-04-02 docs/evol.tex
minor change

@@
 a number of {\it workers}, a {\it task queue}
-mechanism, a {\it data repository}, and the {\it code repository},
-which in our case it was the public Maven repository.
+mechanism,\footnote{\url{http://www.rabbitmq.com/}}
+a {\it data repository},\footnote{\url{http://www.mongodb.org/}}
+and the {\it code repository}, which in our case it was
+the public Maven repository.
 
@@
 Worker & Custom Python Script & 2.7\\
-Task Queue & RabbitMQ\tnote{1} & 3.0.1 \\
-Data Repository & MongoDB\tnote{2} & 2.2 \\
+Task Queue & RabbitMQ & 3.0.1 \\
+Data Repository & MongoDB & 2.2 \\
 Code Repository & Maven Central Repository\tnote{3} & January 2012 \\
@@
 \end{tabular}
- \begin{tablenotes}
-       	\item[1] \url{http://www.rabbitmq.com/}
-       	\item[2] \url{http://www.mongodb.org/}
-	\item[3] \url{http://mvnrepository.com}
-   \end{tablenotes}
 \end{threeparttable}

### 2013-04-02 docs/evol.tex
fixes - more on the related work

@@
 tool. Before and during the experiment, we performed a number of functional
-fits on the data coming from the Maven repository,
-http://search.maven.org/for reasons that we will describe below.
+fits on the data coming from the Maven repository, for reasons that we will describe below.
 
@@
 Data Repository & MongoDB & 2.2 \\
-Code Repository & Maven Central Repository\tnote{3} & January 2012 \\
+Code Repository & Maven Central Repository & January 2012 \\
 \hline
@@
 
-% in a recent paper, Spacco et al.~\cite{SHP06} showed the relation of bugs
-% in general, with the size of every version of Sun's {\sc jdk}.
-
 The evolution of software artifacts has also been analyzed to {\it reduce the false
-alarms} of the various static analysis tools.
-% dimitro: more to come.
+alarms} of the various static analysis tools. To achieve this, Spacco et
+al.~\cite{SHP06} introduced {\it pairing} and {\it warning signatures}. In the
+former they tried to pair sets of bugs between versions in order to find
+similar patterns. In the latter they computed a signature for every bug. This
+signature contained elemnts like the name of the class where the bug was found,
+the method and others. Then they searched for similar signatures between
+versions. In their research they also studied the evolution of 116 sequential
+builds of the Sun Java Sevelopment Kit ({\sc jdk}). Their findings indicated that
+high priority bugs are fixed over time. To improve the precision of bug
+detection, Kim et al.~\cite{KE07b}\cite{KE07} an history-based warning
+prioritization algorithm by mining the warning fix experience of three
+different projects. The algorithm was based on the following hypothesis: if a
+bug that belongs to a specific category is eliminated by a code change, then
+this warning category is important. Working towards the same direction Heckman
+et al.~\cite{HW09}\cite{HW08} have introduced benchmarks that use specific
+correlation algorithms and classification techniques to evaluate alert
+prioritization approaches.
 

### 2013-04-03 docs/evol.tex
relation between jarsize and defects count

@@
 
+We explored te relation between defects with the size of a project,
+measured by the size of its jar file by carrying out correlation tests
+between the size and the defect counts for each project and its
+version. The results, all statistically significant ($p \ll
+0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it Security
+  High} category stands out by having a remarkably lower effect than
+the other categories, even {\it Security Low} that nearly tops the
+list.
+
+\begin{table}
+    \centering
+    \caption{Correlations between jarsize and Defects Count}
+    \label{tbl:jarsizecorr}
+    \input{jarsizecorr.tex}
+\end{table}
+
 \subsubsection{Security Bugs {\sc vs} Other Bug Categories}

### 2013-04-03 analysis/repo-statistics/bug_correlation_calc.py

@@ -42,7 +42,7 @@ data = pd.DataFrame(json_input).T
 for bug_type in bug_types:
     print bug_type, data[bug_type].count()
 
-print "MALICIUS_CODE | SECURITY_LOW ", len(data[data['MALICIOUS_CODE']
+print "MALICIUS_CODE & SECURITY_LOW ", len(data[data['MALICIOUS_CODE']
                                                 * data['SECURITY_LOW'] > 0])
     
 data['SECURITY_LOW'] = (data['MALICIOUS_CODE'].fillna(0)
@@ -79,8 +79,7 @@ with open("corrmatrix.tex", "w") as corrmatrix_tex:
     for row in corrmatrix:
         table_row = ' & '.join(map('{:.2f}'.format, row)) +  r'\\' + '\n'
         corrmatrix_tex.write(table_row)
-    end = r"""
-\hline \\
+    end = r"""\hline \\
 \end{tabular}
 """
     corrmatrix_tex.write(end)

### 2013-04-03 analysis/repo-statistics/project_counters_jarsize_calc.R

@@ -1,42 +1,8 @@
-library(lattice)
-jarsize.counts <- read.csv('data/project_counters_jarsize.csv')
-
-forplot <- make.groups(
-             security.high = data.frame(value = jarsize.counts$SECURITY_HIGH,
-               jarsize = jarsize.counts$jarsize),
-             security.low = data.frame(value = jarsize.counts$SECURITY_LOW,
-               jarsize = jarsize.counts$jarsize),
-             style =  data.frame(value = jarsize.counts$STYLE,
-               jarsize = jarsize.counts$jarsize), 
-             malicious.code = data.frame(value = jarsize.counts$MALICIOUS_CODE,
-               jarsize = jarsize.counts$jarsize), 
-             correctness = data.frame(value = jarsize.counts$CORRECTNESS,
-               jarsize = jarsize.counts$jarsize), 
-             bad.practice = data.frame(value = jarsize.counts$BAD_PRACTICE,
-               jarsize = jarsize.counts$jarsize), 
-             mt.correctness = data.frame(value = jarsize.counts$MT_CORRECTNESS,
-               jarsize = jarsize.counts$jarsize), 
-             i18n = data.frame(value = jarsize.counts$I18N,
-               jarsize = jarsize.counts$jarsize), 
-             performance = data.frame(value = jarsize.counts$PERFORMANCE,
-               jarsize = jarsize.counts$jarsize), 
-             experimental = data.frame(value = jarsize.counts$EXPERIMENTAL,
-               jarsize = jarsize.counts$jarsize))
+jarsize.counts <- read.csv('data/project_counters_jarsize.csv',
+                           header=TRUE)
 
 for (i in names(jarsize.counts)[4:length(colnames(jarsize.counts))]) {
   cor.result = cor.test(jarsize.counts$jarsize, jarsize.counts[[i]])
   cor.result$data.name = paste("jarsize", "and", i)
   print(cor.result)
 }
-
-dev.new()
-pdf(file='data/project_counters_jarsize.pdf', width=7, height=7)
-print(xyplot(jarsize~value|which, data=forplot,
-             type = c("p", "r"),
-             scales = list(relation="free"),
-             pch=19,
-             cex=.2,
-             strip = strip.custom(strip.levels=TRUE,
-               horizontal=TRUE,
-               par.strip.text=list(cex=.8))))
-dev.off()

### 2013-04-03 analysis/repo-statistics/project_counters_jarsize_tab.py

@@ -6,36 +6,46 @@ import json
 import sys
 import csv
 
-bug_types = set()
+bug_types = [
+    'SECURITY_HIGH',
+    'SECURITY_LOW',
+    'STYLE',
+    'CORRECTNESS',
+    'BAD_PRACTICE',
+    'MT_CORRECTNESS',
+    'I18N',
+    'PERFORMANCE',
+    'EXPERIMENTAL',
+]
 
-def get_bug_type(prefix):
-    return prefix[prefix.rfind(".") + 1:]
-
-with open("data/project_counters.json", "r") as json_file:
-    json_input = json.load(json_file)
-    for project, data in json_input.iteritems():
-        for version in data['versions']:
-            counters = version['Counters']
-            for counter in counters:
-                bug_types.add(counter)
- 
-    with open("data/project_counters_jarsize.csv", "w") as csv_output:
-        csvwriter = csv.writer(csv_output)        
-        project_counts = {}
-        project_key = ""
-        row = ['project', 'version', 'jarsize']
-        for bug_type in bug_types:
-            row.append(bug_type)
-        csvwriter.writerow(row)
+with open("data/project_counters_jarsize.csv", "w") as csv_output:
+    csvwriter = csv.writer(csv_output)        
+    project_counts = {}
+    project_key = ""
+    row = ['project', 'version', 'jarsize']
+    for bug_type in bug_types:
+        row.append(bug_type)
+    csvwriter.writerow(row)
+    with open("data/project_counters.json", "r") as json_file:
+        json_input = json.load(json_file)
         for project, data in json_input.iteritems():
             for version in data['versions']:
                 meta_data = version['JarMetadata']                    
                 row = [project, meta_data['version_order'],
                        meta_data['jar_size']]
                 counters = version['Counters']
+                counters = version['Counters']
+                if 'MALICIOUS_CODE' in counters:
+                    malicious_code = counters.pop('MALICIOUS_CODE')
+                    if 'SECURITY_LOW' in counters:
+                        counters['SECURITY_LOW'] += malicious_code
+                    else:
+                        counters['SECURITY_LOW'] = malicious_code
+                security_low = 0
                 for bug_type in bug_types:
-                    bug_count = counters[bug_type] \
-                        if bug_type in counters else 'NA'
-                    row.append(bug_count)
+                    if bug_type in counters:
+                        row.append(counters[bug_type])
+                    else:
+                        row.append('NA')
                 csvwriter.writerow(row)
             

### 2013-04-03 docs/evol.tex
minor fixes

@@
 
-We explored te relation between defects with the size of a project,
-measured by the size of its jar file by carrying out correlation tests
+We explored te relation between defects with the size of a project version,
+measured by the size of its {\sc jar} file by carrying out correlation tests
 between the size and the defect counts for each project and its
@@
 number of distinct bugs that appeared in a project throughout its
-lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} andsplncs.bst
+lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
 Figure~\ref{fig:corrplot}. We found significant correlations between

### 2013-04-03 docs/evol.tex
minor changes in the related work section

@@
 al.~\cite{SHP06} introduced {\it pairing} and {\it warning signatures}. In the
-former they tried to pair sets of bugs between versions in order to find
-similar patterns. In the latter they computed a signature for every bug. This
+former, they tried to pair sets of bugs between versions in order to find
+similar patterns. In the latter, they computed a signature for every bug. This
 signature contained elemnts like the name of the class where the bug was found,
@@
 high priority bugs are fixed over time. To improve the precision of bug
-detection, Kim et al.~\cite{KE07b}\cite{KE07} an history-based warning
-prioritization algorithm by mining the warning fix experience of three
+detection, Kim et al.~\cite{KE07b}\cite{KE07} proposed a history-based warning
+prioritization algorithm by mining the history of bug-fixes of three
 different projects. The algorithm was based on the following hypothesis: if a
 bug that belongs to a specific category is eliminated by a code change, then
-this warning category is important. Working towards the same direction Heckman
+this warning category is important. Working towards the same direction, Heckman
 et al.~\cite{HW09}\cite{HW08} have introduced benchmarks that use specific
@@
 coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
-list,~\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
+list,\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
 Bugzilla entries and others. Their findings indicated that security bugs are

### 2013-04-03 docs/evol.tex
minor changes

@@
 \begin{keywords}
-Software Bugs, Static Analysis, Software Evolution, Software
+Security Bugs, Static Analysis, Software Evolution, Software
 Security, Maven, FindBugs.
@@
 security bugs (the sum of the {\it Security} and {\it Malicious Code}
-categories) are the most popular in the repository. This could be an indication
-that programmers write code that implements the required functionality without considering
-its many security aspects.
+categories) are the most popular in the repository ($\geq 22\%$).
+This could be an indication that programmers write code that implements the
+required functionality without considering its many security aspects.
 % An interesting observation is that 4,908 projects did not
@@
 \label{sec:dis}
+% also mention:
+% - the fact that we don't have the same number of versions in every project.
+% - tell about the graph and Linus.
 

### 2013-04-03 docs/evol.tex
Add architecture figure to text
minor changes

@@
 
-%\begin{figure}
-%	\includegraphics{arch.pdf}
-%\end{figure}
-
 Our experiment involved the collection of the metric results of the FindBugs
@@
 workers that checked out tasks from the queue, processed the data and stored the
-results to the data repository.
+results to the data repository (see Figure~\ref{fig:arch}).
+
+\begin{figure}[t]
+  \begin{center}
+    \includegraphics[scale=0.7]{figures/arch.pdf}
+  \end{center}
+  \caption{The Data Processing Architecture}
+  \label{fig:arch}
+\end{figure}
 
@@
 also stored in the data repository. When the task was completed the queue
-was notified and the next task was requested.
+was notified and the next task was requested. A schematic representation
+of the data processing architecture can be seen in Figure~\ref{fig:arch}.
 
@@
 \label{sec:data}
+
+Maven is a build automation tool used primarily for Java projects and it is
+hosted by the Apache Software Foundation.\footnote{\url{http://www.apache.org/}}
+To describe the software project being built, its dependencies
+on other external modules, the build order, and required plug-ins Maven uses
+{\sc xml}. To build a software component, it dynamically downloads Java libraries
+and Maven plug-ins from the Maven central repository,
+and stores them in a local cache. The repository can be updated with
+new projects and also with new versions of existing projects.
+
+Initially, we obtained a snapshot (January 2012) of the Maven repository and
+handled it locally to retreive a list of all the names of the project versions
+that existed in it. A project version can be uniquely identified by the triplet:
+{\it group id}, {\it artifact id} and {\it version}.
+Since FindBugs analyzes applications written in the Java
+programming language, and the Maven repository
+hosts projects from languages other than Java such as Scala, Groovy,
+Clojure etc. we filtered out such projects by performing a series of checks in
+the repository data and metadata.
 
@@
 \end{table}
-
-Maven is a build automation tool used primarily for Java projects and it is
-hosted by the Apache Software Foundation.\footnote{\url{http://www.apache.org/}}
-To describe the software project being built, its dependencies
-on other external modules, the build order, and required plug-ins Maven uses
-{\sc xml}. To build a software component, it dynamically downloads Java libraries
-and Maven plug-ins from the Maven central repository,
-and stores them in a local cache. The repository can be updated with
-new projects and also with new versions of existing projects.
-
-Initially, we obtained a snapshot (January 2012) of the Maven repository and
-handled it locally to retreive a list of all the names of the project versions
-that existed in it. A project version can be uniquely identified by the triplet:
-{\it group id}, {\it artifact id} and {\it version}.
-Since FindBugs analyzes applications written in the Java
-programming language, and the Maven repository
-hosts projects from languages other than Java such as Scala, Groovy,
-Clojure etc. we filtered out such projects by performing a series of checks in
-the repository data and metadata.
 

### 2013-04-03 docs/evol.tex
added Panos paper sugestion in the rel work section

@@
 
+Lu et al.~\cite{LAAL13} studied the {\it evolution of file-system code}.
+Specifically, they analyzed the changes of Linux file-system patches to extract
+bug patterns and categorize bugs based on their impact. Their findings
+indicated that the number of file-system bugs does not die down over time. By
+categorizing bugs they also showed the frequency of specific bugs in specific
+components.
+
 Contrary to the above, our work focuses on the subset of security bugs.

### 2013-04-04 docs/evol.tex
tiny change

@@
 workers that checked out tasks from the queue, processed the data and stored the
-results to the data repository (see Figure~\ref{fig:arch}).
+results to the data repository.
 

### 2013-04-04 docs/evol.tex
spell-checked paper; corrected various errors

@@
 
-\author{Dimitris Mitropoulos    \and
-       Vassilios Karakoidas	\and
-       Georgios Gousios         \and
-       Panos Louridas		\and
-       Diomidis Spinellis
-}
-\institute{
-       	Department of Management Science and Technology\\
+\author{Dimitris Mitropoulos \and Vassilios Karakoidas \and Georgios Gousios \and Panos Louridas \and Diomidis Spinellis }
+\institute{ Department of Management Science and Technology\\
 			Athens University of Economics and Business\\
@@
 			Delft University of Technology\\
-	\email{G.Gousios@tudelft.nl}
-}
+			\email{G.Gousios@tudelft.nl}}
 
@@
 study them in relation to software evolution~\cite{L96}\cite{LRWPT97}\cite{IB06}\cite{RGMA06}.
-In this paper we present how we used a large software ecosystem to analyze
+In this paper we present how we used a large software ecosystem to analyse
 how evolving software packages are related to the different types of security
@@
 and it costs~\cite{BCL08}. Specifically, a software bug can
-lead to a mulfunction of a software artifact that runs under specific
+lead to a malfunction of a software artifact that runs under specific
 requirements but a security bug can allow a malicious user to alter the execution
@@
 addition, we wanted to investigate other critical features associated with such
-vulnerabilities like the persistency of a bug. In essence, to check if critical bugs stay
+vulnerabilities like the persistence of a bug. In essence, to check if critical bugs stay
 unresolved for a long time. Also, we wanted to elaborate more on the relation of security
@@
 Finally, we examined the Maven ecosystem as a whole from a security
-perspective. Its structure, gave us the oportunity to see if a project version that is a dependency to
+perspective. Its structure, gave us the opportunity to see if a project version that is a dependency to
 a large number of others contains a high rate of security bugs.
-In this case we can strenghten the relationship between Linus' Law and
+In this case we can strengthen the relationship between Linus' Law and
 software security as Meneely et al. have already indicated~\cite{MW10}.
@@
 should eliminate them.
-	\item Security bug persistense between versions. We show evidence that
+	\item Security bug persistence between versions. We show evidence that
 security bugs are not eliminated between versions.
@@
 Initially, we obtained a snapshot (January 2012) of the Maven repository and
-handled it locally to retreive a list of all the names of the project versions
+handled it locally to retrieve a list of all the names of the project versions
 that existed in it. A project version can be uniquely identified by the triplet:
 {\it group id}, {\it artifact id} and {\it version}.
-Since FindBugs analyzes applications written in the Java
+Since FindBugs analyses applications written in the Java
 programming language, and the Maven repository
@@
 
-The statistical mesurements presented in Table~\ref{tbl:repository}
+The statistical measurements presented in Table~\ref{tbl:repository}
 indicate that we have 17,505 projects and the data set's median
@@
 Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
-Performance & Involves inefficient memory usageallocation, usage 
+Performance & Involves inefficient memory usage allocation, usage 
 of non-static classes. \\
@@
 
-Our findings can be analyzed at two levels. First, we discuss some
+Our findings can be analysed at two levels. First, we discuss some
 primary observations concerning the security bugs of the Maven repository as a whole.
@@
 	{\sc pt}: relative path traversal in servlet & 50\\
-	{\sc sql}: nonconstant string passed to execute method on an {\sc sql} & 1,817\\
-	{\sc sql}: a prepared statement is generated from a nonconstant String & 1,438\\
+	{\sc sql}: non-constant string passed to execute method on an {\sc sql} & 1,817\\
+	{\sc sql}: a prepared statement is generated from a non-constant String & 1,438\\
 	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 17\\
@@
 select the latest version found on the repository. Also, this graph is not
-complete. This is because threre were missing versions.
+complete. This is because there were missing versions.
 % Practically, the corresponding {\it pom}, or {\it war} files existed on the
@@
 
-\subsubsection{Persistense of Security Bugs}
+\subsubsection{Persistence of Security Bugs}
 
@@
     \centering
-    \caption{Correlations between jarsize and Defects Count}
+    \caption{Correlations between jar size and Defects Count}
     \label{tbl:jarsizecorr}
@@
 category. In general, the {\it Security High} category showed the
-weekest correlations with the other categories. Our results show that
+weakest correlations with the other categories. Our results show that
 in general bugs do flock together. We do not find projects with only a
@@
 extract useful conclusions. The key idea behind this concept is
-similar to ours: the combination of information like bug decriptions,
+similar to ours: the combination of information like bug descriptions,
 documentation and others with the information retrieved from either the source
@@
 the examination of all revisions of three open-source projects to extract bug
-introduction rates for each pattern. Gil et al.~\cite{GM05} analyzed the
+introduction rates for each pattern. Gil et al.~\cite{GM05} analysed the
 prevalence of micro patterns across five Sun {\sc jdk} versions to conclude that
@@
 recursively enumerable languages. The framework can correlate software
-bugs with developers in various ways. For instanse, return the list of
+bugs with developers in various ways. For instance, return the list of
 bugs fixed by a specific developer. Fischer et al.~\cite{FPG03} proposed
@@
 
-The evolution of software artifacts has also been analyzed to {\it reduce the false
+The evolution of software artifacts has also been analysed to {\it reduce the false
 alarms} of the various static analysis tools. To achieve this, Spacco et
@@
 similar patterns. In the latter, they computed a signature for every bug. This
-signature contained elemnts like the name of the class where the bug was found,
+signature contained elements like the name of the class where the bug was found,
 the method and others. Then they searched for similar signatures between
@@
 Lu et al.~\cite{LAAL13} studied the {\it evolution of file-system code}.
-Specifically, they analyzed the changes of Linux file-system patches to extract
+Specifically, they analysed the changes of Linux file-system patches to extract
 bug patterns and categorize bugs based on their impact. Their findings
@@
 Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
-security bugs with performance bugs. This was also done by analyzing the project's
+security bugs with performance bugs. This was also done by analysing the project's
 Bugzilla. Their research showed that security bugs require more experienced developers
-to be fixed. In addittion, they suggested that security bug fixes are more complex than the
+to be fixed. In addition, they suggested that security bug fixes are more complex than the
 fixes of performance and other bugs.
-Shahzad et al.~\cite{SSL12} analyzed large sets of vulnerability data-sets to observe
+Shahzad et al.~\cite{SSL12} analysed large sets of vulnerability data-sets to observe
 various features of the vulnerabilities that they considered critical. Such features
@@
 
-\section*{Acknowledgments}
+\section*{Acknowledgements}
 

### 2013-04-05 docs/evol.tex
add material on bug persistence

@@
 \usepackage{threeparttable}
+\usepackage{pdflscape}
+\usepackage{array}
 
@@
 
+To examine the relation between the persistence of different kinds of
+bugs, and of security bugs in particular, we used as a persistence
+indicator the number of versions a bug remains open in a project. We
+grouped the persistence numbers by bug categories and then performed
+both descriptive statistics and a Mann-Whitney U test among all bug
+category pairs. The results are presented in
+Table~\ref{tbl:bug_persistence}. Cells in brackets show pairs where no
+statistically significant difference was found.
+
+In general, although the average number of versions bugs in different
+bug categories remained opened was statistically different in many
+cases, the difference is not spectacular. In all cases a bug persists
+on average between two and three versions, with the difference being
+in the decimal digits.
+
+\begin{landscape}
+  \begin{table}
+    \centering
+    \caption{Bug Persistence Comparison}
+    \label{tbl:bug_persistence}
+    \input{bug_persistence.tex}
+  \end{table}
+\end{landscape}
+
 \subsubsection{The Relation of Defects with the size of a {\sc jar}}

### 2013-04-05 analysis/repo-statistics/bug_persistence_calc.py

@@ -1,24 +1,34 @@
-# Extracts the bug counters data from the JSON representation
-# and outputs them in CSV format so that it can be read by R.
+# Calculates the bug persistence statistics
 
 import json
 import numpy as np
 import matplotlib.pyplot as plt
 import scipy.stats as st
 import collections
-import itertools
 
-bug_types_closed = {
-        'SECURITY': [],
-        'MALICIOUS_CODE': [],
-        'STYLE': [],
-        'CORRECTNESS': [],
-        'BAD_PRACTICE': [],
-        'MT_CORRECTNESS': [],
-        'I18N': [],
-        'PERFORMANCE': [],
-        'EXPERIMENTAL': []
-        }
+bug_types_closed = collections.OrderedDict({
+    'SECURITY_HIGH': [],
+    'SECURITY_LOW': [],
+    'STYLE': [],
+    'CORRECTNESS': [],
+    'BAD_PRACTICE': [],
+    'MT_CORRECTNESS': [],
+    'I18N': [],
+    'PERFORMANCE': [],
+    'EXPERIMENTAL': []
+})
+
+bug_labels = [
+    'Security High',
+    'Security Low',
+    'Style',
+    'Correctness',
+    'Bad Practice',
+    'MT Correctness',
+    'i18n',
+    'Performance',
+    'Experimental'
+]
 
 projects_closed = set()
 
@@ -42,6 +52,8 @@ with open("data/bug_persistence.json", "r") as json_file:
         for bug in bugs_opened.keys():
             if bug not in bugs:
                 bug_type = bug.partition('||')[0]
+                if bug_type == 'MALICIOUS_CODE':
+                    bug_type = 'SECURITY_LOW'
                 diff = version_order - bugs_opened[bug]
                 bug_types_closed[bug_type].append(diff)
                 if diff < 1:
@@ -49,21 +61,78 @@ with open("data/bug_persistence.json", "r") as json_file:
                            bugs_opened[bug])
                 del bugs_opened[bug]
         for bug in bugs:
+            if bug == 'MALICIOUS_CODE':
+                bug = 'SECURITY_LOW'
             if bug not in bugs_opened:
                 bugs_opened[bug] = version_order
 
-bug_combinations = itertools.combinations(bug_types_closed.keys(), 2)
-
-bug_type_arrays = {}
-bug_type_means = {}
-bug_type_desc = {}
+bug_type_arrays = []
+bug_type_desc = []
 
[…]

### 2013-04-05 docs/evol.tex
Improved description.

@@
 indicator the number of versions a bug remains open in a project. We
-grouped the persistence numbers by bug categories and then performed
-both descriptive statistics and a Mann-Whitney U test among all bug
-category pairs. The results are presented in
-Table~\ref{tbl:bug_persistence}. Cells in brackets show pairs where no
-statistically significant difference was found.
+grouped the persistence numbers by bug categories and then performed a
+Mann-Whitney $U$ test among all bug category pairs. The results are
+presented in Table~\ref{tbl:bug_persistence}. Cells in brackets show
+pairs where no statistically significant difference was found.
 
@@
   \begin{table}
-    \centering
     \caption{Bug Persistence Comparison}
@@
     \input{bug_persistence.tex}
+    \small The matrix presents pairwise Mann-Whitney $U$ test results
+    between the different bug categories. Each cell contains the test
+    result (the value of $U$), the $p$-value, the average for each
+    category and the sample size for each category. Cells in brackets show
+    pairs where no statistically significant difference was found.
   \end{table}

### 2013-04-05 analysis/repo-statistics/bug_persistence_calc.py

@@ -122,11 +122,11 @@ with open("bug_persistence.tex", "w") as bug_persistence_tex:
                 size_i_str = str(results[4])
                 size_j_str = str(results[5])
                 cell = '{}, {}, {}, {}, {}, {}'.format(z_stat_str,
-                                                         p_val_str,
-                                                         mean_i_str,
-                                                         mean_j_str,
-                                                         size_i_str,
-                                                         size_j_str)
+                                                       p_val_str,
+                                                       mean_i_str,
+                                                       mean_j_str,
+                                                       size_i_str,
+                                                       size_j_str)
                 if not significant:
                     cell = '{{\it ({})}}'.format(cell)
                 row.append(cell)

### 2013-04-05 docs/evol.tex
minor fixes - added one bibtex entry

@@
 the category of security bugs has two distinct features: it is critical~\cite{SZ12}
-and it costs~\cite{BCL08}. Specifically, a software bug can
+and it costs~\cite{BCL08}\cite{R06}. Specifically, a software bug can
 lead to a malfunction of a software artifact that runs under specific
@@
 
-We explored te relation between defects with the size of a project version,
+We explored the relation between defects with the size of a project version,
 measured by the size of its {\sc jar} file by carrying out correlation tests

### 2013-04-05 docs/evol.tex
minor fixes and adoption of Spearman correlation

--- 2013-04-05 docs/evol.tex
@@
 lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
-Figure~\ref{fig:corrplot}. We found significant correlations between
-all pairs apart from two pairs involving the {\it Security High}
-category. In general, the {\it Security High} category showed the
-weakest correlations with the other categories. Our results show that
-in general bugs do flock together. We do not find projects with only a
-certain kind of bug; bugs come upon projects in swarms of different
-kinds. Bugs of the {\it Security High} category, though, are
-different: they are either not associated with other bugs, or only
-weakly so. Perhaps it takes a special kind of blunder to make it a
-security hazard.
+Figure~\ref{fig:corrplot}. We found significant, but not always
+strong, correlations between all pairs. In general, the {\it Security
+  High} category showed the weakest correlations with the other
+categories. Our results show that in general bugs do flock together.
+We do not find projects with only a certain kind of bug; bugs come
+upon projects in swarms of different kinds. Bugs of the {\it Security
+  High} category, though, are different: they are either not
+associated with other bugs, or only weakly so. Perhaps it takes a
+special kind of blunder to make it a security hazard.
 
@@
     \input{corrmatrix.tex}
+    \\
     \small The matrix presents pairwise correlations between the
-        following bug categories in order: Security High, Security
-        Low, Style, Bad Practice, Correctness, {\sc mt} Correctness,
-        Performance, i18n, Experimental.
+        different bug categories.
 \end{table}

### 2013-04-05 analysis/repo-statistics/bug_correlation_calc.py

@@ -62,7 +62,7 @@ for i in xrange(num_bug_types):
         icolumn = bug_types[i]
         jcolumn = bug_types[j]
         data_pair = data[[icolumn, jcolumn]].dropna()
-        (corr, pvalue) = st.pearsonr(data_pair[icolumn], data_pair[jcolumn])
+        (corr, pvalue) = st.spearmanr(data_pair[icolumn], data_pair[jcolumn])
         print "{} ({}) {} ({}) {} {}".format(icolumn, data[icolumn].count(),
                                              jcolumn, data[jcolumn].count(),
                                              corr, pvalue)
@@ -72,14 +72,15 @@ for i in xrange(num_bug_types):
 
 with open("corrmatrix.tex", "w") as corrmatrix_tex:
     start = r"""
-\begin{tabular}{ccccccccc}
-\hline \\
+\begin{tabular}{lccccccccc}
+\hline
 """
     corrmatrix_tex.write(start)
-    for row in corrmatrix:
-        table_row = ' & '.join(map('{:.2f}'.format, row)) +  r'\\' + '\n'
+    for i, row in enumerate(corrmatrix):
+        table_row = labels[i] + ' & '
+        table_row += ' & '.join(map('{:.2f}'.format, row)) +  r'\\' + '\n'
         corrmatrix_tex.write(table_row)
-    end = r"""\hline \\
+    end = r"""\hline
 \end{tabular}
 """
     corrmatrix_tex.write(end)

### 2013-04-05 analysis/repo-statistics/project_bugs_counts.py
fix documentation

@@ -1,3 +1,6 @@
+# Extracts the bug counters data from the JSON representation
+# and outputs them in CSV format so that it can be read by R.
+
 import json
 import sys
 import numpy as np

### 2013-04-05 docs/evol.tex
correct OrderedDict init and version history

@@
 
+The relation between bugs and time can be traced from the number of
+bugs per category in each project version. We can then calculate the
+correlations between the defects count and the ordinal version number
+across all projects to see if bigger versions relate to higher or
+lower defect counts. The results are shown in
+Table~\ref{tbl:bugsperversion}. Although the tendency is for
+defect counts to increase, this tendency is extremely slight.
+\begin{table}
+    \centering
+    \caption{Correlations between Version and Defects Count}
+    \label{tbl:bugsperversion}
+    \input{bugsperversion.tex}
+\end{table}
+
 \subsubsection{Persistence of Security Bugs}

### 2013-04-05 analysis/repo-statistics/bug_persistence_calc.py

@@ -6,17 +6,16 @@ import matplotlib.pyplot as plt
 import scipy.stats as st
 import collections
 
-bug_types_closed = collections.OrderedDict({
-    'SECURITY_HIGH': [],
-    'SECURITY_LOW': [],
-    'STYLE': [],
-    'CORRECTNESS': [],
-    'BAD_PRACTICE': [],
-    'MT_CORRECTNESS': [],
-    'I18N': [],
-    'PERFORMANCE': [],
-    'EXPERIMENTAL': []
-})
+bug_types_closed = collections.OrderedDict()
+bug_types_closed['SECURITY_HIGH'] = []
+bug_types_closed['SECURITY_LOW'] = []
+bug_types_closed['STYLE'] =  []
+bug_types_closed['CORRECTNESS'] = []
+bug_types_closed['BAD_PRACTICE'] = []
+bug_types_closed['MT_CORRECTNESS'] = []
+bug_types_closed['I18N'] =  []
+bug_types_closed['PERFORMANCE'] = []
+bug_types_closed['EXPERIMENTAL'] = []
 
 bug_labels = [
     'Security High',

### 2013-04-05 analysis/repo-statistics/project_bugs_counts.py

@@ -1,5 +1,6 @@
-# Extracts the bug counters data from the JSON representation
-# and outputs them in CSV format so that it can be read by R.
+# Extracts the project counters data from the JSON representation
+# and calculates correlations between version numbers and number
+# of bugs.
 
 import json
 import sys
@@ -7,43 +8,91 @@ import numpy as np
 import matplotlib.pyplot as plt
 import scipy.stats as st
 import math
+import collections
 
-bugs_per_version = {
-    'SECURITY_HIGH': [],
-    'SECURITY_LOW': [],
-    'MALICIOUS_CODE': [],
-    'STYLE': [],
-    'CORRECTNESS': [],
-    'BAD_PRACTICE': [],
-    'MT_CORRECTNESS': [],
-    'I18N': [],
-    'PERFORMANCE': [],
-    'EXPERIMENTAL': []
-    }
+bugs_per_version = collections.OrderedDict()
+bugs_per_version['SECURITY_HIGH'] = []
+bugs_per_version['SECURITY_LOW'] = []
+bugs_per_version['STYLE'] =  []
+bugs_per_version['CORRECTNESS'] = []
+bugs_per_version['BAD_PRACTICE'] = []
+bugs_per_version['MT_CORRECTNESS'] = []
+bugs_per_version['I18N'] =  []
+bugs_per_version['PERFORMANCE'] = []
+bugs_per_version['EXPERIMENTAL'] = []
+
+bugs_per_version_labels = [
+    'Security High',
+    'Security Low',
+    'Style',
+    'Correctness',
+    'Bad Practice',
+    'MT Correctness',
+    'i18n',
+    'Performance',
+    'Experimental'
+]
 
 with open("data/project_counters.json", "r") as json_file:
     json_input = json.load(json_file)
     for project, data in json_input.iteritems():
-        if len(data['versions']) > 100:
-            continue
         for version in data['versions']:
             version_order = version['JarMetadata']['version_order']
             if version_order == 0:
                 continue
             counters = version['Counters']
+            if 'MALICIOUS_CODE' in counters:
+                malicious_code = counters.pop('MALICIOUS_CODE')
+                if 'SECURITY_LOW' in counters:
+                    counters['SECURITY_LOW'] += malicious_code
+                else:
+                    counters['SECURITY_LOW'] = malicious_code
             for counter in bugs_per_version.keys():
-                value = counters.get(counter, 0)
-                if value > 1000:
-                    print project, version_order, counter, value
[…]

### 2013-04-05 analysis/repo-statistics/bug_persistence_calc.py
improved table 6 layout

@@ -93,7 +93,7 @@ for i in range(n):
 
 with open("bug_persistence.tex", "w") as bug_persistence_tex:
     start = r"""
-\begin{tabular}{|l|>{\centering\arraybackslash}m{2.2cm}|>{\centering\arraybackslash}m{2.2cm}|>{\centering\arraybackslash}m{2.2cm}|>{\centering\arraybackslash}m{2.2cm}|>{\centering\arraybackslash}m{2.2cm}|>{\centering\arraybackslash}m{2.2cm}|>{\centering\arraybackslash}m{2.2cm}|>{\centering\arraybackslash}m{2.2cm}|}
+\begin{tabular}{|l|>{\centering\arraybackslash}m{2.5cm}|>{\centering\arraybackslash}m{2.5cm}|>{\centering\arraybackslash}m{2.5cm}|>{\centering\arraybackslash}m{2.5cm}|>{\centering\arraybackslash}m{2.5cm}|>{\centering\arraybackslash}m{2.5cm}|>{\centering\arraybackslash}m{2.5cm}|>{\centering\arraybackslash}m{2.5cm}|}
 \hline 
 """
     bug_persistence_tex.write(start)
@@ -105,33 +105,43 @@ with open("bug_persistence.tex", "w") as bug_persistence_tex:
                     row.append('')
             else:
                 results = results_matrix[i][j]
-                z_stat_str = '{:.2f}'.format(results[0])
+                z_stat_str = '${:.2f}$'.format(results[0])
                 significant = True
                 if results[1] < 0.001:
-                    p_val_str = '$\ll 0.05$'
+                    p_val_str = '$p \ll 0.05$'
                 elif results[1] < 0.01:
-                    p_val_str = '$< 0.01$'
+                    p_val_str = '$p < 0.01$'
                 elif results[1] < 0.05:
-                    p_val_str = '$< 0.05$'
+                    p_val_str = '$p < 0.05$'
                 else:
-                    p_val_str = '{:.2f}'.format(results[1])
+                    p_val_str = '$p = {:.2f}$'.format(results[1])
                     significant = False
                 mean_i_str = '{:.2f}'.format(results[2])
                 mean_j_str = '{:.2f}'.format(results[3])
                 size_i_str = str(results[4])
                 size_j_str = str(results[5])
-                cell = '{}, {}, {}, {}, {}, {}'.format(z_stat_str,
-                                                       p_val_str,
-                                                       mean_i_str,
-                                                       mean_j_str,
-                                                       size_i_str,
[…]

### 2013-04-06 docs/evol.tex
improved table 6 layout
additional bug counter and diffs discussion

@@
 
+Although there seems to be zero tendency taken over all versions of
+all projects together, the situation might be different in individual
+projects. We therefore performed Spearman correlations between bug
+counts and version ordinals in all projects we examined. These paint a
+different picture from the above table, shown in
+Figure~\ref{fig:bugsversioncorr}. The spike in point zero is explained
+by the large number of projects for which no correlation could be
+established---note that the scale is logarithmic.
+
+But we can see that there were projects where a correlation could be
+established, either positive or negative. The {\it Security High}
+category is particularly bimodal, but this is explained by the small
+number of correlations that could be established, nine in total. Taken
+together with Table~\ref{tbl:bugsperversion} this suggests that: we
+cannot say that across projects defect counts increase or decrease
+significantly across time. But in individual projects, defect counts
+can have a strong upwards or downwards tendency. There may be no such
+thing as a ``project'' in general, only particular projects with their
+own idiosyncrasies, quality features, and coding practices.
+
+\begin{figure*}
+  \centering
+  \includegraphics[scale=0.4]{bugsversionscorr.pdf}
+  \caption{Histograms of correlations between bug counts and version
+    ordinals per project}
+  \label{fig:bugsversionscorr}
+\end{figure*}
+
 \subsubsection{Persistence of Security Bugs}
@@
   \begin{table}
+    \setlength{\extrarowheight}{0.10cm}
     \caption{Bug Persistence Comparison}
     \label{tbl:bug_persistence}
-    \input{bug_persistence.tex}
-    \small The matrix presents pairwise Mann-Whitney $U$ test results
+    \resizebox{0.95\columnwidth}{!}{
+    \input{bug_persistence.tex}}\\
+    The matrix presents pairwise Mann-Whitney $U$ test results
     between the different bug categories. Each cell contains the test

### 2013-04-06 analysis/repo-statistics/project_counters_diffs.py

@@ -1,38 +1,61 @@
+# Calculate various statistics on the diffs between bug type counts
+
 import json
 import sys
 import numpy as np
 import matplotlib.pyplot as plt
 import scipy.stats as st
 import math
-from collections import defaultdict
+from collections import defaultdict, OrderedDict
+import itertools
 
-bug_types_diffs = {
-    'SECURITY_HIGH': [],
-    'SECURITY_LOW': [],
-    'MALICIOUS_CODE': [],
-    'STYLE': [],
-    'CORRECTNESS': [],
-    'BAD_PRACTICE': [],
-    'MT_CORRECTNESS': [],
-    'I18N': [],
-    'PERFORMANCE': [],
-    'EXPERIMENTAL': []
-    }
+bug_types = (
+    'SECURITY_HIGH',
+    'SECURITY_LOW',
+    'STYLE',
+    'CORRECTNESS',
+    'BAD_PRACTICE',
+    'MT_CORRECTNESS',
+    'I18N',
+    'PERFORMANCE',
+    'EXPERIMENTAL',
+)
 
+# the bug_types_diffs dict contains, for each bug type, a list of the
+# diffs for that bug type, for all projects
+bug_types_diffs = OrderedDict()
+for bug_type in bug_types:
+    bug_types_diffs[bug_type] = []
+
+bug_labels = {
+    'SECURITY_HIGH': 'Security High',
+    'SECURITY_LOW': 'Security Low',
+    'STYLE': 'Style',
+    'CORRECTNESS': 'Correctness',
+    'BAD_PRACTICE': 'Bad Practice',
+    'MT_CORRECTNESS': 'MT Correctness',
+    'I18N': 'i18n',
+    'PERFORMANCE': 'Performance',
+    'EXPERIMENTAL': 'Experimental'
+}
+
+# diffs is a dict with the projects as keys. The value for each key
+# is itself a dict with the various bug types as keys and a list of
+# their diffs as values.
 diffs = {}
+
 counts = {}
 
 counts_corrs = {}
 
+# get defect counts
 with open("data/project_counters.json", "r") as json_file:
     json_input = json.load(json_file)
     for project, data in json_input.iteritems():
         counts[project] = []
-        diffs[project] = defaultdict(list)
         bad_project = False
         for version in data['versions']:
             if bad_project == True:
-                diffs[project] = {}
                 break
             version_order = version['JarMetadata']['version_order']
             if version_order == 0:
[…]

### 2013-04-06 analysis/repo-statistics/project_counters_diffs.py
improved figure

@@ -154,7 +154,12 @@ for bug_type, bug_type_corrs in counts_corrs.iteritems():
     cc_arr = np.array(bug_type_corrs)
     ax = plt.subplot(num_rows, num_cols, num_plot)
     plt.hist(cc_arr, 30, log=True)
-    plt.title(bug_labels[bug_type])
+    total = len(bug_type_corrs)
+    zeros = total - len(np.nonzero(bug_type_corrs)[0])
+    title = "{} ({}, no correlation: {})".format(bug_labels[bug_type],
+                                                 total,
+                                                 zeros)
+    plt.title(title)
     num_plot += 1
 
 plt.tight_layout()

### 2013-04-06 docs/evol.tex
moved pfs to build succesfully
improved figure

@@
 different picture from the above table, shown in
-Figure~\ref{fig:bugsversioncorr}. The spike in point zero is explained
+Figure~\ref{fig:bugsversionscorr}. The spike in point zero is explained
 by the large number of projects for which no correlation could be
@@
   \centering
-  \includegraphics[scale=0.4]{bugsversionscorr.pdf}
+  \includegraphics[scale=0.4]{bugsversionscorr}
   \caption{Histograms of correlations between bug counts and version
-    ordinals per project}
+    ordinals per project. In brackets the total population size and
+    the number of no correlation instances.}
   \label{fig:bugsversionscorr}

### 2013-04-06 docs/evol.tex
improved writing

@@
 different picture from the above table, shown in
-Figure~\ref{fig:bugsversionscorr}. The spike in point zero is explained
-by the large number of projects for which no correlation could be
-established---note that the scale is logarithmic.
-
-But we can see that there were projects where a correlation could be
+Figure~\ref{fig:bugsversionscorr}. The spike in point zero is
+explained by the large number of projects for which no correlation
+could be established---note that the scale is logarithmic. Still, we
+can see that there were projects where a correlation could be
 established, either positive or negative. The {\it Security High}
@@
 number of correlations that could be established, nine in total. Taken
-together with Table~\ref{tbl:bugsperversion} this suggests that: we
-cannot say that across projects defect counts increase or decrease
-significantly across time. But in individual projects, defect counts
-can have a strong upwards or downwards tendency. There may be no such
-thing as a ``project'' in general, only particular projects with their
-own idiosyncrasies, quality features, and coding practices.
+together with Table~\ref{tbl:bugsperversion},
+Figure~\ref{fig:bugsversionscorr} suggests that we cannot say that across
+projects defect counts increase or decrease significantly across time.
+In individual projects, however, defect counts can have a strong
+upwards or downwards tendency. There may be no such thing as a
+``project'' in general, only particular projects with their own
+idiosyncrasies, quality features, and coding practices.
 

### 2013-04-07 docs/evol.tex
started the discussion section

@@
 
-\author{Dimitris Mitropoulos \and Vassilios Karakoidas \and Georgios Gousios \and Panos Louridas \and Diomidis Spinellis }
+\author{Dimitris Mitropoulos \and Vassilios Karakoidas \and Panos Louridas \and Georgios Gousios \and Diomidis Spinellis }
 \institute{ Department of Management Science and Technology\\
@@
 A security bug is a programming error that introduces a potentially
-exploitable weakness into a computer system~\cite{SSL12}\cite{TJBD11}. This weakness could lead to a
+exploitable weakness into a computer system~\cite{SSL12}\cite{TJBD11}\cite{M06}. This weakness could lead to a
 security breach with unfortunate consequences in different layers, like databases,
@@
 perspective. Its structure, gave us the opportunity to see if a project version that is a dependency to
-a large number of others contains a high rate of security bugs.
-In this case we can strengthen the relationship between Linus' Law and
-software security as Meneely et al. have already indicated~\cite{MW10}.
+a large number of others contains a low rate of security bugs~\cite{MW10}.
+%In this case we can strengthen the relationship between Linus' Law and
+%software security as Meneely et al. have already indicated~\cite{MW10}.
 
@@
 categories) are the most popular in the repository ($\geq 22\%$).
-This could be an indication that programmers write code that implements the
-required functionality without considering its many security aspects.
 % An interesting observation is that 4,908 projects did not
@@
 % repository, but the {\sc jar} file did not.
-From the 56,5680 vertices, 191,433
-belonged to the first case while 16,4234 belonged to the second.
+From the 565,680 vertices, 191,433
+belonged to the first case while 164,234 belonged to the second.
 The graph contained 80,354 nodes. Obviously, the number does not correspond to
@@
 
+By examining Maven as a whole we observed that security bugs and the
+bugs coming from the {\it Bad Practice} category are the most popular types of
+bugs in the ecosystem. This could be a strong indication that programmers write code
+that implements the required functionality without considering its many
+security aspects; an issue that has already been reported in
+literature~\cite{SH09}. In addition, contrary to the Linus' Law, from the top fifty versions
+(based on their PageRank), twenty five of them were the latest versions at the
+time and at the same time contained security bugs.
+This also highlights the {\it domino effect}~\cite{TH04}. No matter how well a programmer
+secures a software component it won't matter if he or she is using vulnerable
+code fragments from another library. Finally, 5,355 versions ($\approx 4,64\% $), contain at
+least one severe security bug. Given the fact that other projects include these
+versions as their dependencies, they are automatically rendered vulnerable if
+they use the code fragments that include the defects.
+
 \section{Related Work}

### 2013-04-07 docs/evol.tex
more on the discussion

@@
 	\item The analysis of how security bugs evolve over time. To achieve
-this, we inspect every project per version. Our hypothesis is that security
-bugs must decrease as a project evolves since they are critical and developers
+this, we inspect every project per version. We expect that security
+bugs should decrease as a project evolves since they are critical and developers
 should eliminate them.
@@
 security bugs (the sum of the {\it Security} and {\it Malicious Code}
-categories) are the most popular in the repository ($\geq 22\%$).
+categories) are the most popular in the repository ($\geq 22\%$ each).
 % An interesting observation is that 4,908 projects did not
@@
 bugs, another program should be written either to incorporate references to
-mutable objects, access non-final fields and others. In addition, as
-bug descriptions indicate,\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
-if an application has bugs like these, it might have more vulnerabilities that FindBugs doesn't
-report. Table~\ref{tbl:sev} presents the number of {\sc jar}s where at least one of these
-bugs exists. In the following section we provide results separately for this
-subcategory which we call {\it Security High}. The remaining bugs of the {\it Security} category
-are grouped together with the bugs of the {\it Malicious Code} category in another subcategory that
-we call {\it Security Low}.
+mutable objects, access non-final fields and others. Table~\ref{tbl:sev} presents the number
+of {\sc jar}s where at least one of these bugs exists. In the following section
+we provide results separately for this subcategory which we call {\it Security High}.
+The remaining bugs of the {\it Security} category
+are grouped together with the bugs of the {\it Malicious Code} category
+in another subcategory that we call {\it Security Low}.
 
@@
 secures a software component it won't matter if he or she is using vulnerable
-code fragments from another library. Finally, 5,355 versions ($\approx 4,64\% $), contain at
+code fragments from another library. Finally, 5,355 versions ($\approx 4,64\% $), contained at
 least one severe security bug. Given the fact that other projects include these
 versions as their dependencies, they are automatically rendered vulnerable if
-they use the code fragments that include the defects.
+they use the code fragments that include the defects. Finally, as
+bug descriptions indicate,\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
+if an application has bugs coming from the {\it Security High} category,
+it might have more vulnerabilities that FindBugs doesn't report.
 

### 2013-04-07 docs/evol.tex
Add discussion on diffs

--- 2013-04-06 docs/evol.tex
@@
 
+Another take on this theme is shown in Figure~\ref{fig:bugddifs},
+which presents an histogram of the changes of different bug counts in
+project versions. In most cases, a bug count does not change between
+versions; but when it does change, it may change upwards or downwards.
+Note also the spectacular changes of introducing or removing thousands
+of defects; this may be the result of doing and undoing a pervasive
+code change that falls foul of some bug identification rule.
+
+\begin{figure*}
+  \centering
+  \includegraphics[scale=0.4]{bugdiffs}
+  \caption{Histograms of the time, measure in versions, it takes for a
+    bug to be closed. }
+  \label{fig:bugdiffs}
+\end{figure*}
+
 \subsubsection{Persistence of Security Bugs}

### 2013-04-07 docs/evol.tex
minor fix

@@
 
-Another take on this theme is shown in Figure~\ref{fig:bugddifs},
+Another take on this theme is shown in Figure~\ref{fig:bugdiffs},
 which presents an histogram of the changes of different bug counts in

### 2013-04-07 docs/evol.tex
removed discussion section. The paper is getting to big.

@@
 categories) are the most popular in the repository ($\geq 22\%$ each).
+This could be a strong indication that programmers write code
+that implements the required functionality without considering its many
+security aspects; an issue that has already been reported in
+literature~\cite{SH09}.
 % An interesting observation is that 4,908 projects did not
@@
 validation and can lead to damaging attacks like {\sc sql} injection~\cite{RL12} and
-Cross-Site Scripting~\cite{WS08}. Note that to exploit such vulnerabilities, a malicious user does
+Cross-Site Scripting~\cite{WS08}.
+Note that to exploit such vulnerabilities, a malicious user does
 not have to know anything about the applications internals. For all the other
 bugs, another program should be written either to incorporate references to
-mutable objects, access non-final fields and others. Table~\ref{tbl:sev} presents the number
-of {\sc jar}s where at least one of these bugs exists. In the following section
+mutable objects, access non-final fields and others.
+Also, as bug descriptions indicate,\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
+if an application has bugs coming from the {\it Security High} category,
+it might have more vulnerabilities that FindBugs doesn't report.
+Table~\ref{tbl:sev} presents the number
+of {\sc jar}s where at least one of these bugs exists. In essence, 5,355 versions
+($\approx 4,64\% $), contained at
+least one severe security bug. Given the fact that other projects include these
+versions as their dependencies, they are automatically rendered vulnerable if
+they use the code fragments that include the defects.
+In the following section
 we provide results separately for this subcategory which we call {\it Security High}.
@@
 examined the security bugs of the fifty most popular nodes based on their PageRank.
-Thirty three of them contained bugs coming from the {\it Security Low} subcategory,
-while two of them contained severe bugs. Twenty five of them were latest
-versions at the time.
-% what can we say about this?
+Contrary to the Linus' Law, thirty three of them contained bugs coming from the
+{\it Security Low} subcategory, while two of them contained severe bugs.
+Twenty five of them were latest versions at the time. This also highlights
+the {\it domino effect}~\cite{TH04}. No matter how well a programmer secures a software component
+it won't matter if he or she is using vulnerable code fragments from another library.
 
@@
 
-\section{Discussion}
-\label{sec:dis}
-% also mention:
-% - the fact that we don't have the same number of versions in every project.
-% - tell about the graph and Linus.
-
-By examining Maven as a whole we observed that security bugs and the
-bugs coming from the {\it Bad Practice} category are the most popular types of
-bugs in the ecosystem. This could be a strong indication that programmers write code
-that implements the required functionality without considering its many
-security aspects; an issue that has already been reported in
-literature~\cite{SH09}. In addition, contrary to the Linus' Law, from the top fifty versions
-(based on their PageRank), twenty five of them were the latest versions at the
-time and at the same time contained security bugs.
-This also highlights the {\it domino effect}~\cite{TH04}. No matter how well a programmer
-secures a software component it won't matter if he or she is using vulnerable
-code fragments from another library. Finally, 5,355 versions ($\approx 4,64\% $), contained at
-least one severe security bug. Given the fact that other projects include these
-versions as their dependencies, they are automatically rendered vulnerable if
-they use the code fragments that include the defects. Finally, as
-bug descriptions indicate,\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
-if an application has bugs coming from the {\it Security High} category,
-it might have more vulnerabilities that FindBugs doesn't report.
-
 \section{Related Work}

### 2013-04-07 docs/evol.tex
started conclusions section

@@
 the other categories, even {\it Security Low} that nearly tops the
-list.
+list. In essense, a severe bug is introduced only when code that deals with
+untrusted input is introduced in a application.
 
@@
 
+In this work we analyzed a large software repository to examine the behavior
+of security bugs. Specifically, we analyzed more than 260GB of interdependent
+projcet versions to see how security bugs evolve over time, their
+persistence, and their relation with other bug categories and the size in
+terms of bytecode.
+
 Our work could (?) aid bug-prediction models in the same way as~\cite{BN11}.

### 2013-04-07 docs/evol.tex
more on the conclusions

@@
 the other categories, even {\it Security Low} that nearly tops the
-list. In essense, a severe bug is introduced only when code that deals with
-untrusted input is introduced in a application.
+list.
 
@@
 persistence, and their relation with other bug categories and the size in
-terms of bytecode.
+terms of bytecode. We have to mentioned that the versions examined were
+actually releases of these projets. In essence, these {\sc jar}s were the ones
+that were or still are out there in the wild, being used either as
+applications, or dependencies of others.
 
-Our work could (?) aid bug-prediction models in the same way as~\cite{BN11}.
+Our primary expectation was that security bugs and especially severe
+ones, should be corrected as projects evolve. But our findigs indicate that this is
+not true. Concerning bug persistence, we saw that the behaviour of security
+bugs is similar to the other categories. We have to point out the fact that
+having an average of two to three versions persistence in a sample where 60\%
+of the projects have three versions, is not a positive result especially in the
+case of the {\it Security High} bugs. An interesting observation was that
+the relation between severe security bugs and a project's size the is different
+than the other categories. In essense, a severe bug is introduced only when code
+that deals with untrusted input is added in a application. Furthermore, the
+pairwise correlations between all categories indicated that severe bugs are
+coming from a special kind of carelessness. Finally, it is interesting to see
+that security bugs were one of the top two bug categories existing in such a
+large ecosystem.
 

### 2013-04-07 docs/evol.tex
minor fixes

@@
 security bugs with performance bugs. This was also done by analysing the project's
-Bugzilla. Their research showed that security bugs require more experienced developers
+Bugzilla. Their research presented evidence that security bugs require more experienced developers
 to be fixed. In addition, they suggested that security bug fixes are more complex than the
@@
 
-Our primary expectation was that security bugs and especially severe
+Our primary hypothesis was that security bugs and especially severe
 ones, should be corrected as projects evolve. But our findigs indicate that this is
@@
 case of the {\it Security High} bugs. An interesting observation was that
-the relation between severe security bugs and a project's size the is different
+the relation between severe security bugs and a project's size is different
 than the other categories. In essense, a severe bug is introduced only when code

### 2013-04-07 docs/evol.tex
added future work

@@
 	\item Security bug persistence between versions. We show evidence that
-security bugs are not eliminated between versions.
+security bugs are not eliminated between releases.
 	\item We show evidence of the relation between security bugs and a project
@@
 
-Our experiment involved four entities (see Table~\ref{tbl:exp}):
-a number of {\it workers}, a {\it task queue}
-mechanism,\footnote{\url{http://www.rabbitmq.com/}}
-a {\it data repository},\footnote{\url{http://www.mongodb.org/}}
+Our experiment involved four entities:
+a number of {\it workers} (a custom Python script), a {\it task queue}
+mechanism (Rabbit{\sc mq} - version 3.0.1),\footnote{\url{http://www.rabbitmq.com/}}
+a {\it data repository} (Mongo{\sc db} - version 2.2),\footnote{\url{http://www.mongodb.org/}}
 and the {\it code repository}, which in our case it was
@@
 
-\begin{table}
-\centering
-\begin{threeparttable}
-\caption{Experiment Entities}
-\label{tbl:exp}
-\begin{tabular}{l r r}
-\hline
-Entity & Software Package & Version\\
-\hline
-Worker & Custom Python Script & 2.7\\
-Task Queue & RabbitMQ & 3.0.1 \\
-Data Repository & MongoDB & 2.2 \\
-Code Repository & Maven Central Repository & January 2012 \\
-\hline
-\end{tabular}
-\end{threeparttable}
-\end{table}
+%\begin{table}
+%\centering
+%\begin{threeparttable}
+%\caption{Experiment Entities}
+%\label{tbl:exp}
+%\begin{tabular}{l r r}
+%\hline
+%Entity & Software Package & Version\\
+%\hline
+%Worker & Custom Python Script & 2.7\\
+%Task Queue & RabbitMQ & 3.0.1 \\
+%Data Repository & MongoDB & 2.2 \\
+%Code Repository & Maven Central Repository & January 2012 \\
+%\hline
+%\end{tabular}
+%\end{threeparttable}
+%\end{table}
 
@@
 
-\begin{table}
+\begin{table}[t]
 \centering
@@
 
-\begin{figure*}
+\begin{figure*}[t]
 	\centering
@@
 
-\begin{table*}
+\begin{table*}[t]
 \centering
@@
 defect counts to increase, this tendency is extremely slight.
-\begin{table}
+
+\begin{table}[t]
     \centering
@@
 
-\begin{figure*}
+\begin{figure*}[t]
   \centering
@@
 
-\begin{table}
+\begin{table}[t]
     \centering
@@
 
+Future work on our approach involves the observation of other ecosystems, that
+serve different languages, in the same manner. For instance, Python's PyPY
+(Python Package Index),\footnote{\url{https://pypi.python.org/pypi}}
+Perl's {\sc cpan} (Comprehensive Perl Archive Network),\footnote{\url{http://www.cpan.org/}}
+and Ruby's RubyGems.\footnote{\url{http://rubygems.org/}}
+
+Our data and code are publicly available and can be found under the following
+GitHub address: \url{https://github.com/bkarak/evol_security_publication_2012}.
+
 \section*{Acknowledgements}

### 2013-04-07 docs/evol.tex
minor fixes

@@
 persistence, and their relation with other bug categories and the size in
-terms of bytecode. We have to mentioned that the versions examined were
+terms of bytecode. We have to mention that the versions examined were
 actually releases of these projets. In essence, these {\sc jar}s were the ones
-that were or still are out there in the wild, being used either as
+that were or still are, out there in the wild, being used either as
 applications, or dependencies of others.

### 2013-04-08 docs/evol.tex
minor corrections and spearman's throughout.

@@
 {\it Maven Central Repository}\footnote{\url{http://search.maven.org/}}
-(approximately 265GB of data - see Section~\ref{sec:data}).
+(approximately 265GB of data---see Section~\ref{sec:data}).
 Then we observed the changes that involved the security bugs and their characteristics.
@@
 addition, we wanted to investigate other critical features associated with such
-vulnerabilities like the persistence of a bug. In essence, to check if critical bugs stay
+vulnerabilities like the persistence of a bug; in essence, to check if critical bugs stay
 unresolved for a long time. Also, we wanted to elaborate more on the relation of security
 bugs not only with performance bugs (as Zaman et al.~\cite{ZAH11} have already
-did) but also with other bug categories. In the same manner, we tried to check
-the relation between a version's size and its' security bugs knowing the
+done) but also with other bug categories. In the same manner, we tried to check
+the relation between version size and security bugs, knowing the
 that research has been contradictory on the the
@@
 Finally, we examined the Maven ecosystem as a whole from a security
-perspective. Its structure, gave us the opportunity to see if a project version that is a dependency to
+perspective. Its structure gave us the opportunity to see if a project version that is a dependency to
 a large number of others contains a low rate of security bugs~\cite{MW10}.
@@
 The statistical measurements presented in Table~\ref{tbl:repository}
-indicate that we have 17,505 projects and the data set's median
-is 3, which means that almost 50\% (8,753 projects) of the project
-population has 1 to 3 versions.
-Note that the Maven repository has many projects with a
-few number of versions. For instance, there are numerous projects with a
-number of versions that is less than ten.
-There are a few projects containing ten
-versions and only a few with hundreds of versions. The maximum number of
-versions for a project is 338. The 3$^{rd}$ quartile measurement
-also indicated that 75\% (13,129) of the projects have a maximum of 8 versions.
+indicate that we have 17,505 projects and the data set's median is 3,
+which means that almost 50\% (8,753 projects) of the project
+population have 1 to 3 versions. In general, most projects have a few
+number of versions, there are some projects with ten versions and
+only a few with hundreds of versions. The maximum number of versions
+for a project is 338. The 3$^{rd}$ quartile measurement also indicated
+that 75\% (13,129) of the projects have a maximum of 8 versions.
 
@@
 Note that to exploit such vulnerabilities, a malicious user does
-not have to know anything about the applications internals. For all the other
-bugs, another program should be written either to incorporate references to
-mutable objects, access non-final fields and others.
+not have to know anything about the application internals. For all the other
+bugs, another program should be written to incorporate references to
+mutable objects, access non-final fields, etc.
 Also, as bug descriptions indicate,\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
@@
 nodes of the graph represented the versions and the vertices their dependencies.
-We have to mention here that the graph was not representative. For instance, if
+The graph was not entirely accurate. For instance, if
 a dependency was pointing only to a project (and not to a specific version), we chose to
@@
 examined the security bugs of the fifty most popular nodes based on their PageRank.
-Contrary to the Linus' Law, thirty three of them contained bugs coming from the
+Contrary to Linus' Law, thirty three of them contained bugs coming from the
 {\it Security Low} subcategory, while two of them contained severe bugs.
@@
 bugs per category in each project version. We can then calculate the
-correlations between the defects count and the ordinal version number
-across all projects to see if bigger versions relate to higher or
-lower defect counts. The results are shown in
-Table~\ref{tbl:bugsperversion}. Although the tendency is for
-defect counts to increase, this tendency is extremely slight.
+Spearman correlations between the defects count and the ordinal
+version number across all projects to see if bigger versions relate to
+higher or lower defect counts. The results are shown in
+Table~\ref{tbl:bugsperversion}. Although the tendency is for defect
+counts to increase, this tendency is extremely slight.
 
@@
 
-Although there seems to be zero tendency taken over all versions of
-all projects together, the situation might be different in individual
-projects. We therefore performed Spearman correlations between bug
-counts and version ordinals in all projects we examined. These paint a
-different picture from the above table, shown in
-Figure~\ref{fig:bugsversionscorr}. The spike in point zero is
-explained by the large number of projects for which no correlation
-could be established---note that the scale is logarithmic. Still, we
-can see that there were projects where a correlation could be
-established, either positive or negative. The {\it Security High}
-category is particularly bimodal, but this is explained by the small
-number of correlations that could be established, nine in total. Taken
-together with Table~\ref{tbl:bugsperversion},
-Figure~\ref{fig:bugsversionscorr} suggests that we cannot say that across
-projects defect counts increase or decrease significantly across time.
-In individual projects, however, defect counts can have a strong
-upwards or downwards tendency. There may be no such thing as a
+The zero tendency applies to all versions of all projects together. 
+The situation might be different in individual projects. We therefore
+performed Spearman correlations between bug counts and version
+ordinals in all projects we examined. These paint a different picture
+from the above table, shown in Figure~\ref{fig:bugsversionscorr}. The
+spike in point zero is explained by the large number of projects for
+which no correlation could be established---note that the scale is
+logarithmic. Still, we can see that there were projects where a
+correlation could be established, either positive or negative. The
+{\it Security High} category is particularly bimodal, but this is
+explained by the small number of correlations that could be
+established, nine in total.
+
+Overall, Table~\ref{tbl:bugsperversion} and
+Figure~\ref{fig:bugsversionscorr} suggest that we cannot say that
+across projects defect counts increase or decrease significantly
+across time. In individual projects, however, defect counts can have a
+strong upwards or downwards tendency. There may be no such thing as a
 ``project'' in general, only particular projects with their own
@@
 
-We explored the relation between defects with the size of a project version,
-measured by the size of its {\sc jar} file by carrying out correlation tests
-between the size and the defect counts for each project and its
-version. The results, all statistically significant ($p \ll
-0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it Security
-  High} category stands out by having a remarkably lower effect than
-the other categories, even {\it Security Low} that nearly tops the
-list.
+We explored the relation between defects with the size of a project
+version, measured by the size of its {\sc jar} file by carrying out
+correlation tests between the size and the defect counts for each
+project and version. The results, all statistically significant ($p
+\ll 0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it
+  Security High} category stands out by having a remarkably lower
+effect than the other categories, even {\it Security Low} that nearly
+tops the list.
 
@@
     \centering
-    \caption{Correlations between jar size and Defects Count}
+    \caption{Correlations between {\sc jar} size and Defects Count}
     \label{tbl:jarsizecorr}

### 2013-04-08 analysis/repo-statistics/project_bugs_counts.py

@@ -65,7 +65,7 @@ with open("bugsperversion.tex", "w") as bugsperversion_tex:
     start = r"""
 \begin{tabular}{lcc}
 \hline \\
-Category & Pearson Correlation & $p$-value \\ \hline 
+Category & Spearman Correlation & $p$-value \\ \hline 
 """
     bugsperversion_tex.write(start)
     for i, row in enumerate(bug_counts_matrix):

### 2013-04-08 docs/evol.tex
merged with Panos comments

@@
 an application, steal data or prevent the application from working at all.
-In this paper, we present how we used the Maven repository to study the
+We used the Maven repository to study the
 characteristics of security bugs individually and in relation to other software
 bugs. In particular, we analyzed every project version of the repository by using a
-popular static analysis tool. Then by taking advantage of the various features of
-the repository (multiple versions for every project, dependencies and others) we studied
+popular static analysis tool. Then by taking advantage of
+the repository's features (multiple versions for every project, dependencies) we studied
 the evolution of security bugs through time, their persistence and their relationship with a) the
-size of the corresponding version and b) other bug categories. Also, based on the
-dependencies of artifacts we constructed the graph of the repository and
-examined the most popular nodes based on their PageRank. 
+size of the corresponding version and b) other bug categories. Our findings
+indicated that security bugs neither increase or decrease as a project evolves.
+In addition, they are not eliminated in a way that is particularly
+different from the other bugs. Also, their relation with the
+size appeared to be different from the other categories. Finally, even if bugs
+seem to flock together, severe security bugs
+seem to be unassociated with other categories.
 \end{abstract}
@@
 In this paper we present how we used a large software ecosystem to analyse
-how evolving software packages are related to the different types of security
-vulnerabilities.
+how different types of security vulnerabilities are related to the evolving software packages.
 
@@
 the category of security bugs has two distinct features: it is critical~\cite{SZ12}
-and it costs~\cite{BCL08}\cite{R06}. Specifically, a software bug can
+and it costs~\cite{BCL08}\c~\cite{TH04}ite{R06}. Specifically, a software bug can
 lead to a malfunction of a software artifact that runs under specific
@@
 \begin{itemize}
-	\item The analysis of how security bugs evolve over time. To achieve
-this, we inspect every project per version. We expect that security
-bugs should decrease as a project evolves since they are critical and developers
-should eliminate them.
-	\item Security bug persistence between versions. We show evidence that
-security bugs are not eliminated between releases.
-	\item We show evidence of the relation between security bugs and a project
+	\item The analysis of how security bugs found through static analysis,
+evolve over time. To achieve this, we inspect every project per version.
+Our hypothesis is that security bugs should decrease as a project evolves since
+they are critical and developers should eliminate them.
+	\item Security bug persistence between versions. We expect that
+security bugs should be eliminated earlier than other bugs.
+	\item The relation between security bugs and a project
+version's size. Our hypothesis is that security bugs are proportional to a project
 version's size.  Here, size is defined in terms of bytecode.
-	\item The correlation of security bugs with other bug categories. We
-show evidence on how such bugs are correlated with bugs that have to do with
+	\item The correlation of security bugs with other bug categories. Our
+hypothesis is that security bugs flock together with bugs that have to do with
 performance, coding practices and others.
@@
 
-Our experiment involved four entities:
+The goal of our experiment was to retrieve all the bugs that FindBugs reports,
+for all the project versions existing on the Maven repository.
+The experiment involved four entities:
 a number of {\it workers} (a custom Python script), a {\it task queue}
@@
 also stored in the data repository. When the task was completed the queue
-was notified and the next task was requested. A schematic representation
-of the data processing architecture can be seen in Figure~\ref{fig:arch}.
-
-This process was executed for all the available {\sc jar}s in the task queue.
-The experiment was executed five times in order to iron out various bugs in
-our scripts and validate the results.
+was notified and the next task was requested. This process was executed for
+all the available {\sc jar}s in the task queue. A schematic representation of
+the data processing architecture can be seen in Figure~\ref{fig:arch}.
 
@@
 Versions (total) & 115,214\\
-Min & 1\\
-Max & 338\\
-Mean & 6.58\\
-Median & 3\\
-Range & 337\\
-1$^{st}$ Quartile & 1\\
-3$^{rd}$ Quartile & 8\\
+Min (versions per project) & 1\\
+Max (versions per project) & 338\\
+Mean (versions per project) & 6.58\\
+Median (versions per project) & 3\\
+Range (over versions) & 337\\
+1$^{st}$ Quartile (over versions) & 1\\
+3$^{rd}$ Quartile (over versions) & 8\\
 \hline
@@
 	\centering
-	\includegraphics[scale=0.6]{version_count.pdf}
+	\includegraphics[scale=0.4]{version_count.pdf}
 	\caption{Distribution of
@@
 
+\subsection{Threats to Validity}
+\label{sec:threats}
+
+A threat to the internal validity of our experiment could be the false alarms of the
+FindBugs tool. The false positives and negatives of static analysis tools and
+how they can be reduced, is an issue that has already been discussed in literature (see
+Section~\ref{sec:rel}). Furthermore, consider a false positive alarm where an
+security bug is reported, but it is invalidated based on the context of the
+application (an {\sc sql} injection vulnerability~\cite{RL12} in an application that
+requires no external input).
+
+We also have to mention that our analysis is done on projects written in the
+Java programming language. Hence, a threat to the external validity of our work
+is the fact that our results may not be the same in another programming
+environment.
+
 \section{Results and Analysis}
@@
 \label{tbl:bug-cat}
-\begin{tabular}{l p{15em}}
+\begin{tabular}{l p{23em}}
 \hline
@@
 coding practice. \\
-Correctness & Involves coding mistakes resulting in code
+Correctness & Involves coding mistin a way that is particularly different from the other bugsakes resulting in code
 that was probably not what the developer intended. \\
@@
 \centering
-\caption{Number of Versions that Contain at Least One Severe Security Bug}
+\caption{Number of Project Releases that Contain at Least One Severe Security Bug}
 \label{tbl:sev}
 \leavevmode
-	\begin{tabular}{l r}
+	\begin{tabular}{p{25em} r}
 	\hline
-	Bug Description & Number of Versions\\
+	Bug Description & Number of Project Releases\\
  	\hline
@@
 
+Our first results involve the most popular bugs in the Maven repository.
 Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
@@
 
-% dimitro@dds: maybe you want to add something here?
 Another observation involves bugs that we could call {\it
@@
 Table~\ref{tbl:sev} presents the number
-of {\sc jar}s where at least one of these bugs exists. In essence, 5,355 versions
+of releases where at least one of these bugs exists. In essence, 5,355 releases
 ($\approx 4,64\% $), contained at
@@
 	\centering
-	\includegraphics[scale=0.6]{bug_percent}
+	\includegraphics[scale=0.4]{bug_percent}
 	\caption{Bug Percentage in Maven Repository}
@@
 
-As we mentioned earlier, during the experiment we managed to retrieve the
+To examine {\it Linus' Law} in relation to the rate of the
+security bugs~\cite{MW10}, and highlight the
+{\it domino effect}~\cite{TH04} we did the
+following: during the experiment we managed to retrieve the
 dependencies of every version. Based on this information we created a graph
@@
 From the 565,680 vertices, 191,433
-belonged to the first case while 164,234 belonged to the second.
+did not point to a specific version while 164,234 were pointing to missing ones.
 The graph contained 80,354 nodes. Obviously, the number does not correspond to
@@
 Twenty five of them were latest versions at the time. This also highlights
-the {\it domino effect}~\cite{TH04}. No matter how well a programmer secures a software component
-it won't matter if he or she is using vulnerable code fragments from another library.
+the domino effect. No matter how well a programmer secures a software component
+it won't matter if he or she is using vulnerable code fragments coming
+from another library.
 
@@
 
-\subsubsection{How Security Bugs Evolve Over Time}
+\subsubsection{How Security Bugs E(over versions)volve Over Time}
 
@@
 Overall, Table~\ref{tbl:bugsperversion} and
-Figure~\ref{fig:bugsversionscorr} suggest that we cannot say that
+Figure~\ref{fig:bugsversionscorr} suggest that \textbf{we cannot say that
 across projects defect counts increase or decrease significantly
-across time. In individual projects, however, defect counts can have a
+across time}. In individual projects, however, defect counts can have a
 strong upwards or downwards tendency. There may be no such thing as a
@@
 Another take on this theme is shown in Figure~\ref{fig:bugdiffs},
-which presents an histogram of the changes of different bug counts in
+which presents a histogram of the changes of different bug counts in
 project versions. In most cases, a bug count does not change between
@@
 grouped the persistence numbers by bug categories and then performed a
-Mann-Whitney $U$ test among all bug category pairs. The results are
+Mann-Whitney $U$~\cite{HM98} test among all bug category pairs. The results are
 presented in Table~\ref{tbl:bug_persistence}. Cells in brackets show
@@
 bug categories remained opened was statistically different in many
-cases, the difference is not spectacular. In all cases a bug persists
-on average between two and three versions, with the difference being
+cases, the difference is not spectacular. \textbf{In all cases a bug persists
+on average between two and three versions}, with the difference being
 in the decimal digits.
@@
 project and version. The results, all statistically significant ($p
-\ll 0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it
+\ll 0.05$) can be seen in Table~\ref{tbl:jarsizecorr}.  \textbf{The {\it
   Security High} category stands out by having a remarkably lower
-effect than the other categories, even {\it Security Low} that nearly
+effect than the other categories}, even {\it Security Low} that nearly
 tops the list.
@@
   High} category showed the weakest correlations with the other
-categories. Our results show that in general bugs do flock together.
+categories. Our results show that in general \textbf{bugs do flock together}.
 We do not find projects with only a certain kind of bug; bugs come
@@
 that highlight the relationship between software bugs and evolution and try to
-extract useful conclusions. The key idea behind this concept is
+extract useful conclusions. The key idea behind this is
 similar to ours: the combination of information like bug descriptions,
@@
 
-Using {\it micro patterns} is a method proposed by Kim et al.~\cite{KPW06}
-to detect bug-prone patterns among source code. Micro patterns describe programming
-idioms like inheritance, data management, immutability and others. The approach involved
-the examination of all revisions of three open-source projects to extract bug
+{\it Micro patterns}, proposed by Kim et al.~\cite{KPW06}
+detect bug-prone patterns among source code. Micro patterns describe programming
+idioms like inheritance, data management, immutability and others. The approach
+involves the examination of all revisions of three open-source projects to extract bug
 introduction rates for each pattern. Gil et al.~\cite{GM05} analysed the
@@
 
-Contrary to the above, our work focuses on the subset of security bugs.
+Completing the above approaches, our work focuses on the subset of security bugs.
 Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
@@
 persistence, and their relation with other bug categories and the size in
-terms of bytecode. We have to mention that the versions examined were
-actually releases of these projets. In essence, these {\sc jar}s were the ones
-that were or still are, out there in the wild, being used either as
-applications, or dependencies of others.
+terms of bytecode.
 
 Our primary hypothesis was that security bugs and especially severe
-ones, should be corrected as projects evolve. But our findigs indicate that this is
-not true. Concerning bug persistence, we saw that the behaviour of security
-bugs is similar to the other categories. We have to point out the fact that
-having an average of two to three versions persistence in a sample where 60\%
+ones, should be corrected as projects evolve. However, our findigs indicate that this is
+not true. Contrary to our second research hypothesis, we showed that security
+bugs are not eliminated in a way that is particularly different from the other bugs.
+Also, having an average of two to three versions persistence in a sample where 60\%
 of the projects have three versions, is not a positive result especially in the
-case of the {\it Security High} bugs. An interesting observation was that
-the relation between severe security bugs and a project's size is different
-than the other categories. In essense, a severe bug is introduced only when code
-that deals with untrusted input is added in a application. Furthermore, the
-pairwise correlations between all categories indicated that severe bugs are
-coming from a special kind of carelessness. Finally, it is interesting to see
-that security bugs were one of the top two bug categories existing in such a
-large ecosystem.
+case of the {\it Security High} bugs. Concerning the relation between severe security bugs and a project's size
+we showed evidence that they are not proportionally related. Furthermore, the
+pairwise correlations between all categories indicated that even though all the other
+categories are related, severe bugs do not flock together with the other bugs.
+Also, it is interesting to see that security bugs were one of the top two
+bug categories existing in a large ecosystem. Finally, we highlighted the
+domino effect, and showed evidence that indicates that the Linus' Law does not
+apply in the case of the security bugs.
 
-Future work on our approach involves the observation of other ecosystems, that
-serve different languages, in the same manner. For instance, Python's PyPY
+Contrary to the approaches that examine all versions
+formed after every change that has been commited to the repository,
+our observations are made from a different perspective.
+The versions examined in this work were actual releases
+of the projets. As a result we do not have an indication of how many changes
+have been made between the releases.
+In essence, these {\sc jar}s were the ones that were or still are,
+out there in the wild, being used either as applications,
+or dependencies of others.
+
+Furthermore, the fact that projects have their own idiosyncrasies concerning
+security bugs, could help us answer questions like: what are the common
+characteristics of the projects where security bugs increase over time?
+
+Future work on our approach could also involve the observation of other ecosystems, that
+serve different languages, in the same manner such as, Python's PyPY
 (Python Package Index),\footnote{\url{https://pypi.python.org/pypi}}

### 2013-04-08 docs/evol.tex
Restructure contributions

@@
 
-A security bug is a programming error that introduces a potentially
-exploitable weakness into a computer system~\cite{SSL12}\cite{TJBD11}\cite{M06}. This weakness could lead to a
-security breach with unfortunate consequences in different layers, like databases,
-native code, applications, libraries and others. Despite the significant
-effort to detect and eliminate such bugs~\cite{SZ12}, little attention has been paid to
-study them in relation to software evolution~\cite{L96}\cite{LRWPT97}\cite{IB06}\cite{RGMA06}.
-In this paper we present how we used a large software ecosystem to analyse
-how different types of security vulnerabilities are related to the evolving software packages.
-
+A security bug is a programming error that introduces a potentially exploitable
+weakness into a computer system~\cite{SSL12}\cite{TJBD11}\cite{M06}. This
+weakness could lead to a security breach with unfortunate consequences in
+different layers, like databases, native code, applications, libraries and
+others. Despite the significant effort to detect and eliminate such
+bugs~\cite{SZ12}, little attention has been paid to study them in relation to
+software evolution~\cite{L96}\cite{LRWPT97}\cite{IB06}\cite{RGMA06}. 
 One of the most common approaches to identify security bugs is
@@
 inspection of the program's source or object code without executing
-it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
+it.
+
+In this
+paper we present how we used a large software ecosystem to analyse how different
+types of security vulnerabilities are related to the evolving software packages.
+For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
 a static analysis tool that examines bytecode to detect software bugs and has already been used in
@@
 
-We chose to focus our study on the security bugs rather than other
-software bugs. This is because compared to other bug categories,
+We chose to focus our study on security bugs rather than other types of
+software defects. This is because compared to other bug categories,
 the category of security bugs has two distinct features: it is critical~\cite{SZ12}
-and it costs~\cite{BCL08}\c~\cite{TH04}ite{R06}. Specifically, a software bug can
+for an organization's infrastructure
+and moreover it can cause significant financial damage to 
+an organization~\cite{TH04}\cite{BCL08}\cite{R06}. 
+Specifically, a software bug can
 lead to a malfunction of a software artifact that runs under specific
@@
 Hence, one of the basic pursuits in every new software release should
-be the mitigation of such bugs.
+be to mitigate such bugs.
 
-The motivation behind our work was to validate if programmers tend to care for
+% @dimitro: say why we did this work, not how we did it
+The motivation behind our work was to validate whether programmers care for
 such high-risk bugs when they release a new version of their software. In
@@
 
-The main contributions of this research are:
+%@dimitro: check the following
+The main contributions of this work are:
 \begin{itemize}
-	\item The analysis of how security bugs found through static analysis,
-evolve over time. To achieve this, we inspect every project per version.
-Our hypothesis is that security bugs should decrease as a project evolves since
-they are critical and developers should eliminate them.
-	\item Security bug persistence between versions. We expect that
-security bugs should be eliminated earlier than other bugs.
-	\item The relation between security bugs and a project
-version's size. Our hypothesis is that security bugs are proportional to a project
-version's size.  Here, size is defined in terms of bytecode.
-	\item The correlation of security bugs with other bug categories. Our
-hypothesis is that security bugs flock together with bugs that have to do with
-performance, coding practices and others.
+	\item We present evidence that defect counts remain relatively stable
+    across project revisions.
+%An analysis of how security bugs found through static analysis,
+%evolve over time.
+%To achieve this, we inspect every project per version.
+%Our hypothesis is that security bugs should decrease as a project evolves since
+%they are critical and developers should eliminate them.
+	\item We find that a specific defect remains unfixed on average 
+    for 3 revisions.
+% Security bug persistence between versions. 
+%We expect that
+%security bugs should be eliminated earlier than other bugs.
+	\item We show that many defect types are correlated with the project's
+    size (with the notable exception of high-risk security defects).
+%Our hypothesis is that security bugs are proportional to a project
+%version's size.  Here, size is defined in terms of bytecode.
+	\item We show that a code base can have defect hotspots.
+%Our
+%hypothesis is that security bugs flock together with bugs that have to do with
+%performance, coding practices and others.
 %	\item The relation of software dependencies and security bugs. Our
@@
 %should have a low rate of security bugs. 
+  \item We make available a carefully constructed dataset and a statistical toolkit for
+    performing analysis of the Java Maven ecosystem.
 \end{itemize}

### 2013-04-08 docs/evol.tex
reverted to hypothesis

--- 2013-04-08 docs/evol.tex
@@
 
-The main contributions of this research are:
+In this work we:
 \begin{itemize}
-	\item The analysis of how security bugs found through static analysis,
+	\item Analyze how security bugs found through static analysis,
 evolve over time. To achieve this, we inspect every project per version.
@@
 they are critical and developers should eliminate them.
-	\item Security bug persistence between versions. We expect that
-security bugs should be eliminated earlier than other bugs.
-	\item The relation between security bugs and a project
+%We present evidence that defect counts remain relatively stable
+%across project revisions.
+	\item Examine security bug persistence between versions. 
+We expect that security bugs should be eliminated earlier than other bugs.
+%We find that a specific defect remains unfixed on average 
+%for 3 revisions.
+	\item Study the relation between security bugs and a project
 version's size. Our hypothesis is that security bugs are proportional to a project
 version's size. Here, size is defined in terms of bytecode.
-	\item The correlation of security bugs with other bug categories. Our
-hypothesis is that security bugs flock together with bugs that have to do with
-performance, coding practices and others.
+%We show that many defect types are correlated with the project's
+%size (with the notable exception of high-risk security defects).
+	\item Examine the correlation of security bugs with other bug categories.
+Our hypothesis is that security bugs flock together with bugs that
+have to do with performance, coding practices and others.
+%We show that a code base can have defect hotspots.
 %	\item The relation of software dependencies and security bugs. Our
@@
 %should have a low rate of security bugs. 
+  %\item Make available a carefully constructed dataset and a statistical toolkit for
+   % performing analysis of the Java Maven ecosystem.
 \end{itemize}
@@
 Also, it is interesting to see that security bugs were one of the top two
-bug categories existing in a large ecosystem. Finally, we highlighted the
+bug Make available a carefully constructed dataset and a statistical toolkit for
+    performing analysis of the Java Maven ecosystem.
+categories existing in a large ecosystem. Finally, we highlighted the
 domino effect, and showed evidence that indicates that the Linus' Law does not

### 2013-04-08 docs/evol.tex
minor fix
minor corrections and ammendments

@@
 an application, steal data or prevent the application from working at all.
-We used the Maven repository to study the
+We used the projects stored in the Maven repository to study the
 characteristics of security bugs individually and in relation to other software
@@
 size of the corresponding version and b) other bug categories. Our findings
-indicated that security bugs neither increase or decrease as a project evolves.
+indicate that there is no simple relationship between the number of
+security bugs and project evolution.
 In addition, they are not eliminated in a way that is particularly
-different from the other bugs. Also, their relation with the
-size appeared to be different from the other categories. Finally, even if bugs
+different from the other bugs. Their relation with
+size appears to be different from the other categories. Finally, even if bugs
 seem to flock together, severe security bugs
@@
 \begin{itemize}
-	\item Analyze how security bugs found through static analysis,
-evolve over time. To achieve this, we inspect every project per version.
+	\item Analyze how security bugs found through static analysis
+evolve over time. To achieve this, we inspected every project per version.
 Our hypothesis is that security bugs should decrease as a project evolves since
@@
 A threat to the internal validity of our experiment could be the false alarms of the
-FindBugs tool. The false positives and negatives of static analysis tools and
-how they can be reduced, is an issue that has already been discussed in literature (see
+FindBugs tool. False positives and negatives of static analysis tools and
+how they can be reduced is an issue that has already been discussed in literature (see
 Section~\ref{sec:rel}). Furthermore, consider a false positive alarm where an
@@
 
-In this work we analyzed a large software repository to examine the behavior
-of security bugs. Specifically, we analyzed more than 260GB of interdependent
-projcet versions to see how security bugs evolve over time, their
-persistence, and their relation with other bug categories and the size in
-terms of bytecode.
+In this work we analyzed a large software repository to examine the
+behavior of security bugs. Specifically, we analyzed more than 260GB
+of interdependent project versions to see how security bugs evolve
+over time, their persistence, their relation with other bug
+categories, and their relationship with size in terms of bytecode.
 
-Our primary hypothesis was that security bugs and especially severe
-ones, should be corrected as projects evolve. However, our findigs indicate that this is
-not true. Contrary to our second research hypothesis, we showed that security
+Our primary hypothesis was that security bugs, and especially severe
+ones, should be corrected as projects evolve. We found that, although
+bugs do close over time in particular projects, we do not have an indication that across
+projects they decrease as projects mature. Moreover, defect counts may
+increase, as well as decrease in time. Contrary to our second research hypothesis, we showed that security
 bugs are not eliminated in a way that is particularly different from the other bugs.
@@
 The versions examined in this work were actual releases
-of the projets. As a result we do not have an indication of how many changes
+of the projects. As a result we do not have an indication of how many changes
 have been made between the releases.

### 2013-04-08 docs/evol.tex
minor fix

@@
 
-\subsubsection{How Security Bugs E(over versions)volve Over Time}
+\subsubsection{How Security Bugs Evolve Over Time}
 
@@
 Also, it is interesting to see that security bugs were one of the top two
-bug Make available a carefully constructed dataset and a statistical toolkit for
-    performing analysis of the Java Maven ecosystem.
-categories existing in a large ecosystem. Finally, we highlighted the
+bug categories existing in a large ecosystem. Finally, we highlighted the
 domino effect, and showed evidence that indicates that the Linus' Law does not

### 2013-04-08 docs/evol.tex
minor change in the threats to validity section

@@
 how they can be reduced is an issue that has already been discussed in literature (see
-Section~\ref{sec:rel}). Furthermore, consider a false positive alarm where an
+Section~\ref{sec:rel}). Furthermore, consider the case where a
 security bug is reported, but it is invalidated based on the context of the
-application (an {\sc sql} injection vulnerability~\cite{RL12} in an application that
-requires no external input).
+application. For instance, an {\sc sql} injection vulnerability~\cite{RL12}
+in an application that requires no external input could be reported by FindBugs,
+but in this case would be a false positive alarm.
 

### 2013-04-08 docs/evol.tex
minor fix
fix: typos

@@
 seem to flock together, severe security bugs
-seem to be unassociated with other categories.
+seem to be dissociated with other categories.
 \end{abstract}
@@
 The goal of our experiment was to retrieve all the bugs that FindBugs reports,
-for all the project versions existing on the Maven repository.
+from all the project versions existing on the Maven repository.
 The experiment involved four entities:
@@
 In this work we analyzed a large software repository to examine the
-behavior of security bugs. Specifically, we analyzed more than 260GB
+behavior of security bugs. Specifically, we analysed more than 260GB
 of interdependent project versions to see how security bugs evolve
@@
 Contrary to the approaches that examine all versions
-formed after every change that has been commited to the repository,
+formed after every change that has been committed to the repository,
 our observations are made from a different perspective.

### 2013-04-08 docs/evol.tex
fixed some latex errors

@@
   \begin{center}
-    \includegraphics[scale=0.7]{figures/arch.pdf}
+    \includegraphics[scale=0.9]{figures/arch.pdf}
   \end{center}
@@
 coding practice. \\
-Correctness & Involves coding mistin a way that is particularly different from the other bugsakes resulting in code
+Correctness & Involves coding misting a way that is particularly different from the other bug sakes resulting in code
 that was probably not what the developer intended. \\
@@
   \centering
-  \includegraphics[scale=0.4]{bugsversionscorr}
+  \includegraphics[width=\textwidth]{bugsversionscorr}
   \caption{Histograms of correlations between bug counts and version

### 2013-04-08 docs/evol.tex
Copy-edit introduction

@@
 software defects. This is because compared to other bug categories,
-the category of security bugs has two distinct features: it is critical~\cite{SZ12}
-for an organization's infrastructure
-and moreover it can cause significant financial damage to 
+failures due to security bugs have two distinct features:
+they can severeyl affect an organization's infrastructure\cite{SZ12}, and
+they can cause significant financial damage to
 an organization~\cite{TH04}\cite{BCL08}\cite{R06}. 
-Specifically, a software bug can
-lead to a malfunction of a software artifact that runs under specific
-requirements but a security bug can allow a malicious user to alter the execution
-of the entire application for his or her own gain. In this case, such bugs could span a wide
-range of security and privacy issues, like viewing sensitive information, the destruction or
-modification of sensitive data, denial of service and others.
+Specifically,
+whereas a software bug can cause a software artifact to fail,
+a security bug can allow a malicious user to alter the execution
+of the entire application for his or her own gain.
+In this case, such bugs could give rise to a wide
+range of security and privacy issues, like
+the access of sensitive information,
+the destruction or modification of data, and
+denial of service.
 Moreover, security bug disclosures lead to a negative and significant change
@@
 The motivation behind our work was to validate whether programmers care for
-such high-risk bugs when they release a new version of their software. In
-addition, we wanted to investigate other critical features associated with such
-vulnerabilities like the persistence of a bug; in essence, to check if critical bugs stay
-unresolved for a long time. Also, we wanted to elaborate more on the relation of security
-bugs not only with performance bugs (as Zaman et al.~\cite{ZAH11} have already
-done) but also with other bug categories. In the same manner, we tried to check
-the relation between version size and security bugs, knowing the
-that research has been contradictory on the the
+the risk posed by security bugs when they release a new version of their software.
+In addition, we wanted to investigate other critical features associated with such
+vulnerabilities like the persistence of a bug;
+in essence, to see whether critical bugs stay unresolved for a long time.
+Also, we wanted to elaborate more on the relation of security
+bugs with other bug categories.
+In the same manner, we tried to looked at the relationship
+between successive product versions and the number of security bugs,
+knowing the that research has produced contradictory results on this
 issue~\cite{BP84}\cite{SYTP85}\cite{NBZ06}\cite{GKMS00}.
@@
 	\item Analyze how security bugs found through static analysis
-evolve over time. To achieve this, we inspected every project per version.
-Our hypothesis is that security bugs should decrease as a project evolves since
-they are critical and developers should eliminate them.
+evolve over time. To achieve this, we inspected all releases of every project.
+Our hypothesis is that security bugs should decrease as a project evolves,
+for they form critical issues, which developers should eliminate.
 %We present evidence that defect counts remain relatively stable
 %across project revisions.
-	\item Examine security bug persistence between versions. 
+	\item Examine security bug persistence across releases. 
 We expect that security bugs should be eliminated earlier than other bugs.
@@
 	\item Study the relation between security bugs and a project
-version's size. Our hypothesis is that security bugs are proportional to a project
-version's size. Here, size is defined in terms of bytecode.
+release's size. Our hypothesis is that security bugs are proportional to a project
+release's size (defined in terms of bytecode size).
 %We show that many defect types are correlated with the project's
@@
 	\item Examine the correlation of security bugs with other bug categories.
-Our hypothesis is that security bugs flock together with bugs that
-have to do with performance, coding practices and others.
+Our hypothesis is that security bugs appear together with bugs that
+are related with performance, coding practices, and product stability.
 %We show that a code base can have defect hotspots.

### 2013-04-08 docs/evol.tex
abstract - corrections

@@
 the repository's features (multiple versions for every project, dependencies) we studied
-the evolution of security bugs through time, their persistence and their relationship with a) the
+the evolution of security bugs through time. In addition, we examined
+their persistence and their relationship with a) the
 size of the corresponding version and b) other bug categories. Our findings
 indicate that there is no simple relationship between the number of
-security bugs and project evolution.
-In addition, they are not eliminated in a way that is particularly
-different from the other bugs. Their relation with
-size appears to be different from the other categories. Finally, even if bugs
-seem to flock together, severe security bugs
-seem to be dissociated with other categories.
+security bugs and project evolution. In particular, we
+cannot say that across projects defect counts increase or decrease
+significantly over time. Furthermore, security bugs are not eliminated in a
+way that is particularly different from the other bugs. Also, the relation of
+such bugs with size appears to be different from the relation of the bugs
+coming from other categories. Finally, even if bugs seem to have similar behaviour,
+severe security bugs seem to be dissociated with other categories.
 \end{abstract}

### 2013-04-08 docs/evol.tex
Improve validity threats

--- 2013-04-08 docs/evol.tex
@@
 FindBugs tool. False positives and negatives of static analysis tools and
-how they can be reduced is an issue that has already been discussed in literature (see
-Section~\ref{sec:rel}). Furthermore, consider the case where a
-security bug is reported, but it is invalidated based on the context of the
-application. For instance, an {\sc sql} injection vulnerability~\cite{RL12}
-in an application that requires no external input could be reported by FindBugs,
-but in this case would be a false positive alarm.
+how they can be reduced is an issue that has already been discussed in the literature
+(see Section~\ref{sec:rel}).
+In addition, reported security bugs may not be applicable to an
+application's typical use context.
+For instance, FindBugs could report an {\sc sql} injection vulnerability~\cite{RL12}
+in an application that receives no external input.
+In this particular context, this would be a false positive alarm.
 
-We also have to mention that our analysis is done on projects written in the
-Java programming language. Hence, a threat to the external validity of our work
-is the fact that our results may not be the same in another programming
-environment.
+Furthermore, given that our analysis is done on open-source projects
+written in the Java programming language and hosted on Maven,
+a threat to the external validity of our work
+is the fact that our results may not be applicable to other
+programming languages, ecosystems, and development cultures.
 

### 2013-04-08 docs/evol.tex
tiny change
Diverse small changes in 3.1 and conclusions

@@
 
-To examine {\it Linus' Law} in relation to the rate of the
+To examine {\it Linus's Law} in relation to the rate of the
 security bugs~\cite{MW10}, and highlight the
 {\it domino effect}~\cite{TH04} we did the
-following: during the experiment we managed to retrieve the
+following: during the experiment we retrieved the
 dependencies of every version. Based on this information we created a graph
@@
 examined the security bugs of the fifty most popular nodes based on their PageRank.
-Contrary to Linus' Law, thirty three of them contained bugs coming from the
+Contrary to Linus's Law, thirty three of them contained bugs coming from the
 {\it Security Low} subcategory, while two of them contained severe bugs.
@@
 Our primary hypothesis was that security bugs, and especially severe
-ones, should be corrected as projects evolve. We found that, although
+ones, would be corrected as projects evolve. We found that, although
 bugs do close over time in particular projects, we do not have an indication that across
 projects they decrease as projects mature. Moreover, defect counts may
-increase, as well as decrease in time. Contrary to our second research hypothesis, we showed that security
+increase, as well as decrease in time. Contrary to our second research hypothesis,
+we found that security
 bugs are not eliminated in a way that is particularly different from the other bugs.
@@
 case of the {\it Security High} bugs. Concerning the relation between severe security bugs and a project's size
-we showed evidence that they are not proportionally related. Furthermore, the
+we showed that they are not proportionally related. Furthermore, the
 pairwise correlations between all categories indicated that even though all the other
-categories are related, severe bugs do not flock together with the other bugs.
+categories are related, severe bugs do not appear together with the other bugs.
 Also, it is interesting to see that security bugs were one of the top two
 bug categories existing in a large ecosystem. Finally, we highlighted the
-domino effect, and showed evidence that indicates that the Linus' Law does not
+domino effect, and showed evidence that indicates that Linus's Law does not
 apply in the case of the security bugs.

### 2013-04-08 docs/evol.tex
Copy-edit abstract

@@
 popular static analysis tool. Then by taking advantage of
-the repository's features (multiple versions for every project, dependencies) we studied
+the repository's project history and dependency data we studied
 the evolution of security bugs through time. In addition, we examined
-their persistence and their relationship with a) the
-size of the corresponding version and b) other bug categories. Our findings
-indicate that there is no simple relationship between the number of
-security bugs and project evolution. In particular, we
-cannot say that across projects defect counts increase or decrease
-significantly over time. Furthermore, security bugs are not eliminated in a
-way that is particularly different from the other bugs. Also, the relation of
-such bugs with size appears to be different from the relation of the bugs
-coming from other categories. Finally, even if bugs seem to have similar behaviour,
-severe security bugs seem to be dissociated with other categories.
+their persistence and their relationship with
+a) the size of the corresponding version, and
+b) other bug categories.
+Our findings indicate that there is no simple rule governing the number of
+security bugs as a project evolves.
+In particular, we cannot say that across projects security-related
+defect counts increase or decrease significantly over time.
+Furthermore, security bugs are not eliminated in a
+way that is particularly different from the other bugs.
+In addition, the relation of security bugs with a project's size
+appears to be different from the relation of the bugs
+coming from other categories.
+Finally, even if bugs seem to have similar behaviour,
+severe security bugs seem to be unassociated with other bug categories.
 \end{abstract}

### 2013-04-08 docs/evol.tex
corrections - after dds' comments

@@
 
-% In the rest of this paper we
-% describe the processing of our data and our experiment (Section \ref{sec:meth}),
-% present and discuss the results we obtained (Section \ref{sec:res}),
-% outline related work (Section \ref{sec:rel}),
-% and end up with a conclusion and directions for future work (Section \ref{sec:con}).
+In the rest of this paper we
+describe the processing of our data and our experiment (Section \ref{sec:meth}),
+present and discuss the results we obtained (Section \ref{sec:res}),
+outline related work (Section \ref{sec:rel}),
+and end up with a conclusion and directions for future work (Section \ref{sec:con}).
 
@@
 
-To examine {\it Linus's Law} in relation to the rate of the
+{\it Linus's Law} states that ``given enough eyeballs, all bugs are shallow".
+To examine Linus's Law in relation to the rate of the
 security bugs~\cite{MW10}, and highlight the
@@
 \label{sec:analysis}
+
+Here, we present our key findings concerning the evolution of security bugs.
 
@@
   \centering
-  \includegraphics[scale=0.4]{bugdiffs}
+  \includegraphics[width=\textwidth]{bugdiffs}
   \caption{Histograms of the time, measure in versions, it takes for a

### 2013-04-08 docs/evol.tex
correct bib

@@
 A security bug is a programming error that introduces a potentially exploitable
-weakness into a computer system~\cite{SSL12}\cite{TJBD11}\cite{M06}. This
+weakness into a computer system~\cite{SSL12,TJBD11,M06}. This
 weakness could lead to a security breach with unfortunate consequences in
@@
 bugs~\cite{SZ12}, little attention has been paid to study them in relation to
-software evolution~\cite{L96}\cite{LRWPT97}\cite{IB06}\cite{RGMA06}. 
+software evolution~\cite{L96,LRWPT97,IB06,RGMA06}. 
 One of the most common approaches to identify security bugs is
@@
 a static analysis tool that examines bytecode to detect software bugs and has already been used in
-research~\cite{AP10}\cite{HP07}\cite{HP04}\cite{HW08}\cite{SHP06}.
+research~\cite{AP10,HP07,HP04,HW08,SHP06}.
 Specifically, we ran FindBugs on all the project
@@
 they can cause significant financial damage to
-an organization~\cite{TH04}\cite{BCL08}\cite{R06}. 
+an organization~\cite{TH04,BCL08,R06}. 
 Specifically,
@@
 knowing the that research has produced contradictory results on this
-issue~\cite{BP84}\cite{SYTP85}\cite{NBZ06}\cite{GKMS00}.
+issue~\cite{BP84,SYTP85,NBZ06,GKMS00}.
 Finally, we examined the Maven ecosystem as a whole from a security
@@
 regarding the evolution history of a project~\cite{HG05}. Bhattacharya et
-al.~\cite{BN11}\cite{B11} proposed a framework that is based upon
+al.~\cite{BN11,B11} proposed a framework that is based upon
 recursively enumerable languages. The framework can correlate software
@@
 high priority bugs are fixed over time. To improve the precision of bug
-detection, Kim et al.~\cite{KE07b}\cite{KE07} proposed a history-based warning
+detection, Kim et al.~\cite{KE07b,KE07} proposed a history-based warning
 prioritization algorithm by mining the history of bug-fixes of three
@@
 this warning category is important. Working towards the same direction, Heckman
-et al.~\cite{HW09}\cite{HW08} have introduced benchmarks that use specific
+et al.~\cite{HW09,HW08} have introduced benchmarks that use specific
 correlation algorithms and classification techniques to evaluate alert

### 2013-04-08 docs/evol.tex
semi-final
fixed bug_percent histogram
new measurements for the severe bugs - with the updated data

@@
   \begin{center}
-    \includegraphics[scale=0.9]{figures/arch.pdf}
+    \includegraphics[scale=0.75]{figures/arch.pdf}
   \end{center}
@@
 	\centering
-	\includegraphics[scale=0.4]{version_count.pdf}
-	\caption{Distribution of
-Version Count Among Project Population}
+	\includegraphics[scale=0.45]{version_count.pdf}
+	\caption{Distribution of Version Count Among Project Population}
 	\label{fig:version-count}
@@
  	\hline
-	{\sc hrs}: {\sc http} cookie formed from untrusted input & 149\\
-	{\sc hrs}: {\sc http} response splitting vulnerability & 1,564\\
-	{\sc pt}: absolute path traversal in servlet  & 92\\
-	{\sc pt}: relative path traversal in servlet & 50\\
-	{\sc sql}: non-constant string passed to execute method on an {\sc sql} & 1,817\\
-	{\sc sql}: a prepared statement is generated from a non-constant String & 1,438\\
-	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 17\\
-	{\sc xss}: Servlet reflected cross site scripting vulnerability in error page & 88\\
-	{\sc xss}: Servlet reflected cross site scripting vulnerability & 140\\
+	{\sc hrs}: {\sc http} cookie formed from untrusted input & 151\\
+	{\sc hrs}: {\sc http} response splitting vulnerability & 1,579\\
+	{\sc pt}: absolute path traversal in servlet  & 103\\
+	{\sc pt}: relative path traversal in servlet & 57\\
+	{\sc sql}: non-constant string passed to execute method on an {\sc sql} statement & 1,875\\
+	{\sc sql}: a prepared statement is generated from a non-constant String & 1,486\\
+	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 18\\
+	{\sc xss}: Servlet reflected cross site scripting vulnerability in error page & 90\\
+	{\sc xss}: Servlet reflected cross site scripting vulnerability & 142\\
 	\hline
@@
 Table~\ref{tbl:sev} presents the number
-of releases where at least one of these bugs exists. In essence, 5,355 releases
-($\approx 4,64\% $), contained at
+of releases where at least one of these bugs exists. In essence, 5,501 releases
+($\approx 4,77\% $), contained at
 least one severe security bug. Given the fact that other projects include these
@@
 	\centering
-	\includegraphics[scale=0.4]{bug_percent}
+	\includegraphics[scale=0.45]{bug_percent}
 	\caption{Bug Percentage in Maven Repository}
@@
   \includegraphics[width=\textwidth]{bugdiffs}
-  \caption{Histograms of the time, measure in versions, it takes for a
-    bug to be closed. }
+  \caption{Histograms of the time, measure in versions, it takes for a bug to be closed. }
   \label{fig:bugdiffs}
@@
 
-Our data and code are publicly available and can be found under the following
-GitHub address: \url{https://github.com/bkarak/evol_security_publication_2012}.
+Our data and code will be publicly available upon publication.
 

### 2013-04-08 docs/evol.tex
final

@@
 bugs. In particular, we analyzed every project version of the repository by using a
-popular static analysis tool. Then by taking advantage of
+popular static analysis tool. Then, by taking advantage of
 the repository's project history and dependency data we studied
@@
 failures due to security bugs have two distinct features:
-they can severeyl affect an organization's infrastructure\cite{SZ12}, and
+they can severely affect an organization's infrastructure~\cite{SZ12}, and
 they can cause significant financial damage to
@@
 bugs with other bug categories.
-In the same manner, we tried to looked at the relationship
-between successive product versions and the number of security bugs,
+In the same manner, we tried to examine the relationship
+between the size of a project release and the number of security bugs that it contains,
 knowing the that research has produced contradictory results on this
@@
 
+\begin{figure}[t]
+  \begin{center}
+    \includegraphics[scale=0.75]{figures/arch.pdf}
+  \end{center}
+  \caption{The Data Processing Architecture}
+  \label{fig:arch}
+\end{figure}
+
 The goal of our experiment was to retrieve all the bugs that FindBugs reports,
@@
 results to the data repository.
-
-\begin{figure}[t]
-  \begin{center}
-    \includegraphics[scale=0.75]{figures/arch.pdf}
-  \end{center}
-  \caption{The Data Processing Architecture}
-  \label{fig:arch}
-\end{figure}
 
@@
 \leavevmode
-	\begin{tabular}{p{25em} r}
+	\begin{tabular}{p{24em} r}
 	\hline
@@
 
+\begin{figure*}[t]
+	\centering
+	\includegraphics[scale=0.45]{bug_percent}
+	\caption{Bug Percentage in Maven Repository}
+	\label{fig:bug-per} 
+\end{figure*}
+
 Another observation involves bugs that we could call {\it
@@
 in another subcategory that we call {\it Security Low}.
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[scale=0.45]{bug_percent}
-	\caption{Bug Percentage in Maven Repository}
-	\label{fig:bug-per} 
-\end{figure*}
 
@@
 
+\begin{table}[t]
+    \centering
+    \caption{Correlations between Version and Defects Count}
+    \label{tbl:bugsperversion}
+    \input{bugsperversion.tex}
+\end{table}
+
 The relation between bugs and time can be traced from the number of
@@
 counts to increase, this tendency is extremely slight.
-
-\begin{table}[t]
-    \centering
-    \caption{Correlations between Version and Defects Count}
-    \label{tbl:bugsperversion}
-    \input{bugsperversion.tex}
-\end{table}
 
@@
 
-Overall, Table~\ref{tbl:bugsperversion} and
-Figure~\ref{fig:bugsversionscorr} suggest that \textbf{we cannot say that
-across projects defect counts increase or decrease significantly
-across time}. In individual projects, however, defect counts can have a
-strong upwards or downwards tendency. There may be no such thing as a
-``project'' in general, only particular projects with their own
-idiosyncrasies, quality features, and coding practices.
-
 \begin{figure*}[t]
@@
 \end{figure*}
+
+Overall, Table~\ref{tbl:bugsperversion} and
+Figure~\ref{fig:bugsversionscorr} suggest that \textbf{we cannot say that
+across projects defect counts increase or decrease significantly
+across time}. In individual projects, however, defect counts can have a
+strong upwards or downwards tendency. There may be no such thing as a
+``project'' in general, only particular projects with their own
+idiosyncrasies, quality features, and coding practices.
 

### 2013-04-08 docs/evol.tex
minor change

@@
 The goal of our experiment was to retrieve all the bugs that FindBugs reports,
-from all the project versions existing on the Maven repository.
-The experiment involved four entities:
+from all the project versions existing on the Maven repository (in the Maven
+repository, versions are {\it actual} releases). The experiment involved four entities:
 a number of {\it workers} (a custom Python script), a {\it task queue}
@@
 Table~\ref{tbl:bug-cat}). Two of them involve security issues: {\it Security} and {\it
-Malicious Code}. From the total number of versions, 4,353 of them contained
+Malicious Code}. From the total number of releases, 4,353 of them contained
 at least one bug coming from the first category

### 2013-06-19 docs/evol.tex
new style

@@
-\documentclass[conference]{llncs}
+\documentclass{sig-alternate}
 
@@
 
-\author{Dimitris Mitropoulos \and Vassilios Karakoidas \and Panos Louridas \and Georgios Gousios \and Diomidis Spinellis }
-\institute{ Department of Management Science and Technology\\
-			Athens University of Economics and Business\\
-      		\email{\{dimitro, bkarak, louridas, dds\}@aueb.gr}\\
-			Software Engineering Research Group\\
-			Delft University of Technology\\
-			\email{G.Gousios@tudelft.nl}}
+\numberofauthors{5}
+
+\author{
+% 1st. author
+\alignauthor
+Dimitris Mitropoulos\\
+       \affaddr{Department of Management Science and Technology}\\
+       \affaddr{Athens University of Economics and Business}\\
+       \email{dimitro@aueb.gr}
+% 2nd. author
+\alignauthor
+Vassilios Karakoidas\\
+       \affaddr{Department of Management Science and Technology}\\
+       \affaddr{Athens University of Economics and Business}\\
+       \email{bkarak@aueb.gr}
+% 3rd. author
+\alignauthor
+Panos Louridas\\
+       \affaddr{Department of Management Science and Technology}\\
+       \affaddr{Athens University of Economics and Business}\\
+       \email{louridas@aueb.gr}
+\and  % use '\and' if you need 'another row' of author names
+% 4th. author
+\alignauthor Georgios Gousios\\
+       \affaddr{Software Engineering Research Group}\\
+       \affaddr{Delft University of Technology}\\
+       \email{G.Gousios@tudelft.nl}
+% 5th. author
+\alignauthor Diomidis Spinellis\\
+       \affaddr{Department of Management Science and Technology}\\
+       \affaddr{Athens University of Economics and Business}\\
+       \email{dds@aueb.gr}
+}
 
 \maketitle
-
 \begin{abstract}
-%\boldmath
 Security bugs are critical programming errors that can lead to serious
@@
 
-\begin{keywords}
-Security Bugs, Static Analysis, Software Evolution, Software
+\keywords{Security Bugs, Static Analysis, Software Evolution, Software
 Security, Maven, FindBugs.
-\end{keywords}
-
+}
 \section{Introduction}
@@
 security bugs (the sum of the {\it Security} and {\it Malicious Code}
-categories) are the most popular in the repository ($\geq 22\%$ each).
+categories) are the most popular in the repository ($\geq 21\%$ each).
 This could be a strong indication that programmers write code
@@
 
-\section*{Acknowledgements}
-
+\section{Acknowledgments}
 This research has been co-financed by the European Union (European Social Fund
@@
 
-\bibliographystyle{splncs}
+\bibliographystyle{abbrv}
 \bibliography{evol}

### 2013-06-21 docs/evol.tex
correct caption
changed pic and table sizes

@@
 before invoking FindBugs. After the project filtering, we narrowed down
-our data set to 17,055 projects with 115,214 versions.
+our data set to 17,505 projects with 115,214 versions.
 Table~\ref{tbl:repository} summarises the data set information and
@@
 
-\begin{table}[t]
+\begin{table*}[t]
 \centering
@@
 \label{tbl:bug-cat}
-\begin{tabular}{l p{23em}}
+\begin{tabular}{l p{35em}}
 \hline
@@
 \end{tabular}
-\end{table}
+\end{table*}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{bugsversionscorr}
+  \includegraphics[scale=0.35]{bugsversionscorr}
   \caption{Histograms of correlations between bug counts and version
@@
   \includegraphics[width=\textwidth]{bugdiffs}
-  \caption{Histograms of the time, measure in versions, it takes for a bug to be closed. }
+  \caption{Changes in bug counts between versions.}
   \label{fig:bugdiffs}

### 2013-06-21 docs/evol.tex
work on the reviewers comments

@@
 
+Maven is a build automation tool used primarily for Java projects and it is
+hosted by the Apache Software Foundation.\footnote{\url{http://www.apache.org/}}
+To describe the software project being built, its dependencies
+on other external modules, the build order, and required plug-ins Maven uses
+{\sc xml}. To build a software component, it dynamically downloads Java libraries
+and Maven plug-ins from the Maven central repository,
+and stores them in a local cache. The repository can be updated with
+new projects and also with new versions of existing projects.
+
 First, we scanned the Maven repository for appropriate {\sc jar}s and created a
@@
 
-Maven is a build automation tool used primarily for Java projects and it is
-hosted by the Apache Software Foundation.\footnote{\url{http://www.apache.org/}}
-To describe the software project being built, its dependencies
-on other external modules, the build order, and required plug-ins Maven uses
-{\sc xml}. To build a software component, it dynamically downloads Java libraries
-and Maven plug-ins from the Maven central repository,
-and stores them in a local cache. The repository can be updated with
-new projects and also with new versions of existing projects.
-
 Initially, we obtained a snapshot (January 2012) of the Maven repository and
@@
 {\it group id}, {\it artifact id} and {\it version}.
+
+FindBugs is an open source static analysis tool that
+searches for software bugs. It works by examining the compiled Java virtual
+machine bytecodes of the programs it checks, using the bytecode engineering
+library ({\sc bcel}).
+To detect a bug, FindBugs uses various formal methods like
+{\it control flow} and {\it data flow
+analysis}. It has also other detectors that employ {\it visitor patterns} over
+classes and methods by using {\it state machines} to reason about values stored
+in variables or on the stack.
 Since FindBugs analyses applications written in the Java

### 2013-06-24 docs/evol.tex
more on the reviewers comments

@@
 versions of all the projects that exist in the
-{\it Maven Central Repository}\footnote{\url{http://search.maven.org/}}
+{\it Maven Central Repository}\footnote{\url{http://mvnrepository.com/}}
 (approximately 265GB of data---see Section~\ref{sec:data}).
@@
 programming languages, ecosystems, and development cultures.
+In particular, a large class of security problems such as
+buffer overflows~\cite{K11} do not apply in our study since
+Java enforces bound checking at runtime.
 
@@
 in another subcategory that we call {\it Security Low}.
+Note that this categorization was done specifically for this research to point out the
+behaviour of bugs that currently top the corresponding lists of most
+security providers.\footnote{\url{http://cwe.mitre.org/top25/index.html}}
 

### 2013-06-25 docs/evol.tex
more on the comments

@@
 provides the basic descriptive statistic measurements. The distribution of version
-count among the selected projects is presented in Figure \ref{fig:version-count}.
+count among the selected projects is presented in Figure~\ref{fig:version-count}.
 
@@
 in an application that receives no external input.
-In this particular context, this would be a false positive alarm.
+In this particular context, this would be a false positive alarm~\cite{AP10}.
 
@@
 {\it Linus's Law} states that ``given enough eyeballs, all bugs are shallow".
-To examine Linus's Law in relation to the rate of the
-security bugs~\cite{MW10}, and highlight the
+In a context like this, we expect that
+the project versions that are dependencies to many other projects,
+would have a small number of security
+bugs. To examine this variation of the Linus's Law and highlight the
 {\it domino effect}~\cite{TH04} we did the
@@
 Twenty five of them were latest versions at the time. This also highlights
-the domino effect. No matter how well a programmer secures a software component
-it won't matter if he or she is using vulnerable code fragments coming
-from another library.
+the domino effect.
+%No matter how well a programmer secures a software component
+%it won't matter if he or she is using vulnerable code fragments coming
+%from another library.
 

### 2013-06-25 docs/evol.tex
minor changes

@@
 A threat to the internal validity of our experiment could be the false alarms of the
-FindBugs tool. False positives and negatives of static analysis tools and
+FindBugs tool~\cite{AP10, HP04}. False positives and negatives of static analysis tools and
 how they can be reduced is an issue that has already been discussed in the literature
@@
 in an application that receives no external input.
-In this particular context, this would be a false positive alarm~\cite{AP10}.
+In this particular context, this would be a false positive alarm.
 

### 2013-06-25 docs/evol.tex
more on the related work

@@
 the percentage of remotely exploitable vulnerabilities has gradually increased
-over the years.
+over the years. Finally, Edwards et al.~\cite{EC12} have recently conducted
+a similar study to ours in which they have considered only four projects.
+Their results demonstrate that the number of exploitable bugs, does not
+always improve with each new release and that the rate of discovery of
+exploitable bugs begins to drop three to five years after the
+initial release.
 

### 2013-06-26 docs/evol.tex
trying to make some space adjustments with no luck
paper size changes
fixed layout
content is ready

@@
 % 1st. author
-\alignauthor
-Dimitris Mitropoulos\\
+\alignauthor Dimitris Mitropoulos\\
        \affaddr{Department of Management Science and Technology}\\
@@
 % 2nd. author
-\alignauthor
-Vassilios Karakoidas\\
+\alignauthor Vassilios Karakoidas\\
        \affaddr{Department of Management Science and Technology}\\
@@
 % 3rd. author
-\alignauthor
-Panos Louridas\\
+\alignauthor Panos Louridas\\
        \affaddr{Department of Management Science and Technology}\\
@@
 
-\begin{figure*}[t]
+\begin{figure}[t]
 	\centering
-	\includegraphics[scale=0.45]{version_count.pdf}
+	\includegraphics[scale=0.42]{version_count.pdf}
 	\caption{Distribution of Version Count Among Project Population}
 	\label{fig:version-count}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[t]
+\begin{figure}[t]
 	\centering
-	\includegraphics[scale=0.45]{bug_percent}
+	\includegraphics[scale=0.39]{bug_percent}
 	\caption{Bug Percentage in Maven Repository}
 	\label{fig:bug-per} 
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[t]
-  \centering
-  \includegraphics[scale=0.35]{bugsversionscorr}
-  \caption{Histograms of correlations between bug counts and version
-    ordinals per project. In brackets the total population size and
-    the number of no correlation instances.}
-  \label{fig:bugsversionscorr}
-\end{figure*}
-
 Overall, Table~\ref{tbl:bugsperversion} and
@@
 
-\begin{figure*}[t]
+\begin{figure*}[p]
   \centering
-  \includegraphics[width=\textwidth]{bugdiffs}
+  \includegraphics[scale=0.30]{bugsversionscorr}
+  \caption{Histograms of correlations between bug counts and version
+    ordinals per project. In brackets the total population size and
+    the number of no correlation instances.}
+  \label{fig:bugsversionscorr}
+  \centering
+  \includegraphics[scale=0.35]{bugdiffs}
   \caption{Changes in bug counts between versions.}
@@
 bugs, and of security bugs in particular, we used as a persistence
-indicator the number of versions a bug remains open in a project. We
-grouped the persistence numbers by bug categories and then performed a
+indicator the number of versions a bug remains open in a project.
+To ``tag" a bug we created a bug identifier by using
+the type of the bug, the method name and the class name in which
+the bug was found in. We chose not to use the line number
+of the location of the bug since it could change from version
+to version and after a possible code refactoring.
+We grouped the persistence numbers by bug categories and then performed a
 Mann-Whitney $U$~\cite{HM98} test among all bug category pairs. The results are
@@
 in the decimal digits.
+
+\subsubsection{The Relation of Defects with the size of a {\sc jar}}
+
+We explored the relation between defects with the size of a project
+version, measured by the size of its {\sc jar} file by carrying out
+correlation tests between the size and the defect counts for each
+project and version. The results, all statistically significant ($p
+\ll 0.05$) can be seen in Table~\ref{tbl:jarsizecorr}.  \textbf{The {\it
+  Security High} category stands out by having a remarkably lower
+effect than the other categories}, even {\it Security Low} that nearly
+tops the list.
+% dds proposed the following:
+Given that, we could say that it would be productive to search for and fix
+security bugs even if a project grows bigger.
+
+\subsubsection{Security Bugs {\sc vs} Other Bug Categories}
+
+To see whether bugs flock together we performed pairwise correlations
+between all bug categories. We calculated the correlations between the
+number of distinct bugs that appeared in a project throughout its
+lifetime. The results can be seen in % Table~\ref{tbl:corrmatrix} and
+Figure~\ref{fig:corrplot}. We found significant, but not always
+strong, correlations between all pairs. In general, the {\it Security
+  High} category showed the weakest correlations with the other
+categories. Our results show that in general \textbf{bugs do flock together}.
+We do not find projects with only a certain kind of bug; bugs come
+upon projects in swarms of different kinds. Bugs of the {\it Security
+  High} category, though, are different: they are either not
+associated with other bugs, or only weakly so. Perhaps it takes a
+special kind of blunder to make it a security hazard.
+
+%\begin{table*}[t]
+%    \centering
+%    \caption{Correlation matrix}
+%    \label{tbl:corrmatrix}
+%    \input{corrmatrix.tex}
+%    \\
+%    \small The matrix presents pairwise correlations between the
+%        different bug categories.
+%\end{table*}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[scale=0.47]{corrplot.pdf}
+  \caption{Correlation matrix plot for bug categories}
+  \label{fig:corrplot}
+\end{figure}
 
@@
 
-\subsubsection{The Relation of Defects with the size of a {\sc jar}}
-
-We explored the relation between defects with the size of a project
-version, measured by the size of its {\sc jar} file by carrying out
-correlation tests between the size and the defect counts for each
-project and version. The results, all statistically significant ($p
-\ll 0.05$) can be seen in Table~\ref{tbl:jarsizecorr}.  \textbf{The {\it
-  Security High} category stands out by having a remarkably lower
-effect than the other categories}, even {\it Security Low} that nearly
-tops the list.
-
 \begin{table}[t]
@@
 \end{table}
-
-\subsubsection{Security Bugs {\sc vs} Other Bug Categories}
-
-To see whether bugs flock together we performed pairwise correlations
-between all bug categories. We calculated the correlations between the
-number of distinct bugs that appeared in a project throughout its
-lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
-Figure~\ref{fig:corrplot}. We found significant, but not always
-strong, correlations between all pairs. In general, the {\it Security
-  High} category showed the weakest correlations with the other
-categories. Our results show that in general \textbf{bugs do flock together}.
-We do not find projects with only a certain kind of bug; bugs come
-upon projects in swarms of different kinds. Bugs of the {\it Security
-  High} category, though, are different: they are either not
-associated with other bugs, or only weakly so. Perhaps it takes a
-special kind of blunder to make it a security hazard.
-
-\begin{table}[t]
-    \centering
-    \caption{Correlation matrix}
-    \label{tbl:corrmatrix}
-    \input{corrmatrix.tex}
-    \\
-    \small The matrix presents pairwise correlations between the
-        different bug categories.
-\end{table}
-
-\begin{figure*}[t]
-  \centering
-  \includegraphics[scale=0.6]{corrplot.pdf}
-  \caption{Correlation matrix plot for bug categories}
-  \label{fig:corrplot}
-\end{figure*}
 
@@
 of the projects have three versions, is not a positive result especially in the
-case of the {\it Security High} bugs. Concerning the relation between severe security bugs and a project's size
+case of the {\it Security High} bugs. Concerning the relation between
+severe security bugs and a project's size
 we showed that they are not proportionally related. Furthermore, the

### 2013-06-26 docs/evol.tex
minor changes

@@
 bugs~\cite{SZ12}, little attention has been paid to study them in relation to
-software evolution~\cite{L96,LRWPT97,IB06,RGMA06}. 
+software evolution~\cite{L96,LRWPT97}. 
 One of the most common approaches to identify security bugs is
@@
 a static analysis tool that examines bytecode to detect software bugs and has already been used in
-research~\cite{AP10,HP07,HP04,HW08,SHP06}.
+research~\cite{AP10,HP07,HW08,SHP06}.
 Specifically, we ran FindBugs on all the project
@@
 In the rest of this paper we
+outline related work (Section \ref{sec:rel}),
 describe the processing of our data and our experiment (Section \ref{sec:meth}),
 present and discuss the results we obtained (Section \ref{sec:res}),
-outline related work (Section \ref{sec:rel}),
 and end up with a conclusion and directions for future work (Section \ref{sec:con}).
+
+\section{Related Work}
+\label{sec:rel}
+
+There are numerous methods for mining software repositories in the context
+of software evolution~\cite{KCM07}. In this section we focus on the ones
+that highlight the relationship between software bugs and evolution and try to
+extract useful conclusions. The key idea behind this is
+similar to ours: the combination of information like bug descriptions,
+documentation and others with the information retrieved from either the source
+or object code of a project version.
+
+{\it Refactoring identification} through software evolution is an approach used to
+relate refactorings with software bugs. Wei{\ss}gerber et al. found that a high
+ratio of refactorings is usually followed by an increasing ratio of bug
+reports~\cite{WD06}. In addition, they indicated that software bugs are sometimes introduced
+after an incomplete refactoring~\cite{GW05}.
+Ratzinger et al.~\cite{RSG08} showed that the number of bugs decreases, when the number of
+refactorings increases. Finally, Kim M. et al.~\cite{KCK11} indicated that {\sc api}-level
+refactorings aid bug fixes.
+
+{\it Micro patterns}, proposed by Kim et al.~\cite{KPW06}
+detect bug-prone patterns among source code. Micro patterns describe programming
+idioms like inheritance, data management, immutability and others. The approach
+involves the examination of all revisions of three open-source projects to extract bug
+introduction rates for each pattern. Gil et al.~\cite{GM05} analysed the
+prevalence of micro patterns across five Sun {\sc jdk} versions to conclude that
+pattern prevalence tends to be the same in software collections.
+
+{\it Querying techniques} are used to answer a broad range of questions
+regarding the evolution history of a project~\cite{HG05}. Bhattacharya et
+al.~\cite{BN11,B11} proposed a framework that is based upon
+recursively enumerable languages. The framework can correlate software
+bugs with developers in various ways. For instance, return the list of
+bugs fixed by a specific developer. Fischer et al.~\cite{FPG03} proposed
+an approach for populating a release history database that combines code
+information with bug tracking data. In this way, a developer can couple files
+that contain common bugs, estimate code maturity with respect to the bugs
+and others. The ``Ultimate Debian Database''~\cite{NZ10} is an {\sc sql}-based
+framework that integrates information about the Debian project from various
+sources to answer queries related to software bugs and source code.
+
+D'Ambros et al. have used {\it bug history analysis} to detect
+the critical components of a project~\cite{D08}. This is done by using an
+evolutionary meta-model~\cite{DL08}. The same approach was
+also used by Zimmermann et al.~\cite{ZNA08} to check the correlation
+of bugs with software properties like code complexity, process quality and others
+and predict future properties.
+
+The evolution of software artifacts has also been analysed to {\it reduce the false
+alarms} of the various static analysis tools. To achieve this, Spacco et
+al.~\cite{SHP06} introduced {\it pairing} and {\it warning signatures}. In the
+former, they tried to pair sets of bugs between versions in order to find
+similar patterns. In the latter, they computed a signature for every bug. This
+signature contained elements like the name of the class where the bug was found,
+the method and others. Then they searched for similar signatures between
+versions. In their research they also studied the evolution of 116 sequential
+builds of the Sun Java Sevelopment Kit ({\sc jdk}). Their findings indicated that
+high priority bugs are fixed over time. To improve the precision of bug
+detection, Kim et al.~\cite{KE07b,KE07} proposed a history-based warning
+prioritization algorithm by mining the history of bug-fixes of three
+different projects. The algorithm was based on the following hypothesis: if a
+bug that belongs to a specific category is eliminated by a code change, then
+this warning category is important. Working towards the same direction, Heckman
+et al.~\cite{HW09,HW08} have introduced benchmarks that use specific
+correlation algorithms and classification techniques to evaluate alert
+prioritization approaches.
+
+Lu et al.~\cite{LAAL13} studied the {\it evolution of file-system code}.
+Specifically, they analysed the changes of Linux file-system patches to extract
+bug patterns and categorize bugs based on their impact. Their findings
+indicated that the number of file-system bugs does not die down over time. By
+categorizing bugs they also showed the frequency of specific bugs in specific
+components.
+
+Completing the above approaches, our work focuses on the subset of security bugs.
+Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
+the evolution of software defects by examining six major versions of Firefox.
+To achieve this they created a database schema that contained information
+coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
+list,\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
+Bugzilla entries and others. Their findings indicated that security bugs are
+persistent over time. They also showed that there are many web users that use
+old versions of Firefox, meaning that old attacks will continue to work.
+Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
+security bugs with performance bugs. This was also done by analysing the project's
+Bugzilla. Their research presented evidence that security bugs require more experienced developers
+to be fixed. In addition, they suggested that security bug fixes are more complex than the
+fixes of performance and other bugs.
+Shahzad et al.~\cite{SSL12} analysed large sets of vulnerability data-sets to observe
+various features of the vulnerabilities that they considered critical. Such features
+were the functionality and the criticality of the defects. Their analysis
+included the observation of vulnerability disclosures, the behavior of
+hackers in releasing exploits for vulnerabilities, patching and others. In
+their findings they highlighted the most exploited defects and showed that
+the percentage of remotely exploitable vulnerabilities has gradually increased
+over the years. Finally, Edwards et al.~\cite{EC12} have recently conducted
+a similar study to ours in which they have considered only four projects.
+Their results demonstrate that the number of exploitable bugs, does not
+always improve with each new release and that the rate of discovery of
+exploitable bugs begins to drop three to five years after the
+initial release.
 
@@
 \label{sec:exp}
-
-\begin{figure}[t]
-  \begin{center}
-    \includegraphics[scale=0.75]{figures/arch.pdf}
-  \end{center}
-  \caption{The Data Processing Architecture}
-  \label{fig:arch}
-\end{figure}
 
@@
 
+\begin{figure}[t]
+  \begin{center}
+    \includegraphics[scale=0.75]{figures/arch.pdf}
+  \end{center}
+  \caption{The Data Processing Architecture}
+  \label{fig:arch}
+\end{figure}
+
 \subsection{Data Provenance}
@@
 
+In addition, we implemented a series of audits in the worker scripts that
+checked if the {\sc jar}s are valid in terms of implementation. For instance,
+for every {\sc jar} the worker checked if there were any {\it .class} files
+before invoking FindBugs. After the project filtering, we narrowed down
+our data set to 17,505 projects with 115,214 versions.
+Table~\ref{tbl:repository} summarises the data set information and
+provides the basic descriptive statistic measurements. The distribution of version
+count among the selected projects is presented in Figure~\ref{fig:version-count}.
+
+The statistical measurements presented in Table~\ref{tbl:repository}
+indicate that we have 17,505 projects and the data set's median is 3,
+which means that almost 50\% (8,753 projects) of the project
+population have 1 to 3 versions. In general, most projects have a few
+number of versions, there are some projects with ten versions and
+only a few with hundreds of versions. The maximum number of versions
+for a project is 338. The 3$^{rd}$ quartile measurement also indicated
+that 75\% (13,129) of the projects have a maximum of 8 versions.
+
 \begin{table}[t]
@@
 
-In addition, we implemented a series of audits in the worker scripts that
-checked if the {\sc jar}s are valid in terms of implementation. For instance,
-for every {\sc jar} the worker checked if there were any {\it .class} files
-before invoking FindBugs. After the project filtering, we narrowed down
-our data set to 17,505 projects with 115,214 versions.
-Table~\ref{tbl:repository} summarises the data set information and
-provides the basic descriptive statistic measurements. The distribution of version
-count among the selected projects is presented in Figure~\ref{fig:version-count}.
-
 \begin{figure}[t]
@@
 \end{figure}
-
-The statistical measurements presented in Table~\ref{tbl:repository}
-indicate that we have 17,505 projects and the data set's median is 3,
-which means that almost 50\% (8,753 projects) of the project
-population have 1 to 3 versions. In general, most projects have a few
-number of versions, there are some projects with ten versions and
-only a few with hundreds of versions. The maximum number of versions
-for a project is 338. The 3$^{rd}$ quartile measurement also indicated
-that 75\% (13,129) of the projects have a maximum of 8 versions.
 
@@
 \label{sec:res}
+
+Our findings can be analysed at two levels. First, we discuss some
+primary observations concerning the security bugs of the Maven repository as a whole.
+Then, we provide a comprehensive analysis of the results and highlight our key findings.
 
@@
 
-Our findings can be analysed at two levels. First, we discuss some
-primary observations concerning the security bugs of the Maven repository as a whole.
-Then, we provide a comprehensive analysis of the results and highlight our key findings.
-
 \subsection{Overview and Initial Results}
@@
 \leavevmode
-	\begin{tabular}{p{24em} r}
+	\begin{tabular}{p{31em} r}
 	\hline
@@
 
-\begin{table}[t]
-    \centering
-    \caption{Correlations between Version and Defects Count}
-    \label{tbl:bugsperversion}
-    \input{bugsperversion.tex}
-\end{table}
-
 The relation between bugs and time can be traced from the number of
@@
 code change that falls foul of some bug identification rule.
+
+\begin{table}[t]
+    \centering
+    \caption{Correlations between Version and Defects Count}
+    \label{tbl:bugsperversion}
+    \input{bugsperversion.tex}
+\end{table}
 
@@
 
-\section{Related Work}
-\label{sec:rel}
-
-There are numerous methods for mining software repositories in the context
-of software evolution~\cite{KCM07}. In this section we focus on the ones
-that highlight the relationship between software bugs and evolution and try to
-extract useful conclusions. The key idea behind this is
-similar to ours: the combination of information like bug descriptions,
-documentation and others with the information retrieved from either the source
-or object code of a project version.
-
-{\it Refactoring identification} through software evolution is an approach used to
-relate refactorings with software bugs. Wei{\ss}gerber et al. found that a high
-ratio of refactorings is usually followed by an increasing ratio of bug
-reports~\cite{WD06}. In addition, they indicated that software bugs are sometimes introduced
-after an incomplete refactoring~\cite{GW05}.
-Ratzinger et al.~\cite{RSG08} showed that the number of bugs decreases, when the number of
-refactorings increases. Finally, Kim M. et al.~\cite{KCK11} indicated that {\sc api}-level
-refactorings aid bug fixes.
-
-{\it Micro patterns}, proposed by Kim et al.~\cite{KPW06}
-detect bug-prone patterns among source code. Micro patterns describe programming
-idioms like inheritance, data management, immutability and others. The approach
-involves the examination of all revisions of three open-source projects to extract bug
-introduction rates for each pattern. Gil et al.~\cite{GM05} analysed the
-prevalence of micro patterns across five Sun {\sc jdk} versions to conclude that
-pattern prevalence tends to be the same in software collections.
-
-{\it Querying techniques} are used to answer a broad range of questions
-regarding the evolution history of a project~\cite{HG05}. Bhattacharya et
-al.~\cite{BN11,B11} proposed a framework that is based upon
-recursively enumerable languages. The framework can correlate software
-bugs with developers in various ways. For instance, return the list of
-bugs fixed by a specific developer. Fischer et al.~\cite{FPG03} proposed
-an approach for populating a release history database that combines code
-information with bug tracking data. In this way, a developer can couple files
-that contain common bugs, estimate code maturity with respect to the bugs
-and others. The ``Ultimate Debian Database''~\cite{NZ10} is an {\sc sql}-based
-framework that integrates information about the Debian project from various
-sources to answer queries related to software bugs and source code.
-
-D'Ambros et al. have used {\it bug history analysis} to detect
-the critical components of a project~\cite{D08}. This is done by using an
-evolutionary meta-model~\cite{DL08}. The same approach was
-also used by Zimmermann et al.~\cite{ZNA08} to check the correlation
-of bugs with software properties like code complexity, process quality and others
-and predict future properties.
-
-The evolution of software artifacts has also been analysed to {\it reduce the false
-alarms} of the various static analysis tools. To achieve this, Spacco et
-al.~\cite{SHP06} introduced {\it pairing} and {\it warning signatures}. In the
-former, they tried to pair sets of bugs between versions in order to find
-similar patterns. In the latter, they computed a signature for every bug. This
-signature contained elements like the name of the class where the bug was found,
-the method and others. Then they searched for similar signatures between
-versions. In their research they also studied the evolution of 116 sequential
-builds of the Sun Java Sevelopment Kit ({\sc jdk}). Their findings indicated that
-high priority bugs are fixed over time. To improve the precision of bug
-detection, Kim et al.~\cite{KE07b,KE07} proposed a history-based warning
-prioritization algorithm by mining the history of bug-fixes of three
-different projects. The algorithm was based on the following hypothesis: if a
-bug that belongs to a specific category is eliminated by a code change, then
-this warning category is important. Working towards the same direction, Heckman
-et al.~\cite{HW09,HW08} have introduced benchmarks that use specific
-correlation algorithms and classification techniques to evaluate alert
-prioritization approaches.
-
-Lu et al.~\cite{LAAL13} studied the {\it evolution of file-system code}.
-Specifically, they analysed the changes of Linux file-system patches to extract
-bug patterns and categorize bugs based on their impact. Their findings
-indicated that the number of file-system bugs does not die down over time. By
-categorizing bugs they also showed the frequency of specific bugs in specific
-components.
-
-Completing the above approaches, our work focuses on the subset of security bugs.
-Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
-the evolution of software defects by examining six major versions of Firefox.
-To achieve this they created a database schema that contained information
-coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
-list,\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
-Bugzilla entries and others. Their findings indicated that security bugs are
-persistent over time. They also showed that there are many web users that use
-old versions of Firefox, meaning that old attacks will continue to work.
-Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
-security bugs with performance bugs. This was also done by analysing the project's
-Bugzilla. Their research presented evidence that security bugs require more experienced developers
-to be fixed. In addition, they suggested that security bug fixes are more complex than the
-fixes of performance and other bugs.
-Shahzad et al.~\cite{SSL12} analysed large sets of vulnerability data-sets to observe
-various features of the vulnerabilities that they considered critical. Such features
-were the functionality and the criticality of the defects. Their analysis
-included the observation of vulnerability disclosures, the behavior of
-hackers in releasing exploits for vulnerabilities, patching and others. In
-their findings they highlighted the most exploited defects and showed that
-the percentage of remotely exploitable vulnerabilities has gradually increased
-over the years. Finally, Edwards et al.~\cite{EC12} have recently conducted
-a similar study to ours in which they have considered only four projects.
-Their results demonstrate that the number of exploitable bugs, does not
-always improve with each new release and that the rate of discovery of
-exploitable bugs begins to drop three to five years after the
-initial release.
-
 \section{Conclusions and Future Work}
@@
 This research has been co-financed by the European Union (European Social Fund
---– {\sc esf}) and Greek national funds through the Operational Program
-``Education and Lifelong Learning'' of the National Strategic Reference Framework –
+- {\sc esf}) and Greek national funds through the Operational Program
+``Education and Lifelong Learning'' of the National Strategic Reference Framework -
 Research Funding Program: Heracleitus II. Investing in knowledge society

### 2013-06-26 docs/evol.tex
various fixes

@@
 In this
-paper we present how we used a large software ecosystem to analyse how different
-types of security vulnerabilities are related to the evolving software packages.
+paper we present how we used a large software ecosystem to analyse the
+relationship of different types of security vulnerabilities to 
+evolving software packages.
 For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
@@
 Finally, we examined the Maven ecosystem as a whole from a security
-perspective. Its structure gave us the opportunity to see if a project version that is a dependency to
+perspective. Its structure gave us the opportunity to see if a project version that is a dependency of
 a large number of others contains a low rate of security bugs~\cite{MW10}.
@@
 that highlight the relationship between software bugs and evolution and try to
-extract useful conclusions. The key idea behind this is
-similar to ours: the combination of information like bug descriptions,
-documentation and others with the information retrieved from either the source
-or object code of a project version.
+extract useful conclusions.
 
@@
 idioms like inheritance, data management, immutability and others. The approach
-involves the examination of all revisions of three open-source projects to extract bug
+involved the examination of all revisions of three open-source projects to extract bug
 introduction rates for each pattern. Gil et al.~\cite{GM05} analysed the
@@
 regarding the evolution history of a project~\cite{HG05}. Bhattacharya et
-al.~\cite{BN11,B11} proposed a framework that is based upon
+al.~\cite{BN11,B11} proposed a framework that is based on
 recursively enumerable languages. The framework can correlate software
@@
 information with bug tracking data. In this way, a developer can couple files
-that contain common bugs, estimate code maturity with respect to the bugs
-and others. The ``Ultimate Debian Database''~\cite{NZ10} is an {\sc sql}-based
+that contain common bugs, estimate code maturity with respect to the bugs,
+etc. The ``Ultimate Debian Database''~\cite{NZ10} is an {\sc sql}-based
 framework that integrates information about the Debian project from various
@@
 of bugs with software properties like code complexity, process quality and others
-and predict future properties.
+and to predict future properties.
 
@@
 the method and others. Then they searched for similar signatures between
-versions. In their research they also studied the evolution of 116 sequential
+versions. In their research they studied the evolution of 116 sequential
 builds of the Sun Java Sevelopment Kit ({\sc jdk}). Their findings indicated that
@@
 prioritization algorithm by mining the history of bug-fixes of three
-different projects. The algorithm was based on the following hypothesis: if a
-bug that belongs to a specific category is eliminated by a code change, then
-this warning category is important. Working towards the same direction, Heckman
+different projects. Working towards the same direction, Heckman
 et al.~\cite{HW09,HW08} have introduced benchmarks that use specific
@@
 over the years. Finally, Edwards et al.~\cite{EC12} have recently conducted
-a similar study to ours in which they have considered only four projects.
-Their results demonstrate that the number of exploitable bugs, does not
+a study similar  to ours in which they have considered only four projects.
+Their results demonstrate that the number of exploitable bugs does not
 always improve with each new release and that the rate of discovery of
@@
 
-Our experiment involved the collection of the metric results of the FindBugs
-tool. Before and during the experiment, we performed a number of functional
-fits on the data coming from the Maven repository, for reasons that we will describe below.
+Our experiment involved the collection of the metric results of the
+FindBugs tool. Before and during the experiment, we performed a number
+of filters on the data coming from the Maven repository, for reasons
+that we will describe below.
 
@@
 a number of {\it workers} (a custom Python script), a {\it task queue}
-mechanism (Rabbit{\sc mq} - version 3.0.1),\footnote{\url{http://www.rabbitmq.com/}}
-a {\it data repository} (Mongo{\sc db} - version 2.2),\footnote{\url{http://www.mongodb.org/}}
+mechanism (Rabbit{\sc mq}---version 3.0.1),
+a {\it data repository} (Mongo{\sc db}---version 2.2),
 and the {\it code repository}, which in our case it was
@@
 Maven is a build automation tool used primarily for Java projects and it is
-hosted by the Apache Software Foundation.\footnote{\url{http://www.apache.org/}}
-To describe the software project being built, its dependencies
-on other external modules, the build order, and required plug-ins Maven uses
-{\sc xml}. To build a software component, it dynamically downloads Java libraries
-and Maven plug-ins from the Maven central repository,
-and stores them in a local cache. The repository can be updated with
-new projects and also with new versions of existing projects.
+hosted by the Apache Software Foundation.
+It uses {\sc xml} to describe the software project being built, its dependencies
+on other external modules, the build order, and required plug-ins.
 
@@
 
-FindBugs is an open source static analysis tool that
-searches for software bugs. It works by examining the compiled Java virtual
+FindBugs works by examining the compiled Java virtual
 machine bytecodes of the programs it checks, using the bytecode engineering
@@
 hosts projects from languages other than Java such as Scala, Groovy,
-Clojure etc. we filtered out such projects by performing a series of checks in
+Clojure, etc., we filtered out such projects by performing a series of checks in
 the repository data and metadata.
@@
 \centering
-\caption{Number of Project Releases that Contain at Least One Severe Security Bug}
+\caption{Number of Project Releases that Contain at Least One Security
+  High Bug}
 \label{tbl:sev}
@@
 Another observation involves bugs that we could call {\it
-severe} and they are a subset of the {\it Security} category.
+Security High} and they are a subset of the {\it Security} category.
 Such bugs are related to vulnerabilities that appear due to the lack of user-input
@@
 Cross-Site Scripting~\cite{WS08}.
-Note that to exploit such vulnerabilities, a malicious user does
+To exploit such vulnerabilities, a malicious user does
 not have to know anything about the application internals. For all the other
@@
 they use the code fragments that include the defects.
-In the following section
-we provide results separately for this subcategory which we call {\it Security High}.
 The remaining bugs of the {\it Security} category
@@
 in another subcategory that we call {\it Security Low}.
-Note that this categorization was done specifically for this research to point out the
+This categorization was done specifically to point out the
 behaviour of bugs that currently top the corresponding lists of most
@@
 
-{\it Linus's Law} states that ``given enough eyeballs, all bugs are shallow".
+{\it Linus's Law} states that ``given enough eyeballs, all bugs are shallow''.
 In a context like this, we expect that
-the project versions that are dependencies to many other projects,
+the project versions that are dependencies to many other projects
 would have a small number of security
@@
 Contrary to Linus's Law, thirty three of them contained bugs coming from the
-{\it Security Low} subcategory, while two of them contained severe bugs.
+{\it Security Low} subcategory, while two of them contained {\it
+  Security High} bugs.
 Twenty five of them were latest versions at the time. This also highlights
@@
 of defects; this may be the result of doing and undoing a pervasive
-code change that falls foul of some bug identification rule.
+code change that runs foul of some bug identification rule.
 
-\begin{table}[t]
+\begin{table}[tphp]
     \centering
@@
 bugs, and of security bugs in particular, we used as a persistence
-indicator the number of versions a bug remains open in a project.
-To ``tag" a bug we created a bug identifier by using
-the type of the bug, the method name and the class name in which
-the bug was found in. We chose not to use the line number
-of the location of the bug since it could change from version
-to version and after a possible code refactoring.
-We grouped the persistence numbers by bug categories and then performed a
-Mann-Whitney $U$~\cite{HM98} test among all bug category pairs. The results are
-presented in Table~\ref{tbl:bug_persistence}. Cells in brackets show
-pairs where no statistically significant difference was found.
+indicator the number of versions a bug remains open in a project. To
+``tag" a bug we created a bug identifier by using the type of the bug,
+the method name and the class name in which the bug was found in. We
+chose not to use the line number of the location of the bug since it
+could change from version to version and after a possible code
+refactoring. We grouped the persistence numbers by bug categories and
+then performed a Mann-Whitney $U$~\cite{HM98} test among all bug
+category pairs. The results are presented in
+Table~\ref{tbl:bug_persistence} (at the end of this paper). Cells in
+brackets show pairs where no statistically significant difference was
+found.
 
 In general, although the average number of versions bugs in different
-bug categories remained opened was statistically different in many
+bug categories that remained open was statistically different in many
 cases, the difference is not spectacular. \textbf{In all cases a bug persists
@@
 
+\begin{table}[hbt]
+    \centering
+    \caption{Correlations between {\sc jar} size and Defects Count}
+    \label{tbl:jarsizecorr}
+    \input{jarsizecorr.tex}
+\end{table}
+
 \subsubsection{Security Bugs {\sc vs} Other Bug Categories}
@@
 number of distinct bugs that appeared in a project throughout its
-lifetime. The results can be seen in % Table~\ref{tbl:corrmatrix} and
-Figure~\ref{fig:corrplot}. We found significant, but not always
+lifetime, see Figure~\ref{fig:corrplot}. We found significant, but not always
 strong, correlations between all pairs. In general, the {\it Security
@@
 
-\begin{landscape}
-  \begin{table}
-    \setlength{\extrarowheight}{0.10cm}
-    \caption{Bug Persistence Comparison}
-    \label{tbl:bug_persistence}
-    \resizebox{0.95\columnwidth}{!}{
-    \input{bug_persistence.tex}}\\
-    The matrix presents pairwise Mann-Whitney $U$ test results
-    between the different bug categories. Each cell contains the test
-    result (the value of $U$), the $p$-value, the average for each
-    category and the sample size for each category. Cells in brackets show
-    pairs where no statistically significant difference was found.
-  \end{table}
-\end{landscape}
-
-\begin{table}[t]
-    \centering
-    \caption{Correlations between {\sc jar} size and Defects Count}
-    \label{tbl:jarsizecorr}
-    \input{jarsizecorr.tex}
-\end{table}
-
 \section{Conclusions and Future Work}
@@
 
-In this work we analyzed a large software repository to examine the
-behavior of security bugs. Specifically, we analysed more than 260GB
-of interdependent project versions to see how security bugs evolve
-over time, their persistence, their relation with other bug
-categories, and their relationship with size in terms of bytecode.
+We analysed more than 260GB of interdependent project versions to see
+how security bugs evolve over time, their persistence, their relation
+with other bug categories, and their relationship with size in terms
+of bytecode.
 
@@
 
-Contrary to the approaches that examine all versions
+Contrary to the approaches that examine versions
 formed after every change that has been committed to the repository,
@@
 
-Future work on our approach could also involve the observation of other ecosystems, that
-serve different languages, in the same manner such as, Python's PyPY
-(Python Package Index),\footnote{\url{https://pypi.python.org/pypi}}
-Perl's {\sc cpan} (Comprehensive Perl Archive Network),\footnote{\url{http://www.cpan.org/}}
-and Ruby's RubyGems.\footnote{\url{http://rubygems.org/}}
+Future work on our approach could also involve the observation of
+other ecosystems, that serve different languages, in the same manner
+such as, Python's PyPY (Python Package Index), Perl's {\sc cpan}
+(Comprehensive Perl Archive Network), and Ruby's
+RubyGems.
 
@@
 
+\begin{landscape}
+  \begin{table}
+    \setlength{\extrarowheight}{0.10cm}
+    \caption{Bug Persistence Comparison}
+    \label{tbl:bug_persistence}
+    \resizebox{0.95\columnwidth}{!}{
+    \input{bug_persistence.tex}}\\
+    The matrix presents pairwise Mann-Whitney $U$ test results
+    between the different bug categories. Each cell contains the test
+    result (the value of $U$), the $p$-value, the average for each
+    category and the sample size for each category. Cells in brackets show
+    pairs where no statistically significant difference was found.
+  \end{table}
+\end{landscape}
+
 \end{document}

### 2013-06-26 docs/evol.tex
final LASER version

@@
 A security bug is a programming error that introduces a potentially exploitable
-weakness into a computer system~\cite{SSL12,TJBD11,M06}. This
+weakness into a computer system~\cite{SSL12}. This
 weakness could lead to a security breach with unfortunate consequences in
@@
 others. Despite the significant effort to detect and eliminate such
-bugs~\cite{SZ12}, little attention has been paid to study them in relation to
-software evolution~\cite{L96,LRWPT97}. 
+bugs, little attention has been paid to study them in relation to
+software evolution~\cite{LRWPT97}. 
 One of the most common approaches to identify security bugs is
@@
 a static analysis tool that examines bytecode to detect software bugs and has already been used in
-research~\cite{AP10,HP07,HW08,SHP06}.
+research~\cite{AP10,HP07,SHP06}.
 Specifically, we ran FindBugs on all the project
@@
 they can cause significant financial damage to
-an organization~\cite{TH04,BCL08,R06}. 
+an organization~\cite{TH04,BCL08}. 
 Specifically,
@@
 knowing the that research has produced contradictory results on this
-issue~\cite{BP84,SYTP85,NBZ06,GKMS00}.
+issue~\cite{SYTP85,NBZ06,GKMS00}.
 Finally, we examined the Maven ecosystem as a whole from a security
 perspective. Its structure gave us the opportunity to see if a project version that is a dependency of
-a large number of others contains a low rate of security bugs~\cite{MW10}.
+a large number of others contains a low rate of security bugs.
 %In this case we can strengthen the relationship between Linus' Law and
@@
 \centering
-\caption{Number of Project Releases that Contain at Least One Security
-  High Bug}
+\caption{Number of Project Releases that Contain at Least One ``Security
+  High" Bug}
 \label{tbl:sev}
@@
 Such bugs are related to vulnerabilities that appear due to the lack of user-input
-validation and can lead to damaging attacks like {\sc sql} injection~\cite{RL12} and
-Cross-Site Scripting~\cite{WS08}.
+validation and can lead to damaging attacks like {\sc sql} injection and
+Cross-Site Scripting~\cite{RL12}.
 To exploit such vulnerabilities, a malicious user does
@@
 
-\subsubsection{The Relation of Defects with the size of a {\sc jar}}
+\subsubsection{The Relation of Defects with the size of a JAR}
 
@@
 % dds proposed the following:
-Given that, we could say that it would be productive to search for and fix
-security bugs even if a project grows bigger.
+%Given that, we could say that it would be productive to search for and fix
+%security bugs even if a project grows bigger.
 

### 2013-07-10 docs/evol.tex
minor fix
with a structured abstract

@@
 
-\author{
-% 1st. author
-\alignauthor Dimitris Mitropoulos\\
-       \affaddr{Department of Management Science and Technology}\\
-       \affaddr{Athens University of Economics and Business}\\
-       \email{dimitro@aueb.gr}
-% 2nd. author
-\alignauthor Vassilios Karakoidas\\
-       \affaddr{Department of Management Science and Technology}\\
-       \affaddr{Athens University of Economics and Business}\\
-       \email{bkarak@aueb.gr}
-% 3rd. author
-\alignauthor Panos Louridas\\
-       \affaddr{Department of Management Science and Technology}\\
-       \affaddr{Athens University of Economics and Business}\\
-       \email{louridas@aueb.gr}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Georgios Gousios\\
-       \affaddr{Software Engineering Research Group}\\
-       \affaddr{Delft University of Technology}\\
-       \email{G.Gousios@tudelft.nl}
-% 5th. author
-\alignauthor Diomidis Spinellis\\
-       \affaddr{Department of Management Science and Technology}\\
-       \affaddr{Athens University of Economics and Business}\\
-       \email{dds@aueb.gr}
-}
-
 \maketitle
 \begin{abstract}
-Security bugs are critical programming errors that can lead to serious
+{\bf Background.} Security bugs are critical programming errors that can lead to serious
 vulnerabilities in software. Such bugs may allow an attacker to take over
-an application, steal data or prevent the application from working at all.
-We used the projects stored in the Maven repository to study the
+an application, steal data or prevent the application from working at all.\\
+{\bf Aim.} We used the projects stored in the Maven repository to study the
 characteristics of security bugs individually and in relation to other software
-bugs. In particular, we analyzed every project version of the repository by using a
-popular static analysis tool. Then, by taking advantage of
-the repository's project history and dependency data we studied
+bugs. Specifically, we studied
 the evolution of security bugs through time. In addition, we examined
@@
 a) the size of the corresponding version, and
-b) other bug categories.
-Our findings indicate that there is no simple rule governing the number of
-security bugs as a project evolves.
+b) other bug categories.\\
+{\bf Method.} We analyzed every project version of the Maven repository by
+using FindBugs, a popular static analysis tool.
+To see how security bugs evolve over time we took advantage of
+the repository's project history and dependency data.\\
+{\bf Results.} Our results indicate that there is no simple rule governing
+the number of security bugs as a project evolves.
 In particular, we cannot say that across projects security-related
@@
 Finally, even if bugs seem to have similar behaviour,
-severe security bugs seem to be unassociated with other bug categories.
+severe security bugs seem to be unassociated with other bug categories.\\
+{\bf Conclusions.} Our findings indicate that further research should be done
+to analyze the evolution of security bugs. Given the fact that our experiment
+included only Java projects, similar research could be done for another
+ecosystem. Finally, the fact that projects have their own idiosyncrasies
+concerning security bugs, could help us find the common characteristics
+of the projects where security bugs increase over time.
 \end{abstract}
@@
 Then we observed the changes that involved the security bugs and their characteristics.
-This research builds upon our earlier work on the topic~\cite{MGS12}.
+%This research builds upon our earlier work on the topic~\cite{MGS12}.
 
@@
 high priority bugs are fixed over time. To improve the precision of bug
-detection, Kim et al.~\cite{KE07b,KE07} proposed a history-based warning
+detection, Kim et al.~\cite{KE07b} proposed a history-based warning
 prioritization algorithm by mining the history of bug-fixes of three
@@
 
-\subsubsection{Security Bugs {\sc vs} Other Bug Categories}
+\subsubsection{Security Bugs VS Other Bug Categories}
 

### 2013-09-12 docs/evol.tex
added usenix bib

@@
 \numberofauthors{5}
+
+\author{
+% 1st. author
+\alignauthor
+Dimitris Mitropoulos\\
+       \affaddr{Department of Management Science and Technology}\\
+       \affaddr{Athens University of Economics and Business}\\
+       \email{dimitro@aueb.gr}
+% 2nd. author
+\alignauthor
+Vassilios Karakoidas\\
+       \affaddr{Department of Management Science and Technology}\\
+       \affaddr{Athens University of Economics and Business}\\
+       \email{bkarak@aueb.gr}
+% 3rd. author
+\alignauthor
+Panos Louridas\\
+       \affaddr{Department of Management Science and Technology}\\
+       \affaddr{Athens University of Economics and Business}\\
+       \email{louridas@aueb.gr}
+\and  % use '\and' if you need 'another row' of author names
+% 4th. author
+\alignauthor Georgios Gousios\\
+       \affaddr{Software Engineering Research Group}\\
+       \affaddr{Delft University of Technology}\\
+       \email{G.Gousios@tudelft.nl}
+% 5th. author
+\alignauthor Diomidis Spinellis\\
+       \affaddr{Department of Management Science and Technology}\\
+       \affaddr{Athens University of Economics and Business}\\
+       \email{dds@aueb.gr}
+}
 
@@
 
-In this
-paper we present how we used a large software ecosystem to analyse the
+In this paper we present how we used a large software ecosystem to analyse the
 relationship of different types of security vulnerabilities to 
@@
 Completing the above approaches, our work focuses on the subset of security bugs.
-Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
+Focusing on such bugs is not a new idea.
+Ozment and Schechter~\cite{OS06} examined the code base of the Open{\sc bsd}
+operating system to determine whether its security is increasing
+over time. In particular, they measured the rate at which new code
+has been introduced and the rate at which defects have been reported over
+a 7.5 year period and fifteen releases.
+Even though the authors present statistical evidence
+of a decrease in the rate at which vulnerabilities are being reported
+defects seem to appear persistent for a period of at least 2.6 years.
+Massacci et al.~\cite{MNN11} observed
 the evolution of software defects by examining six major versions of Firefox.

### 2013-09-12 docs/evol.tex
more on the PC comments

@@
 Even though the authors present statistical evidence
-of a decrease in the rate at which vulnerabilities are being reported
+of a decrease in the rate at which vulnerabilities are being reported,
 defects seem to appear persistent for a period of at least 2.6 years.
@@
 To exploit such vulnerabilities, a malicious user does
-not have to know anything about the application internals. For all the other
-bugs, another program should be written to incorporate references to
+not have to know anything about the application internals. For almost
+all the other security bugs (coming from the {\it Malicious Code}
+category and the rest of the {\it Security} category bugs),
+another program should be written to incorporate references to
 mutable objects, access non-final fields, etc.
@@
 in another subcategory that we call {\it Security Low}.
-This categorization was done specifically to point out the
+This category contains for the most part, bugs
+that imply violations of good {\sc oop} (object-oriented programming)
+design (i.e. keeping variables private to classes and others).
+The above categorization was done specifically to point out the
 behaviour of bugs that currently top the corresponding lists of most
@@
 effect than the other categories}, even {\it Security Low} that nearly
-tops the list.
+tops the list. As we mentioned earlier, bugs that belong to the
+{\it Security High} category are related with
+user-input validation issues. Hence, even if a programmer adds
+code to a new version, if this code does not requires user
+input the possibility of such bug is minimal. 
 % dds proposed the following:
@@
 severe security bugs and a project's size
-we showed that they are not proportionally related. Furthermore, the
-pairwise correlations between all categories indicated that even though all the other
+we showed that they are not proportionally related.
+Given that, we could say that it would be productive to search for and fix
+security bugs even if a project grows bigger.
+Furthermore, the pairwise correlations between all categories
+indicated that even though all the other
 categories are related, severe bugs do not appear together with the other bugs.
@@
 characteristics of the projects where security bugs increase over time?
+In addition, by examining source code repositories more closely we could see how
+different development styles (i.e. size of commits, number of developers)
+affect projects.
 
-Future work on our approach could also involve the observation of
-other ecosystems, that serve different languages, in the same manner
-such as, Python's PyPY (Python Package Index), Perl's {\sc cpan}
-(Comprehensive Perl Archive Network), and Ruby's
+By selecting an large ecosystem that includes applications written only
+in Java, we excluded by default measurements that involve vulnerabilities like
+the infamous buffer overflow defects~\cite{K11}. Still, by examining software
+artefacts with similar characteristics facilitates the formation of
+an experiment. Thus, future work on our approach could also involve
+the observation of other ecosystems, that serve different languages,
+in the same manner such as, Python's PyPY (Python Package Index),
+Perl's {\sc cpan} (Comprehensive Perl Archive Network), and Ruby's
 RubyGems.
@@
 
-The project has been also co-financed by the European Regional Development Fund ({\sc erdf})
-and national funds and is a part of the Operational Programme ``Competitiveness \&
-Entrepreneurship" ({\sc opce} II), Measure ``{\sc cooperation}" (Action I).
+%The project has been also co-financed by the European Regional Development Fund ({\sc erdf})
+%and national funds and is a part of the Operational Programme ``Competitiveness \&
+%Entrepreneurship" ({\sc opce} II), Measure ``{\sc cooperation}" (Action I).
 

### 2013-09-16 docs/evol.tex
added percentages for the security bugs separetely

@@
 security bugs (the sum of the {\it Security} and {\it Malicious Code}
-categories) are the most popular in the repository ($\geq 21\%$ each).
+categories - 0.21\% + 21.81\%) are the most popular in the repository ($\geq 21\%$ each).
 This could be a strong indication that programmers write code
@@
 with other bug categories, and their relationship with size in terms
-of bytecode.
+of bytecode.\footnote{Our data and code are available online at:
+\url{https://github.com/bkarak/evol_security_publication_2012}}
 
@@
 
-Our data and code will be publicly available upon publication.
-
 \section{Acknowledgments}

### 2013-09-25 docs/evol.tex
final version

@@
 \usepackage{array}
+\usepackage{color}
+
+\usepackage{ulem}
 
@@
 To exploit such vulnerabilities, a malicious user does
-not have to know anything about the application internals. For almost
-all the other security bugs (coming from the {\it Malicious Code}
-category and the rest of the {\it Security} category bugs),
+not have to know anything about the application internals.
+For almost all the other security bugs (coming from
+the {\it Malicious Code} category and the rest of
+the {\it Security} category bugs),
 another program should be written to incorporate references to
@@
 tops the list. As we mentioned earlier, bugs that belong to the
-{\it Security High} category are related with
+{\it Security High} category are related to
 user-input validation issues. Hence, even if a programmer adds
-code to a new version, if this code does not requires user
-input the possibility of such bug is minimal. 
+code to a new version, if this code does not require user
+input, the possibility of such bug is minimal. 
 % dds proposed the following:
@@
 associated with other bugs, or only weakly so. Perhaps it takes a
-special kind of blunder to make it a security hazard.
+special kind of blunder to make it a security hazard. Thus, to find such
+defects, code reviewers with experience in software security
+issues might be needed.
 

### 2013-09-25 docs/evol.tex
new style - USENIX proceedings

@@
-\documentclass{sig-alternate}
+\documentclass[letterpaper,twocolumn,10pt]{article}
+\usepackage{usenix,epsfig,endnotes}
+%\documentclass{sig-alternate}
 
@@
 
-\usepackage{ulem}
+\pdfpagewidth=8.5in
+\pdfpageheight=11in
 
@@
 
-\title{Dismal Code: Studying the Evolution of Security Bugs}
+\date{}
 
-\numberofauthors{5}
+\title{\Large \bf Dismal Code: Studying the Evolution of Security Bugs}
 
 \author{
-% 1st. author
-\alignauthor
-Dimitris Mitropoulos\\
-       \affaddr{Department of Management Science and Technology}\\
-       \affaddr{Athens University of Economics and Business}\\
-       \email{dimitro@aueb.gr}
-% 2nd. author
-\alignauthor
-Vassilios Karakoidas\\
-       \affaddr{Department of Management Science and Technology}\\
-       \affaddr{Athens University of Economics and Business}\\
-       \email{bkarak@aueb.gr}
-% 3rd. author
-\alignauthor
-Panos Louridas\\
-       \affaddr{Department of Management Science and Technology}\\
-       \affaddr{Athens University of Economics and Business}\\
-       \email{louridas@aueb.gr}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Georgios Gousios\\
-       \affaddr{Software Engineering Research Group}\\
-       \affaddr{Delft University of Technology}\\
-       \email{G.Gousios@tudelft.nl}
-% 5th. author
-\alignauthor Diomidis Spinellis\\
-       \affaddr{Department of Management Science and Technology}\\
-       \affaddr{Athens University of Economics and Business}\\
-       \email{dds@aueb.gr}
+{\rm Dimitris Mitropoulos}\\
+Department of Management Science and Technology,
+Athens University of Economics and Business
+\and
+{\rm Vassilios Karakoidas}\\
+Department of Management Science and Technology,
+Athens University of Economics and Business
+\and
+{\rm Panos Louridas}\\
+Department of Management Science and Technology,
+Athens University of Economics and Business
+\and
+{\rm Georgios Gousios}\\
+Software Engineering Research Group,
+Delft University of Technology
+\and
+{\rm Diomidis Spinellis}\\
+Department of Management Science and Technology,
+Athens University of Economics and Business
 }
@@
 \maketitle
-\begin{abstract}
+\thispagestyle{empty}
+
+\subsection*{Abstract}
 {\bf Background.} Security bugs are critical programming errors that can lead to serious
@@
 of the projects where security bugs increase over time.
-\end{abstract}
 
-\keywords{Security Bugs, Static Analysis, Software Evolution, Software
-Security, Maven, FindBugs.
-}
 \section{Introduction}
@@
 evolving software packages.
-For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
+For our research we used {\it FindBugs},\endnote{\url{http://findbugs.sourceforge.net/}}
 a static analysis tool that examines bytecode to detect software bugs and has already been used in
@@
 versions of all the projects that exist in the
-{\it Maven Central Repository}\footnote{\url{http://mvnrepository.com/}}
+{\it Maven Central Repository}\endnote{\url{http://mvnrepository.com/}}
 (approximately 265GB of data---see Section~\ref{sec:data}).
@@
 coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
-list,\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
+list,\endnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
 Bugzilla entries and others. Their findings indicated that security bugs are
@@
 mutable objects, access non-final fields, etc.
-Also, as bug descriptions indicate,\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
+Also, as bug descriptions indicate,\endnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
 if an application has bugs coming from the {\it Security High} category,
@@
 behaviour of bugs that currently top the corresponding lists of most
-security providers.\footnote{\url{http://cwe.mitre.org/top25/index.html}}
+security providers.\endnote{\url{http://cwe.mitre.org/top25/index.html}}
 
@@
 with other bug categories, and their relationship with size in terms
-of bytecode.\footnote{Our data and code are available online at:
+of bytecode.\endnote{Our data and code are available online at:
 \url{https://github.com/bkarak/evol_security_publication_2012}}
@@
 
-\bibliographystyle{abbrv}
+{\footnotesize \bibliographystyle{acm}
 \bibliography{evol}

### 2013-09-26 docs/evol.tex
fixed authors, pics

@@
 \author{
-{\rm Dimitris Mitropoulos}\\
-Department of Management Science and Technology,
-Athens University of Economics and Business
-\and
-{\rm Vassilios Karakoidas}\\
-Department of Management Science and Technology,
-Athens University of Economics and Business
-\and
-{\rm Panos Louridas}\\
-Department of Management Science and Technology,
-Athens University of Economics and Business
+{\rm Dimitris Mitropoulos,Vassilios Karakoidas,Panos Louridas}\\
+{\it Department of Management Science and Technology,
+Athens University of Economics and Business}\\
+{\tt dimitro@aueb.gr, bkarak@aueb.gr, louridas@aueb.gr}
+%\and
+%{\rm Vassilios Karakoidas}\\
+%Department of Management Science and Technology,
+%Athens University of Economics and Business
+%\and
+%{\rm Panos Louridas}\\
+%Department of Management Science and Technology,
+%Athens University of Economics and Business
 \and
 {\rm Georgios Gousios}\\
-Software Engineering Research Group,
-Delft University of Technology
+{\it Software Engineering Research Group,
+Delft University of Technology}\\
+{\tt G.Gousios@tudelft.nl}
 \and
 {\rm Diomidis Spinellis}\\
-Department of Management Science and Technology,
-Athens University of Economics and Business
+{\it Department of Management Science and Technology,
+Athens University of Economics and Business}\\
+{\tt dds@aueb.gr}
 }
@@
   \begin{center}
-    \includegraphics[scale=0.75]{figures/arch.pdf}
+    \includegraphics[scale=0.73]{figures/arch.pdf}
   \end{center}
@@
 	\centering
-	\includegraphics[scale=0.42]{version_count.pdf}
+	\includegraphics[scale=0.37]{version_count.pdf}
 	\caption{Distribution of Version Count Among Project Population}
@@
 \label{tbl:bug-cat}
-\begin{tabular}{l p{35em}}
+\begin{tabular}{l p{29em}}
 \hline
@@
 	\centering
-	\includegraphics[scale=0.39]{bug_percent}
+	\includegraphics[scale=0.35]{bug_percent}
 	\caption{Bug Percentage in Maven Repository}
@@
   \centering
-  \includegraphics[scale=0.47]{corrplot.pdf}
+  \includegraphics[scale=0.43]{corrplot.pdf}
   \caption{Correlation matrix plot for bug categories}

### 2013-10-08 docs/evol.tex
changed image captions, removed page numbers
minor fixes

@@
 \maketitle
+%\thispagestyle{empty}
 \thispagestyle{empty}
+\pagestyle{empty}
 
@@
 {\it Maven Central Repository}\endnote{\url{http://mvnrepository.com/}}
-(approximately 265GB of data---see Section~\ref{sec:data}).
+(approximately 265{\sc gb} of data---see Section~\ref{sec:data}).
 Then we observed the changes that involved the security bugs and their characteristics.
@@
 on other external modules, the build order, and required plug-ins.
+To build a software component, it dynamically downloads Java libraries
+and Maven plug-ins from the Maven central repository,
+and stores them in a local cache. The repository can be updated with
+new projects and also with new versions of existing projects.
 
@@
 \centering
-\caption{Descriptive Statistics Measurements for the Maven Repository}
 \label{tbl:repository}
@@
 \end{tabular}
+\caption{Descriptive Statistics Measurements for the Maven Repository}
 \end{table}
@@
 \centering
-\caption{Bug Categorisation According to FindBugs}
 \label{tbl:bug-cat}
@@
 \end{tabular}
+\caption{Bug Categorisation According to FindBugs}
 \end{table*}
@@
 \centering
-\caption{Number of Project Releases that Contain at Least One ``Security
-  High" Bug}
 \label{tbl:sev}
@@
 	\end{tabular}
+\caption{Number of Project Releases that Contain at Least One ``Security
+  High" Bug}
 \end{table*}
@@
 
+\theendnotes
+
 \begin{landscape}

### 2013-10-13 docs/evol.tex
minor fixes.

@@
   \end{center}
-  \caption{The Data Processing Architecture}
+  \caption{The data processing architecture.}
   \label{fig:arch}
@@
 \centering
+\caption{Descriptive statistics measurements for the Maven repository.}
 \label{tbl:repository}
@@
 \end{tabular}
-\caption{Descriptive Statistics Measurements for the Maven Repository}
 \end{table}
@@
 	\includegraphics[scale=0.37]{version_count.pdf}
-	\caption{Distribution of Version Count Among Project Population}
+	\caption{Distribution of version count among project population.}
 	\label{fig:version-count}
@@
 \centering
+\caption{Bug categorisation according to FindBugs.}
 \label{tbl:bug-cat}
@@
 \end{tabular}
-\caption{Bug Categorisation According to FindBugs}
 \end{table*}
@@
 and 45,559 coming from the second.
-
-\begin{table*}[t]
-\centering
-\label{tbl:sev}
-\leavevmode
-	\begin{tabular}{p{31em} r}
-	\hline
-	Bug Description & Number of Project Releases\\
- 	\hline
-	{\sc hrs}: {\sc http} cookie formed from untrusted input & 151\\
-	{\sc hrs}: {\sc http} response splitting vulnerability & 1,579\\
-	{\sc pt}: absolute path traversal in servlet  & 103\\
-	{\sc pt}: relative path traversal in servlet & 57\\
-	{\sc sql}: non-constant string passed to execute method on an {\sc sql} statement & 1,875\\
-	{\sc sql}: a prepared statement is generated from a non-constant String & 1,486\\
-	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 18\\
-	{\sc xss}: Servlet reflected cross site scripting vulnerability in error page & 90\\
-	{\sc xss}: Servlet reflected cross site scripting vulnerability & 142\\
-	\hline
-	\end{tabular}
-\caption{Number of Project Releases that Contain at Least One ``Security
-  High" Bug}
-\end{table*}
 
@@
 	\includegraphics[scale=0.35]{bug_percent}
-	\caption{Bug Percentage in Maven Repository}
+	\caption{Bug percentage in Maven repository.}
 	\label{fig:bug-per} 
@@
 it might have more vulnerabilities that FindBugs doesn't report.
-Table~\ref{tbl:sev} presents the number
+Table~\ref{tbl:severe} presents the number
 of releases where at least one of these bugs exists. In essence, 5,501 releases
@@
 security providers.\endnote{\url{http://cwe.mitre.org/top25/index.html}}
+
+\begin{table*}[t]
+\centering
+\caption{Number of project releases that contain at least one ``Security
+  High" bug.}
+\label{tbl:severe}
+\leavevmode
+	\begin{tabular}{p{31em} r}
+	\hline
+	Bug Description & Number of Project Releases\\
+ 	\hline
+	{\sc hrs}: {\sc http} cookie formed from untrusted input & 151\\
+	{\sc hrs}: {\sc http} response splitting vulnerability & 1,579\\
+	{\sc pt}: absolute path traversal in servlet  & 103\\
+	{\sc pt}: relative path traversal in servlet & 57\\
+	{\sc sql}: non-constant string passed to execute method on an {\sc sql} statement & 1,875\\
+	{\sc sql}: a prepared statement is generated from a non-constant String & 1,486\\
+	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 18\\
+	{\sc xss}: Servlet reflected cross site scripting vulnerability in error page & 90\\
+	{\sc xss}: Servlet reflected cross site scripting vulnerability & 142\\
+	\hline
+	\end{tabular}
+\end{table*}
 
@@
     \centering
-    \caption{Correlations between Version and Defects Count}
+    \caption{Correlations between version and defects count.}
     \label{tbl:bugsperversion}
@@
     \centering
-    \caption{Correlations between {\sc jar} size and Defects Count}
+    \caption{Correlations between {\sc jar} size and defects count.}
     \label{tbl:jarsizecorr}
@@
   \includegraphics[scale=0.43]{corrplot.pdf}
-  \caption{Correlation matrix plot for bug categories}
+  \caption{Correlation matrix plot for bug categories.}
   \label{fig:corrplot}
@@
 
-We analysed more than 260GB of interdependent project versions to see
+We analysed more than 260{\sc gb} of interdependent project versions to see
 how security bugs evolve over time, their persistence, their relation
@@
 the infamous buffer overflow defects~\cite{K11}. Still, by examining software
-artefacts with similar characteristics facilitates the formation of
+artifacts with similar characteristics facilitates the formation of
 an experiment. Thus, future work on our approach could also involve
@@
     \setlength{\extrarowheight}{0.10cm}
-    \caption{Bug Persistence Comparison}
+    \caption{Bug persistence comparison.}
     \label{tbl:bug_persistence}
